### 2021-11-28 Initial idea/initial_idea_paper.tex
Initial commit

\documentclass{setup}

\assignment{Initial idea: Visual Question Answering}
\authorOne{Jorrit Willaert} % Name of first team partner.
\studentnumberOne{r0652971} % Student number of first team partner.

\begin{document}
	\maketitle

	DeepProbLog offers the ability to integrate probabilistic knowledge with deep neural networks. This way, the strength of the neural network (system 1: typical subconscious tasks such as visual recognition, the processing of languages, \dots) is complemented with the strength of rule-based mechanisms (system 2: slow, sequential thinking such as the derivation of a proof). I propose an application that requires the integration of both systems.

	The Sort-of-CLEVR dataset is a simplified version of the CLEVR dataset \cite{clevr_dataset}. This simplified dataset is composed of 10 000 images with per image 20 accompanied questions. An image consists of spread out objects, with randomly chosen shapes and colors. The questions are divided in

	\bibliographystyle{plain} 
	\bibliography{library.bib}

\end{document}

### 2021-11-28 Initial idea/initial_idea_paper.tex
Write further

@@
 An image consists of spread out objects, with randomly chosen shapes and colors.
-The questions are divided in
+The questions are divided in two categories: non-relational and relational questions.
+Non-relational questions ask for example about the shape, the horizontal or vertical location of the colored object.
+Relational questions, on the other hand, ask about the shape of the object which is closest (or furthest) to a certain colored object, or ask about the number of objects with the same shape \cite{sort_of_clevr_dataset}.
+
+	\begin{figure}[htbp]
+		\centerline{\includegraphics[scale=.48]{example_image_of_dataset.png}}
+		\caption{An sample image from the Sort-of-CLEVR dataset \cite{sort_of_clevr_dataset}}
+		\label{image:example_image_of_dataset}
+		\end{figure}
+
+	A sample image is given in Figure \ref{image:example_image_of_dataset}.
+With this sample image, an answer on a non-relational question such as "What is the shape of the blue object?" would be: "square", while an answer on a relational question such as "How many objects have same the same shape as the blue one?" would be: "3".
 
 	\bibliographystyle{plain} 
-	\bibliography{library.bib}
+	\bibliography{Capita_Selecta_AI_Initial_Idea}
 

### 2021-11-29 Initial idea/initial_idea_paper.tex
Write a bit further

@@
 \assignment{Initial idea: Visual Question Answering}
-\authorOne{Jorrit Willaert} % Name of first team partner.
-\studentnumberOne{r0652971} % Student number of first team partner.
+\authorOne{Jorrit Willaert} 
+\studentnumberOne{r0652971}
 
@@
 	DeepProbLog offers the ability to integrate probabilistic knowledge with deep neural networks.
-This way, the strength of the neural network (system 1: typical subconscious tasks such as visual recognition, the processing of languages, \dots) is complemented with the strength of rule-based mechanisms (system 2: slow, sequential thinking such as the derivation of a proof).
+This way, the strength of neural networks (system 1: typical subconscious tasks such as visual recognition, the processing of languages, \dots) is complemented with the strength of rule-based mechanisms (system 2: slow, sequential thinking such as the derivation of a proof).
 I propose an application that requires the integration of both systems.
@@
 	\begin{figure}[htbp]
-		\centerline{\includegraphics[scale=.48]{example_image_of_dataset.png}}
-		\caption{An sample image from the Sort-of-CLEVR dataset \cite{sort_of_clevr_dataset}}
+		\centerline{\fbox{\includegraphics[scale=.25]{example_image_of_dataset.png}}}
+		\caption{A sample image from the Sort-of-CLEVR dataset \cite{sort_of_clevr_dataset}}
 		\label{image:example_image_of_dataset}
@@
 	A sample image is given in Figure \ref{image:example_image_of_dataset}.
-With this sample image, an answer on a non-relational question such as "What is the shape of the blue object?" would be: "square", while an answer on a relational question such as "How many objects have same the same shape as the blue one?" would be: "3".
+With this sample image, an answer on a non-relational question such as "What is the shape of the blue object?" would be: "square", while an answer on a relational question such as "How many objects have the same shape as the blue one?" would be: "3".
+
+	I propose to generate data based on the Sort-of-CLEVR dataset, with the simplification that objects may not be entirely randomly located, but instead only in certain positions on a grid.
+A 5 by 5 grid could for example be used.
+The generation of new images and accompanied questions is rather straightforward, which could probably even be done at training time.
+
+	I would use 25 convolutional neural networks, one for each grid position.
+The output would naturally be if an object is located in that position, and what its shape and color is.
+Once the location, shapes and colors of the objects are known, rule-based mechanisms can be used to answer the accompanied questions.
 

### 2022-03-06 relational-networks/sort_of_clevr_generator.py
Also generate test and val sets with different seeds

@@ -12,7 +12,7 @@ import argparse
 import csv
 
 parser = argparse.ArgumentParser(description='Sort-of-CLEVR dataset generator')
-parser.add_argument('--seed', type=int, default=3, metavar='S',
+parser.add_argument('--seed', type=int, default=10, metavar='S',
                     help='random seed (default: 1)')
 parser.add_argument('--t-subtype', type=int, default=-1,
                     help='Force ternary questions to be of a given type')
@@ -182,7 +182,7 @@ def build_dataset_item():
     return dataset
 
 if __name__ == "__main__":
-    with open('../deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/test/test.csv', 'w') as f:
+    with open('../deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/val/val.csv', 'w') as f:
         writer = csv.writer(f)
         for i in range(2000):
             img, norelations, binary_relations = build_dataset_item()
@@ -195,5 +195,5 @@ if __name__ == "__main__":
             for q in questions_binary_relations:
                 array.append(q)
             array.append(answer_binary_relations)
-            cv2.imwrite('../deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/test/images/' + str(i) + '.png', img)
+            cv2.imwrite('../deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/val/images/' + str(i) + '.png', img)
             writer.writerow(array)

### 2022-03-07 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Add things to the to_query() method

@@ -22,22 +22,60 @@ class Coins(ImageDataset):
         self.subset = subset
         with open("{}/{}/{}.csv".format(path, subset, subset)) as f:
             for line in f:
-                norelational_question, norelational_answer, binary_question, binary_answer = [(l.rstrip('\n')[1:-1]).split() for l in line.split(",")]
+                norelational_question, norelational_answer, binary_question, binary_answer = \
+                    [(l.rstrip('\n')[1:-1]).split() for l in line.split(",")]
                 self.data.append((norelational_question, norelational_answer, binary_question, binary_answer))
 
     def to_query(self, i):
         norelational_question, norelational_answer, binary_question, binary_answer = self.data[i]
-        #sub = {Term("a"): Term("tensor", Term(self.subset, Constant(i)))}
-        # if j == 0:
-        #     return Term('coin', Constant(j + 1), Term('a'), Term(c1)), sub
-        # elif j == 1:
-        #     return Term('coin', Constant(j + 1), Term('a'), Term(c2)), sub
-        # else:
-        #return Query(Term("game", Term("a"), Term(outcome)), sub)
+        # Begin with nonrelational 
+        sh = None
+        if norelational_question[0] == 1: # Question about red object
+            sh = "red"
+        elif norelational_answer[1] == 1:
+            sh = "green"
+        else:
+            print("[ERROR] No object specified")
+        
+        if norelational_question[2] == 1: # Nonbinary question
+            pass
+        elif norelational_question[3] == 1: # Binary question
+            print("Not yet defined")
+        else:
+            print("[ERROR] No type of question specified")
+        
+        if norelational_question[4] == 1: # Query about the shape of the object
+            question = "shape"
+            if norelational_answer == 2:
+                outcome = "rectangle"
+            elif norelational_answer == 3:
+                outcome = "circle"
+            else:
+                print("[ERROR] Wrong outcome for the shape")
+        if norelational_question[5] == 1: # Query about the horizontal position
+            question = "horizontal_side"
+            if norelational_answer == 0:
+                outcome = "left"
+            elif norelational_answer == 1:
+                outcome = "right"
+            else: 
+                print("[ERROR] Wrong outcome for the horizontal position")
+        if norelational_question[6] == 1: # Query about the vertical position
+            question = "vertical_side"
+            if norelational_answer == 0:
+                outcome = "bottom"
+            elif norelational_answer == 1:
[…]

### 2022-03-07 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
First bugfixes in to_query()

@@ -12,7 +12,7 @@ transform = transforms.Compose(
     [transforms.ToTensor(), transforms.Normalize((0.5, 0.5, 0.5), (0.5, 0.5, 0.5))]
 )
 
-class Coins(ImageDataset):
+class SORTOFCLEVRDataset(ImageDataset):
     def __init__(
         self,
         subset,
@@ -24,6 +24,10 @@ class Coins(ImageDataset):
             for line in f:
                 norelational_question, norelational_answer, binary_question, binary_answer = \
                     [(l.rstrip('\n')[1:-1]).split() for l in line.split(",")]
+                norelational_question = list(map(int, list(map(float, norelational_question))))
+                norelational_answer = int(float(norelational_answer[0]))
+                binary_question = list(map(int, list(map(float, binary_question))))
+                binary_answer = int(float(binary_answer[0]))
                 self.data.append((norelational_question, norelational_answer, binary_question, binary_answer))
 
     def to_query(self, i):
@@ -32,7 +36,7 @@ class Coins(ImageDataset):
         sh = None
         if norelational_question[0] == 1: # Question about red object
             sh = "red"
-        elif norelational_answer[1] == 1:
+        elif norelational_question[1] == 1:
             sh = "green"
         else:
             print("[ERROR] No object specified")
@@ -44,6 +48,8 @@ class Coins(ImageDataset):
         else:
             print("[ERROR] No type of question specified")
         
+        question = None
+        outcome = None
         if norelational_question[4] == 1: # Query about the shape of the object
             question = "shape"
             if norelational_answer == 2:
@@ -52,7 +58,7 @@ class Coins(ImageDataset):
                 outcome = "circle"
             else:
                 print("[ERROR] Wrong outcome for the shape")
-        if norelational_question[5] == 1: # Query about the horizontal position
+        elif norelational_question[5] == 1: # Query about the horizontal position
             question = "horizontal_side"
             if norelational_answer == 0:
                 outcome = "left"
@@ -60,7 +66,7 @@ class Coins(ImageDataset):
                 outcome = "right"
             else: 
                 print("[ERROR] Wrong outcome for the horizontal position")
-        if norelational_question[6] == 1: # Query about the vertical position
+        elif norelational_question[6] == 1: # Query about the vertical position
             question = "vertical_side"
             if norelational_answer == 0:
                 outcome = "bottom"
[…]

### 2022-03-07 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl

@@ -1,11 +1,36 @@
 % We know that there are two objects in a four grid space. Two shapes possible, two colors possible.
 % The green cnn detects the position, and the shape --> x. If x < 4: Shape = rectangle. Else: shape = circle. (x modulo 4 = position)  
 
-nn(cnn_red,[X],Y,[0,1,2,3,4,5,6,7]) :: detect_green_state(X,Y_red).
-nn(cnn_green, [X], Y, [0,1,2,3,4,5,6,7]) :: detect_red_state(X, Y_green).
+nn(cnn_red,[X],Y,[0,1,2,3,4,5,6,7]) :: detect_red_state(X,Y_red).
+nn(cnn_green, [X], Y, [0,1,2,3,4,5,6,7]) :: detect_green_state(X, Y_green).
 
-shape_is_rectangle(Out) :-
-    Out < 4.
+shape(red, Img, rectangle) :-
+    detect_red_state(Img, Y_red),
+    Y_red < 4.
+
+shape(green, Img, rectangle) :-
+    detect_green_state(Img, Y_green),
+    Y_green < 4.
+
+horizontal_side(red, Img, left) :-
+    detect_red_state(Img, Y_red),
+    position(Y_red, Pos)
+    left_side(Pos).
+
+horizontal_side(green, Img, left) :-
+    detect_green_state(Img, Y_red),
+    position(Y_red, Pos)
+    left_side(Pos).
+
+vertical_side(red, Img, bottom) :-
+    detect_red_state(Img, Y_red),
+    position(Y_red, Pos)
+    bottom_side(Pos).
+
+vertical_side(green, Img, bottom) :-
+    detect_green_state(Img, Y_red),
+    position(Y_red, Pos)
+    bottom_side(Pos).
 
 position(Out, Pos) :-
     Pos is Out mod 4.

### 2022-03-07 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -9,7 +9,7 @@ from deepproblog.utils import format_time_precise
 from deepproblog.evaluate import get_confusion_matrix
 from deepproblog.train import train_model
 from deepproblog.dataset import DataLoader
-from deepproblog.examples.SORTOFCLEVR.data.data import SORTOFCLEVRDataset
+from data.data import SORTOFCLEVRDataset
 
 
 cnn_red = CNNNetwork(out_size=8)
@@ -20,13 +20,15 @@ net_green = Network(cnn_green, "cnn_green", Adam(cnn_green.parameters(), lr=3e-3
 
 model = Model("/home/jorrit/Data/KU Leuven/Semester 12/Capita Selecta H05N0a/deepproblog/src/deepproblog/examples/HWF/model.pl", [net_red, net_green])
 
-# model.add_tensor_source("sort_of_clevr", TODO)
-model.set_engine(ExactEngine(model), cache=True)
-
-dataset = SORTOFCLEVRDataset("train")
+train_dataset = SORTOFCLEVRDataset("train")
 val_dataset = SORTOFCLEVRDataset("val")
 test_dataset = SORTOFCLEVRDataset("test")
-loader = DataLoader(dataset, 32, shuffle=True)
+loader = DataLoader(train_dataset, 32, shuffle=True)
+
+model.add_tensor_source("train", train_dataset)
+model.add_tensor_source("val", val_dataset)
+model.add_tensor_source("test", test_dataset)
+model.set_engine(ExactEngine(model), cache=True)
 
 train_log = train_model(
     model,

### 2022-03-07 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Bugfixes: now searching for non-ground prob fact

@@ -1,35 +1,35 @@
 % We know that there are two objects in a four grid space. Two shapes possible, two colors possible.
 % The green cnn detects the position, and the shape --> x. If x < 4: Shape = rectangle. Else: shape = circle. (x modulo 4 = position)  
 
-nn(cnn_red,[X],Y,[0,1,2,3,4,5,6,7]) :: detect_red_state(X,Y_red).
-nn(cnn_green, [X], Y, [0,1,2,3,4,5,6,7]) :: detect_green_state(X, Y_green).
+nn(cnn_red,[X],Y,[0,1,2,3,4,5,6,7]) :: detect_state(red, X, Y_red).
+nn(cnn_green, [X], Y, [0,1,2,3,4,5,6,7]) :: detect_state(green, X, Y_green).
 
 shape(red, Img, rectangle) :-
-    detect_red_state(Img, Y_red),
+    detect_state(red, Img, Y_red),
     Y_red < 4.
 
 shape(green, Img, rectangle) :-
-    detect_green_state(Img, Y_green),
+    detect_state(green, Img, Y_green),
     Y_green < 4.
 
 horizontal_side(red, Img, left) :-
-    detect_red_state(Img, Y_red),
-    position(Y_red, Pos)
+    detect_state(red, Img, Y_red),
+    position(Y_red, Pos),
     left_side(Pos).
 
 horizontal_side(green, Img, left) :-
-    detect_green_state(Img, Y_red),
-    position(Y_red, Pos)
+    detect_state(green, Img, Y_green),
+    position(Y_green, Pos),
     left_side(Pos).
 
 vertical_side(red, Img, bottom) :-
-    detect_red_state(Img, Y_red),
-    position(Y_red, Pos)
+    detect_state(red, Img, Y_red),
+    position(Y_red, Pos),
     bottom_side(Pos).
 
 vertical_side(green, Img, bottom) :-
-    detect_green_state(Img, Y_red),
-    position(Y_red, Pos)
+    detect_state(green, Img, Y_green),
+    position(Y_green, Pos),
     bottom_side(Pos).
 
 position(Out, Pos) :-

### 2022-03-07 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -1,7 +1,7 @@
 from json import dumps
 from torch.optim import Adam
 
-from deepproblog.examples.SORTOFCLEVR.network import CNNNetwork
+from network import CNNNetwork
 from deepproblog.network import Network
 from deepproblog.model import Model
 from deepproblog.engines.exact_engine import ExactEngine
@@ -18,7 +18,7 @@ cnn_green = CNNNetwork(out_size=8)
 net_red = Network(cnn_red, "cnn_red", Adam(cnn_red.parameters(), lr=3e-3), batching=True)
 net_green = Network(cnn_green, "cnn_green", Adam(cnn_green.parameters(), lr=3e-3), batching=True)
 
-model = Model("/home/jorrit/Data/KU Leuven/Semester 12/Capita Selecta H05N0a/deepproblog/src/deepproblog/examples/HWF/model.pl", [net_red, net_green])
+model = Model("/home/jorrit/Data/KU Leuven/Semester 12/Capita Selecta H05N0a/deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl", [net_red, net_green])
 
 train_dataset = SORTOFCLEVRDataset("train")
 val_dataset = SORTOFCLEVRDataset("val")
@@ -35,12 +35,12 @@ train_log = train_model(
     loader,
     50,
     log_iter=50,
-    inital_test=False,
-    test_iter=100,
-    test=lambda x: [
-        ("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
-        ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),
-    ],
+    #inital_test=False,
+    #test_iter=100,
+    #test=lambda x: [
+    #    ("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
+    #    ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),
+    #],
 )
 
 name = "sort_of_clevr_" + format_time_precise()

### 2022-03-07 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Something is training - loss not particularly going down

@@ -1,8 +1,8 @@
 % We know that there are two objects in a four grid space. Two shapes possible, two colors possible.
 % The green cnn detects the position, and the shape --> x. If x < 4: Shape = rectangle. Else: shape = circle. (x modulo 4 = position)  
 
-nn(cnn_red,[X],Y,[0,1,2,3,4,5,6,7]) :: detect_state(red, X, Y_red).
-nn(cnn_green, [X], Y, [0,1,2,3,4,5,6,7]) :: detect_state(green, X, Y_green).
+nn(cnn_red,[X],Y_red,[0,1,2,3,4,5,6,7]) :: detect_state(red, X, Y_red).
+nn(cnn_green, [X], Y_green, [0,1,2,3,4,5,6,7]) :: detect_state(green, X, Y_green).
 
 shape(red, Img, rectangle) :-
     detect_state(red, Img, Y_red),

### 2022-03-07 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py
Test a bit further

@@ -33,10 +33,10 @@ model.set_engine(ExactEngine(model), cache=True)
 train_log = train_model(
     model,
     loader,
-    50,
+    1,
     log_iter=50,
-    #inital_test=False,
-    #test_iter=100,
+    inital_test=False,
+    test_iter=100,
     #test=lambda x: [
     #    ("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
     #    ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),

### 2022-03-08 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Some bugfixes: Working training process

@@ -53,33 +53,33 @@ class SORTOFCLEVRDataset(ImageDataset):
         if norelational_question[4] == 1: # Query about the shape of the object
             question = "shape"
             if norelational_answer == 2:
-                outcome = "rectangle"
+                outcome = 1 #"rectangle"
             elif norelational_answer == 3:
-                outcome = "circle"
+                outcome = 0 # "circle"
             else:
                 print("[ERROR] Wrong outcome for the shape")
         elif norelational_question[5] == 1: # Query about the horizontal position
             question = "horizontal_side"
             if norelational_answer == 0:
-                outcome = "left"
+                outcome = 1 # "left"
             elif norelational_answer == 1:
-                outcome = "right"
+                outcome = 0 # "right"
             else: 
                 print("[ERROR] Wrong outcome for the horizontal position")
         elif norelational_question[6] == 1: # Query about the vertical position
             question = "vertical_side"
             if norelational_answer == 0:
-                outcome = "bottom"
+                outcome = 1 # "bottom"
             elif norelational_answer == 1:
-                outcome = "top"
+                outcome = 0 # "top"
             else: 
                 print("[ERROR] Wrong outcome for the vertical position")
         else:
             print("[ERROR] No question specified")
 
         sub = {Term("image"): Term("tensor", Term(self.subset, Constant(i)))}
-        
-        return Query(Term(question, Term(sh), Term("image"), Term(outcome)), sub)
+        question = sh + "_" + question
+        return Query(Term(question, Term("image"), Constant(outcome)), sub)
 
     def __len__(self):
         return len(self.data)

### 2022-03-08 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl

@@ -4,33 +4,67 @@
 nn(cnn_red,[X],Y_red,[0,1,2,3,4,5,6,7]) :: detect_state(red, X, Y_red).
 nn(cnn_green, [X], Y_green, [0,1,2,3,4,5,6,7]) :: detect_state(green, X, Y_green).
 
-shape(red, Img, rectangle) :-
+red_shape(Img, Rectangle) :-
     detect_state(red, Img, Y_red),
-    Y_red < 4.
+    Y_red < 4,
+    Rectangle = 1.
+red_shape(Img, Rectangle) :-
+    detect_state(red, Img, Y_red),
+    Y_red >= 4,
+    Rectangle = 0.
 
-shape(green, Img, rectangle) :-
+green_shape(Img, Rectangle) :-
     detect_state(green, Img, Y_green),
-    Y_green < 4.
+    Y_green < 4, 
+    Rectangle = 1.
+green_shape(Img, Rectangle) :-
+    detect_state(green, Img, Y_green),
+    Y_green >= 4, 
+    Rectangle = 0.
 
-horizontal_side(red, Img, left) :-
+red_horizontal_side(Img, Left) :-
     detect_state(red, Img, Y_red),
     position(Y_red, Pos),
-    left_side(Pos).
-
-horizontal_side(green, Img, left) :-
-    detect_state(green, Img, Y_green),
-    position(Y_green, Pos),
-    left_side(Pos).
-
-vertical_side(red, Img, bottom) :-
+    left_side(Pos), 
+    Left = 1.
+red_horizontal_side(Img, Left) :-
     detect_state(red, Img, Y_red),
     position(Y_red, Pos),
-    bottom_side(Pos).
+    \+ left_side(Pos), 
+    Left = 0.
 
-vertical_side(green, Img, bottom) :-
+green_horizontal_side(Img, Left) :-
     detect_state(green, Img, Y_green),
     position(Y_green, Pos),
-    bottom_side(Pos).
+    left_side(Pos), 
+    Left = 1.
+green_horizontal_side(Img, Left) :-
+    detect_state(green, Img, Y_green),
+    position(Y_green, Pos),
+    \+ left_side(Pos), 
+    Left = 0.
+
+red_vertical_side(Img, Bottom) :-
+    detect_state(red, Img, Y_red),
+    position(Y_red, Pos),
+    bottom_side(Pos), 
+    Bottom = 1.
+red_vertical_side(Img, Bottom) :-
[…]

### 2022-03-08 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -35,8 +35,8 @@ train_log = train_model(
     loader,
     1,
     log_iter=50,
-    inital_test=False,
-    test_iter=100,
+    #initial_test=False,
+    #test_iter=100,
     #test=lambda x: [
     #    ("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
     #    ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),

### 2022-03-09 paper/initial_template.tex
Add the first writings for the paper

\documentclass[english]{sobraep}

\title{ENGLISH GUIDELINES FOR PUBLICATION - TITLE HERE \\(14 PT TYPE SIZE, UPPERCASE, BOLD, CENTERED)}

\author{First A. Author$^{1}$, Second B. Author$^{2}$ (Authors' Names, 12 pt Type Size, Centered Under the Title)\\
	\normalsize $^{1}$First Affiliation, City -- State, Country (10 pt Type Size, Centered Under the Authors' Names)\\
	\normalsize $^{2}$Second Affiliation (if necessary), City -- State, Country (10 pt Type Size, Centered Under the Authors' Names)\\
	\normalsize e-mail: author1@email.br, author2@email.com
}

\begin{document}

\maketitle

\begin{abstract}
	The objective of this document is to instruct the authors about the preparation of the manuscript for its submission to the Revista Eletrônica de Potência (Brazilian Power Electronics Journal).~The authors should use these guidelines for preparing both the initial and final versions of their paper. Additional information about procedures and guidelines for publication can be obtained directly with the editor, or through the web site https://mc04.manuscriptcentral.com/revistaep. This text was written according to these guidelines.
\end{abstract}

\begin{keywords}
	Authors shall provide a maximum of six keywords (in alphabetical order, capitalized, separated by commas) to help identify the major topics of the paper.
\end{keywords}

\let\thefootnote\relax\footnotetext{\hspace*{-5mm}This footnote will be used only by the Editor and Associate Editors.~The edition in this area is not permitted to the authors. This footnote must not be removed while editing the manuscript.}

\section*{NOMENCLATURE}

\symbolnomenclature{$P$}{Number of poles.}
\symbolnomenclature{$V_{qd}$}{Stator voltage \textit{dq} components.}
\symbolnomenclature{$I_{qd}$}{Stator current \textit{dq} components.}

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%Sections
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%Introduction

\section{INTRODUCTION}

The Brazilian Power Electronics Journal (Revista Eletrônica de Potência) is an appropriate media through which the SOBRAEP (Brazilian Power Electronics Society) members and experts in the field of Power Electronics may present and discuss their scientific and academic activities. Therefore, the Editorial Staff invites you to submit a full format paper in the field of Power Electronics, including advances in the state of the art, through theoretical and experimental results, as well as tutorial information on subjects of interest to the Society. In case the paper, or part of it, has been presented or published in any national or international journal or conference, it must be declared by the authors in the body of the paper (when and where).

Papers in Portuguese and English will be accepted. The texts submitted in Portuguese must include the title, the abstract and the keywords in English as well.

Authors must submit their manuscript electronically and follow the revision process through the https://mc04.manuscriptcentral.com/revistaep.~From this entry page, access can be obtained to all information required for the submission of a manuscript.

It should be noted that manuscripts must be submitted as an editable PDF document. Therefore, after editing your manuscript in agreement with these guidelines, a high-quality PDF file must be generated so it can be submitted through the https://mc04.manuscriptcentral.com/revistaep. Upon Final Acceptance of the manuscript, the strong requirement for publication is a final electronic version of the paper prepared in agreement with these guidelines. In addition, papers will only be published if the Copyright form available at the https://mc04.manuscriptcentral.com/revistaep is completed.

The main objective of the Introduction section is presenting the nature of the problem that is discussed in the paper, through an adequate literature review, and the contribution of the submitted manuscript.

If relevant, a Nomenclature section may be included immediately before the Introduction, with a list of variables used in the text. This item should not contain reference numeration, as well as items Acknowledgements, References and Biographies.

\subsection{Presentation of the Text}

Papers submitted for publication to the Brazilian Power Electronics Journal should have, preferably, eight pages or less. Papers with a higher number of pages must pay an overlength page charge (R\$ 150 per extra page for SOBRAEP Member corresponding author or R\$ 200 per extra page for SOBRAEP Non-Member corresponding author) before its publication, until the limit of four extra pages. Consequently, the maximum page limit is 12 pages.
The Brazilian Power Electronics Journal is an open access journal, having the following publication fees: SOBRAEP Professional Member corresponding author – free; SOBRAEP Student Member corresponding author – R\$ 50 per paper; SOBRAEP Non-Member corresponding author – R\$ 200 per paper.

Authors must use International System units (SI or MKS).

Authors of the paper must prepare it and then send it as a PDF file, through the https://mc04.manuscriptcentral.com/revistaep, in accordance with these guidelines. The manuscripts that do not follow these guidelines will be rejected, and the authors will be informed.

\subsection{Text Editing}
The manuscript must be prepared on A4 page format \linebreak (297 mm x 210 mm), as demonstrated in these guidelines.

The recommended word processor is Word for Windows.

\subsubsection{Type sizes} The type sizes specified in these guidelines are according to the word processor Word for Windows and the typeface must be Times New Roman. Table I shows the standard sizes of the characters that should be used in the different sections of the manuscript.

\subsubsection{Page Format} Set top and bottom margins to 25 mm, left margin to 18 mm and right margin to 12 mm.~The column is \linebreak 87 mm. The space between the two columns is 6 mm. Paragraph indentation is 4mm.

%Body Text
\begin{table}[H]
	\centering
	\caption{\textbf{Type Sizes}}
	\footnotesize
	\setlength{\tabcolsep}{5pt}
	\begin{tabular}{cccc}
		\toprule [1.3pt]	
		\multicolumn{4}{c}{ \textbf{Style} } \\
		\hline
		\multirow{2}{1.1cm}{\centering \textbf{Size (Points)}} & \multirow{2}{*}{\textbf{Normal}} &
		\multirow{2}{*}{\textbf{Bold}} & \multirow{2}{*}{\textbf{Italic}} \\
		&  &  & \\		
		\hline
		8 & Table texts &  &  \\
		\hline
		9 &  Figure captions  &  &  \\
		\hline
		\multirow{3}{*}{10} &
		\multirow{3}{2cm}{\centering Authors' affiliations; main text; references}  &
		\multirow{3}{2cm}{\centering Abstract text; keywords, table captions} &
		\multirow{3}{2.1cm}{\centering Abstract title and keywords title} \\
		& &  &  \\
		& &  &  \\
		\hline
		12 & Authors' names & &  \\
		\hline
		14 &  & Paper title & \vspace*{-0.8mm}\\
		\bottomrule[1.3pt]
	\end{tabular} \label{table:TableI}
\end{table}

\section{ORGANIZATION OF THE PAPER}

This section presents the main issues for editing the manuscript.

\subsection{General Organization}

The papers that shall be published in the Brazilian Power Electronics Journal must contain the following main sections:
1) Title; 2) Authors and Affiliations; 3) Abstract and Keywords; 4) Introduction; 5) Body Text; 6) Conclusions; \linebreak 7) References; 8) Biographies. This order must be respected, unless the authors add some items, such as: Nomenclature; Appendices and Acknowledgements.

Some comments regarding the main items of the manuscripts are presented below.

\subsubsection{Title}

The title of the paper should be as succinct as possible, stating the subject of the paper in a very clear manner. It should be centered at the top of the first page, in bold, type size 14 points, with the whole title in capital letters.

\subsubsection{Authors and affiliations}

Below the title (leaving one blank line), also centered, the name(s) of the author(s) must be included. The middle names may be abbreviated, but the first and last names must be written in their complete forms (type size 12 points). Immediately below the authors' names, their affiliations, with city, state and country, must be informed (type size 10 points).~The electronic addresses must be informed just below the affiliations (type size 10 points).

\subsubsection{Abstract and keywords}

This part is considered one of the most important in the whole paper. It is based on information in Abstract and Keywords that technical papers are indexed and stored in databases.

The Abstract should have no more than 200 words, indicating the main ideas contained in the paper, as well as procedures and obtained results. The Abstract should not be confused with the Introduction and should not have any abbreviations, references, figures, etc. For writing the Abstract, as well as the whole manuscript, you should use passive voice, e. g.,  ``... the experimental results show that...'' instead of ``...~the results we obtained show that...''.~The word Abstract must be written both in italic and in bold. The Abstract text should be in bold.

Keywords are index terms that identify the main topics of the paper. The term Keywords must be both in italic and bold. The Keywords themselves should be in bold.

\subsubsection{Introduction}

The Introduction must prepare the reader for the paper he/she will read, including a historical overview of the subject and also presenting the main contributions of the paper. The Introduction must not be similar to the Abstract and it is the first section of the paper to be numbered as a section.

\subsubsection{Body text}

The authors must organize the body text in various sections, which should contain important information about the proposal of the paper, facilitating its comprehension for readers.

\subsubsection{Conclusions}

The conclusions should be as clear as possible, highlighting the importance of the paper in the respective research area. The advantages and disadvantages of the proposed subject should be clearly emphasized, as well as the obtained results and possible applications.

\subsubsection{References}

The citation of references throughout the text should appear between square brackets, just before the punctuation mark at the end of the sentence in which the reference is inserted. Only the number of the references should be used, avoiding citations such as ``... according to the reference [2]...''.

Papers that were accepted for publication, but were not published yet, should also be in the references along with the citation ``in Press''.

Papers from journals and conferences must begin with the name of the authors (initials followed by the last name), followed by the title, journal or conference name (in italic), number of volume, pages, month and year of publication.

Regarding books, following the name of the authors (initials followed by last name), the title should be in italic, and then should come the publisher, number of edition and place and year of publication.

At the end of these guidelines, there is an example of how the references should be inserted~\cite{refbib1,refbib2,refbib3,refbib4,refbib5,refbib6,refbib7,refbib8}.

%\nocite{refbib1}
%\nocite{refbib2}
%\nocite{refbib3}
%\nocite{refbib4}
%\nocite{refbib5}
%\nocite{refbib6}
%\nocite{refbib7}
%\nocite{refbib8}

\subsubsection{Biographies}

The biographies of the authors should appear in the same order as in the beginning of the paper and should basically contain the following items:
\begin{itemize}
	\item Full name (in bold and underlined);
	\item Place and year of undergraduation and graduation conclusions;
	\item Professional experience (Institutions and companies in which they have worked, number of patents obtained, areas of expertise, relevant scientific activities, scientific societies in which they are members, etc.). \newline
\end{itemize}

In case additional items are used, such as Nomenclature, Appendices and Acknowledgements, the following instructions should be considered:

\subsubsection{Nomenclature}

The nomenclature consists of the definition of quantities and symbols used throughout the paper. Its inclusion is not mandatory and this item must not be numbered. If this item is included, it should precede the Introduction. In case the authors do not include this item, the  definition of quantities and symbols must occur during the text, right after they appear. In the beginning of these guidelines there is an example of this optional item.

\subsubsection{Acknowledgements and appendices}

The acknowledgements to any collaborators, as well as appendices, do not receive any numeration and should be at the end of the text, before the references. At the end of this text there is an example of this optional item.

On the last page of the paper, the authors should distribute the contents evenly, using both columns, in a way that both end in a parallel manner.

\subsection{Organization of the Sections of the Paper}

The organization of the manuscript in titles and subtitles is important to divide it in sections, which help the reader to find subjects of interest in the paper. They also help the authors to develop their paper in an orderly form. The paper can be organized in primary, secondary and tertiary sections.

The primary sections are the titles of the actual sections. They are written in capital letters in the center of the column separated by a blank line above and another one below them, and sequential Roman numerals should be used.

The secondary sections are the subtitles of the sections. Just the first letter of each word of the section should be written with a capital letter. It should be located at the left part of the column being separated by a blank line above from the rest of the text. The designation of the secondary sections is done with letters in uppercase form, followed by a dot. They should be in italic.

The tertiary sections are subdivisions of the secondary sections. Only the first letter of the first word of the section should be a capital letter. The designation of the tertiary sections should be done with Arabic numerals, followed by parentheses. They should be in italic.

\section{OTHER INSTRUCTIONS}

\subsection{Editorial Rules}

For papers with multiple authors, it is necessary to inform the order of presentation of the authors and filling out the Copyright form at the https://mc04.manuscriptcentral.com/revistaep, authorizing the publication of the paper.

The Brazilian Power Electronics Journal should be considered source of original publication. It reserves its right to make normative, spelling and grammatical modifications in the original files, but respecting the style of the authors. The final versions cannot be sent to the authors.

The published papers will become property of the Brazilian Power Electronics Journal, and its total or partial reprinting must be authorized by SOBRAEP.

Figures, tables and equations should follow the following guidelines.

\subsection{Figures and Tables}

Tables and figures (drawings or pictures) should be inserted in the text right after they are mentioned for the first time, as long as they fit the size of the columns; if necessary, use the whole page. Figures resolution should be at least 300 dpi and vector files should be preferably used for better print quality. Table captions should be above the tables and figure captions should be below the figures. The tables should have titles and they are designated by the word Table, being numbered in sequence by Roman numerals. Table captions must be centered and in bold.

Figures also need captions and they are designated by Figure in the text (Fig. in the caption itself), numbered with Arabic numerals in a sequenced manner, left- and right- justified, as shown in the example. The designation of the parts of a figure is done by adding lowercase letters to the numbers of the figures starting with the letter a, e.g. Figure 1(a).

\begin{figure}[H]
	\includegraphics[scale=1]{figura.eps}
	\centering
	\caption{Magnetization as a function of applied field. (Note that ``Fig.'' is abbreviated and there is a period after the figure number followed by two spaces.)}
	\label{fig:fig1}
\end{figure}

To better understand graphs, the definition of their axes should be done with words not letters, except when referring to waveforms and phase planes. The units should be between parentheses. For example, use the denomination ``Magnetization (A/m)'', instead of ``M (A/m)''.

Figures and tables should be positioned preferably in the beginning or the end of the column, avoiding putting them in the middle. Avoid tables and figures whose sizes exceed the size of the columns. The figures should preferentially be in black, with a white background, since the printed version of the journal is in black and white. Their lines should be thick, so the impression is readable.

\subsection{Abbreviations and Acronyms}
Abbreviations and acronyms must be defined the first time they are used in the text, e.g. ``... Pulse-Width Modulation (PWM)...''.

\subsection{Equations}
Number equations consecutively with equation numbers in parentheses flush with the right margin, as in (1). The equations should be written in a compact form, centered in the column. If a nomenclature section is not included in the beginning of the text, the quantities should be defined right after the equation, such as:
\begin{equation}
	\Delta I_{L}=I_{o}+\frac{\sqrt{3}}{2}\frac{V_{i}}{Z}
\end{equation}
where:

\symboldescription{$\Delta I_{L}$}{resonant inductor peak current;}
\symboldescription{$I_o$}{load current;}
\symboldescription{$V_i$}{source voltage;}
\symboldescription{$Z$}{characteristic impedance.}

\section{CONCLUSIONS}
This paper was fully written in accordance with the guidelines for submissions of papers in English.

\section*{ACKNOWLEDGEMENTS}
The authors thank John Doe for the collaboration of preparing this paper. This Project was financed by the CNPq (xxyyzz process).

\bibliographystyle{bib_sobraep}
\bibliography{ref_sobraep}

\balance

\section*{BIOGRAPHIES}
\noindent\textbf{\underline{John Doe}}, born in 02/30/1960 in Somewhere is an electrical engineer (1983), master (1985) and doctor in Electrical Engineer (1990) with the University of Y.

Between 1990 and 1995 he was the coordinator of Laboratory X. He is currently a full professor at University of Y. His areas of interest are: power electronics, electricity conversion quality, electronic control systems and electrical machine actuation.

Dr. Doe is member of the SOBRAEP, SBA and IEEE. Between 1998 and 2000, he was editor of the Brazilian \linebreak Power Electronics Journal.

\end{document}

### 2022-03-09 paper/paper.tex
Add the first writings for the paper

--- 2022-03-09 paper/initial_template.tex
@@
 
-\title{ENGLISH GUIDELINES FOR PUBLICATION - TITLE HERE \\(14 PT TYPE SIZE, UPPERCASE, BOLD, CENTERED)}
+\title{Visual Question Answering with DeepProbLog}
 
-\author{First A. Author$^{1}$, Second B. Author$^{2}$ (Authors' Names, 12 pt Type Size, Centered Under the Title)\\
-	\normalsize $^{1}$First Affiliation, City -- State, Country (10 pt Type Size, Centered Under the Authors' Names)\\
-	\normalsize $^{2}$Second Affiliation (if necessary), City -- State, Country (10 pt Type Size, Centered Under the Authors' Names)\\
-	\normalsize e-mail: author1@email.br, author2@email.com
+\author{Jorrit Willaert$^{1}$ \\
+	\normalsize $^{1}$Catholic University of Leuven, Leuven -- Belgium \\
+	\normalsize e-mail: jorrit.willaert@student.kuleuven.be
 }
@@
 \begin{abstract}
-	The objective of this document is to instruct the authors about the preparation of the manuscript for its submission to the Revista Eletrônica de Potência (Brazilian Power Electronics Journal).~The authors should use these guidelines for preparing both the initial and final versions of their paper.
-Additional information about procedures and guidelines for publication can be obtained directly with the editor, or through the web site https://mc04.manuscriptcentral.com/revistaep.
-This text was written according to these guidelines.
+	TODO
 \end{abstract}
@@
 \begin{keywords}
-	Authors shall provide a maximum of six keywords (in alphabetical order, capitalized, separated by commas) to help identify the major topics of the paper.
+	Neuro Symbolic AI, Visual Question Answering, DeepProbLog, Problog, Convolutional Neural Networks
 \end{keywords}
 
-\let\thefootnote\relax\footnotetext{\hspace*{-5mm}This footnote will be used only by the Editor and Associate Editors.~The edition in this area is not permitted to the authors.
+%\let\thefootnote\relax\footnotetext{\hspace*{-5mm}This footnote will be used only by the Editor and Associate Editors.~The edition in this area is not permitted to the authors.
 This footnote must not be removed while editing the manuscript.}
 
-\section*{NOMENCLATURE}
+%\section*{NOMENCLATURE}
 
-\symbolnomenclature{$P$}{Number of poles.}
-\symbolnomenclature{$V_{qd}$}{Stator voltage \textit{dq} components.}
-\symbolnomenclature{$I_{qd}$}{Stator current \textit{dq} components.}
+%\symbolnomenclature{$P$}{Number of poles.}
+%\symbolnomenclature{$V_{qd}$}{Stator voltage \textit{dq} components.}
+%\symbolnomenclature{$I_{qd}$}{Stator current \textit{dq} components.}
 
@@
 \section{INTRODUCTION}
+The Neuro Symbolic AI community is growing rapidly, indicating that people start to recognize the value of the field.
+The Neuro Symbolic AI field is interested in building a bridge between the robustness of probabilistic knowledge, with the well-known popularity and proven strengths of deep neural networks.
+DeepProbLog offers this ability, by using both the strengths of neural networks (i.e.
+system 1, typical subconscious tasks such as visual recognition, the processing of languages, \dots), along with the strengths of rule-based probabilistic systems (i.e.
+system 2, slow, sequential thinking such as the derivation of a proof).
 
-The Brazilian Power Electronics Journal (Revista Eletrônica de Potência) is an appropriate media through which the SOBRAEP (Brazilian Power Electronics Society) members and experts in the field of Power Electronics may present and discuss their scientific and academic activities.
-Therefore, the Editorial Staff invites you to submit a full format paper in the field of Power Electronics, including advances in the state of the art, through theoretical and experimental results, as well as tutorial information on subjects of interest to the Society.
-In case the paper, or part of it, has been presented or published in any national or international journal or conference, it must be declared by the authors in the body of the paper (when and where).
-
-Papers in Portuguese and English will be accepted. The texts submitted in Portuguese must include the title, the abstract and the keywords in English as well.
-
-Authors must submit their manuscript electronically and follow the revision process through the https://mc04.manuscriptcentral.com/revistaep.~From this entry page, access can be obtained to all information required for the submission of a manuscript.
-
-It should be noted that manuscripts must be submitted as an editable PDF document.
-Therefore, after editing your manuscript in agreement with these guidelines, a high-quality PDF file must be generated so it can be submitted through the https://mc04.manuscriptcentral.com/revistaep.
-Upon Final Acceptance of the manuscript, the strong requirement for publication is a final electronic version of the paper prepared in agreement with these guidelines.
-In addition, papers will only be published if the Copyright form available at the https://mc04.manuscriptcentral.com/revistaep is completed.
-
-The main objective of the Introduction section is presenting the nature of the problem that is discussed in the paper, through an adequate literature review, and the contribution of the submitted manuscript.
-
-If relevant, a Nomenclature section may be included immediately before the Introduction, with a list of variables used in the text.
-This item should not contain reference numeration, as well as items Acknowledgements, References and Biographies.
+This paper elaborates on an application that requires both systems to be used, namely Visual Question Answering.
+System 1 will be required in order to gain an understanding of the image under investigation, with in particular their shapes and colors.
+System 2, on the other hand, will use this extracted information for deriving certain properties of objects\footnote{For example, finding the shape of the green object, or deriving if it is located on the left hand side of the image.}, or even for capturing the relations\footnote{Here, one could think of deriving if an object is located to the left of another object, or also for finding the number of circles in the image.} between the objects.
 
@@
 
-At the end of these guidelines, there is an example of how the references should be inserted~\cite{refbib1,refbib2,refbib3,refbib4,refbib5,refbib6,refbib7,refbib8}.
+At the end of these guidelines, there is an example of how the references should be inserted~%\cite{refbib1,refbib2,refbib3,refbib4,refbib5,refbib6,refbib7,refbib8}.
 
@@
 \begin{figure}[H]
-	\includegraphics[scale=1]{figura.eps}
+%	\includegraphics[scale=1]{figura.eps}
 	\centering

### 2022-03-09 paper/paper.tex
Add bibs

@@
 The Neuro Symbolic AI field is interested in building a bridge between the robustness of probabilistic knowledge, with the well-known popularity and proven strengths of deep neural networks.
-DeepProbLog offers this ability, by using both the strengths of neural networks (i.e.
+DeepProbLog \cite{deepproblog} offers this ability, by using both the strengths of neural networks (i.e.
 system 1, typical subconscious tasks such as visual recognition, the processing of languages, \dots), along with the strengths of rule-based probabilistic systems (i.e.
@@
 
-\subsection{Presentation of the Text}
-
-Papers submitted for publication to the Brazilian Power Electronics Journal should have, preferably, eight pages or less.
-Papers with a higher number of pages must pay an overlength page charge (R\$ 150 per extra page for SOBRAEP Member corresponding author or R\$ 200 per extra page for SOBRAEP Non-Member corresponding author) before its publication, until the limit of four extra pages.
-Consequently, the maximum page limit is 12 pages.
-The Brazilian Power Electronics Journal is an open access journal, having the following publication fees: SOBRAEP Professional Member corresponding author – free; SOBRAEP Student Member corresponding author – R\$ 50 per paper; SOBRAEP Non-Member corresponding author – R\$ 200 per paper.
-
-Authors must use International System units (SI or MKS).
-
-Authors of the paper must prepare it and then send it as a PDF file, through the https://mc04.manuscriptcentral.com/revistaep, in accordance with these guidelines.
-The manuscripts that do not follow these guidelines will be rejected, and the authors will be informed.
-
-\subsection{Text Editing}
-The manuscript must be prepared on A4 page format \linebreak (297 mm x 210 mm), as demonstrated in these guidelines.
-
-The recommended word processor is Word for Windows.
-
-\subsubsection{Type sizes} The type sizes specified in these guidelines are according to the word processor Word for Windows and the typeface must be Times New Roman.
-Table I shows the standard sizes of the characters that should be used in the different sections of the manuscript.
-
-\subsubsection{Page Format} Set top and bottom margins to 25 mm, left margin to 18 mm and right margin to 12 mm.~The column is \linebreak 87 mm.
-The space between the two columns is 6 mm.
-Paragraph indentation is 4mm.
-
-%Body Text
-\begin{table}[H]
-	\centering
-	\caption{\textbf{Type Sizes}}
-	\footnotesize
-	\setlength{\tabcolsep}{5pt}
-	\begin{tabular}{cccc}
-		\toprule [1.3pt]	
-		\multicolumn{4}{c}{ \textbf{Style} } \\
-		\hline
-		\multirow{2}{1.1cm}{\centering \textbf{Size (Points)}} & \multirow{2}{*}{\textbf{Normal}} &
-		\multirow{2}{*}{\textbf{Bold}} & \multirow{2}{*}{\textbf{Italic}} \\
-		&  &  & \\		
-		\hline
-		8 & Table texts &  &  \\
-		\hline
-		9 &  Figure captions  &  &  \\
-		\hline
-		\multirow{3}{*}{10} &
-		\multirow{3}{2cm}{\centering Authors' affiliations; main text; references}  &
-		\multirow{3}{2cm}{\centering Abstract text; keywords, table captions} &
-		\multirow{3}{2.1cm}{\centering Abstract title and keywords title} \\
-		& &  &  \\
-		& &  &  \\
-		\hline
-		12 & Authors' names & &  \\
-		\hline
-		14 &  & Paper title & \vspace*{-0.8mm}\\
-		\bottomrule[1.3pt]
-	\end{tabular} \label{table:TableI}
-\end{table}
-
 \section{ORGANIZATION OF THE PAPER}
+%TODO
 
@@
 \bibliographystyle{bib_sobraep}
-\bibliography{ref_sobraep}
+\bibliography{Capita_Selecta_AI_Initial_Idea}
 
@@
 
-\section*{BIOGRAPHIES}
-\noindent\textbf{\underline{John Doe}}, born in 02/30/1960 in Somewhere is an electrical engineer (1983), master (1985) and doctor in Electrical Engineer (1990) with the University of Y.
-
-Between 1990 and 1995 he was the coordinator of Laboratory X.
-He is currently a full professor at University of Y.
-His areas of interest are: power electronics, electricity conversion quality, electronic control systems and electrical machine actuation.
-
-Dr. Doe is member of the SOBRAEP, SBA and IEEE. Between 1998 and 2000, he was editor of the Brazilian \linebreak Power Electronics Journal.
-
 \end{document}

### 2022-03-09 paper/paper.tex
Write some more for literature survey

@@
 
+\section{LITERATURE SURVEY}
+The application focuses on Visual Question Answering (VQA), for which huge datasets are present, along with very sophisticated methods.
+The best known dataset for VQA is CLEVR \cite{clevr_dataset}, which contains 100k images with one million questions.
+An example image is given in Figure \ref{fig:sample_image_clevr}, while example questions are:
+\begin{itemize}
+    \item Are there an equal number of large things and metal spheres?
+    \item What size is the cylinder that is left of the brown metal thing that is left of the big sphere?
+    \item How many objects are either small cylinders or metal things?
+\end{itemize}
+
+\begin{figure}[H]
+    \begin{center}
+    \includegraphics[width=0.3\textwidth]{clevr.jpg}
+    \captionsetup{justification=centering}
+    \caption{A sample image from the CLEVR dataset \cite{clevr_dataset}}
+    \label{fig:sample_image_clevr}
+    \end{center}
+\end{figure}
+
+Clearly, both system 1 and system 2 are actively used when answering these questions.
+One could wonder if neural networks alone could answer these questions without having an explicit system 2 encoding (i.e.
+the rule based knowledge base).
+Intuitively, it makes sense that if certain facts of the world are known\footnote{They can be encoded, e.g.
+counting the number of spheres is simply a matter of detecting all the spheres in the image, after which a mathematical summation is a statement in the knowledge base.}, learning can proceed much more quickly\footnote{Not to say that learning might even be impossible if a lot of background knowledge is required.}.
+Seen from an optimization viewpoint, errors made during prediction in this setup can be targeted exactly, which makes the optimization process also more targeted, and hence more efficient.
+Finally, this paper also provides evidence for these statements, since in Section \ref{comparison_with_CNN} % TODO ref here
+the comparison between this implementation with DeepProbLog is made with a purely CNN based approach. % TODO is this the case?
+
+\section{COMPARISONS WITH PURE SYSTEM 1 APPROACHES}
+\label{comparison_with_CNN}
+
 \section{ORGANIZATION OF THE PAPER}
-%TODO
+%TODO. Put this above the literature study
 

### 2022-03-09 paper/paper.tex
Write about Sort-Of-CLEVR dataset

@@
 Seen from an optimization viewpoint, errors made during prediction in this setup can be targeted exactly, which makes the optimization process also more targeted, and hence more efficient.
-Finally, this paper also provides evidence for these statements, since in Section \ref{comparison_with_CNN} % TODO ref here
-the comparison between this implementation with DeepProbLog is made with a purely CNN based approach. % TODO is this the case?
+Finally, this paper also provides evidence for these statements, since in Section \ref{comparison_with_CNN}, the comparison between a VQA implementation with DeepProbLog is made with a purely CNN based approach.
+% TODO is this the case?
+
+This paper is based on the CLEVR dataset, but uses however a much more simplified version.
+In essence, it is almost like the Sort-Of-CLEVR dataset \cite{sort_of_clevr_dataset}.
+This Sort-Of-CLEVR dataset contains images such as in Figure \ref{fig:sample_image_sort_of_clevr}, while asking questions such as:
+\begin{itemize}
+    \item Non-relational questions: the shape, horizontal or vertical location of an object.
+    \item Relational questions: shape of the closest/furthest object to the object under investigation, or the number of objects with the same shape.
+\end{itemize}
+
+\begin{figure}[H]
+    \begin{center}
+    \includegraphics[width=0.3\textwidth]{sort_of_clevr.png}
+    \captionsetup{justification=centering}
+    \caption{A sample image from the CLEVR dataset \cite{sort_of_clevr_dataset}}
+    \label{fig:sample_image_sort_of_clevr}
+    \end{center}
+\end{figure}
+
+As explained earlier, both system 1 and system 2 are required for these types of VQA's.
+
+Finally, since this application uses DeepProbLog, quite some time was spent in digesting the DeepProbLog paper \cite{deepproblog}, along with understanding the  examples provided in the code repository \cite{deepproblog_code}.
 

### 2022-03-09 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py
Change some experimental settings

@@ -34,13 +34,13 @@ train_log = train_model(
     model,
     loader,
     1,
-    log_iter=50,
+    log_iter=2,
     #initial_test=False,
-    #test_iter=100,
-    #test=lambda x: [
-    #    ("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
-    #    ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),
-    #],
+    test_iter=3,
+    test=lambda x: [
+        ("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
+        ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),
+    ],
 )
 
 name = "sort_of_clevr_" + format_time_precise()

### 2022-03-09 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py
Nice logging

@@ -10,7 +10,10 @@ from deepproblog.evaluate import get_confusion_matrix
 from deepproblog.train import train_model
 from deepproblog.dataset import DataLoader
 from data.data import SORTOFCLEVRDataset
+import random
 
+random.seed(0)
+#np.random.seed(args.seed)
 
 cnn_red = CNNNetwork(out_size=8)
 cnn_green = CNNNetwork(out_size=8)
@@ -29,17 +32,20 @@ model.add_tensor_source("train", train_dataset)
 model.add_tensor_source("val", val_dataset)
 model.add_tensor_source("test", test_dataset)
 model.set_engine(ExactEngine(model), cache=True)
+test_accs = []
+train_accs = []
 
 train_log = train_model(
     model,
     loader,
     1,
-    log_iter=2,
+    log_iter=1,
     #initial_test=False,
-    test_iter=3,
+    test_iter=50,
     test=lambda x: [
-        ("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
+        #("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
         ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),
+        #("Train_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy())
     ],
 )
 

### 2022-03-09 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py
Parameters to be used for a graph - only with nonbinary questions

@@ -39,9 +39,9 @@ train_log = train_model(
     model,
     loader,
     1,
-    log_iter=1,
+    log_iter=3,
     #initial_test=False,
-    test_iter=50,
+    test_iter=3,
     test=lambda x: [
         #("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
         ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),

### 2022-03-09 relational-networks/sort_of_clevr_generator.py
Generalize data generation for train, test and val set

@@ -18,9 +18,6 @@ parser.add_argument('--t-subtype', type=int, default=-1,
                     help='Force ternary questions to be of a given type')
 args = parser.parse_args()
 
-random.seed(args.seed)
-np.random.seed(args.seed)
-
 IMG_SIZE = 100
 NUM_OBJECTS = 2
 WIDTH = 2
@@ -41,7 +38,7 @@ class Object:
         self.shape = shape
 
 size = 5
-question_size = len(colors) + 2 + 3 ## (number of colors for one-hot vector of color), 3 for question type (nonbinary VS binary), 3 for question subtype
+question_size = len(colors) + 2 + 3 ## (number of colors for one-hot vector of color), 2 for question type (nonbinary VS binary), 3 for question subtype
 q_type_idx = len(colors)
 sub_q_type_idx = len(colors) + 2
 """Answer : [yes, no, rectangle, circle, r, g, b, o, k, y]"""
@@ -132,30 +129,34 @@ def build_binary_questions(objects):
         color = random.randint(0, len(colors) - 1)
         question[color] = 1
         question[q_type_idx+1] = 1
-        subtype = random.randint(0,2)
+        #subtype = random.randint(0,2)
+        subtype = 2
         question[subtype+sub_q_type_idx] = 1
         binary_questions.append(question)
 
         if subtype == 0:
             """closest-to->rectangle/circle"""
-            my_obj = objects[color]
-            dist_list = [((np.subtract(pos_to_coor(my_obj.position), pos_to_coor(obj.position))) ** 2).sum() for obj in objects]
-            dist_list[dist_list.index(0)] = float('inf') # The distance to the element itself should not be considered
-            closest = dist_list.index(min(dist_list))
-            if objects[closest].shape == 'square':
-                answer = 2
-            else:
-                answer = 3
+            pass
+            # Skipped
+            #my_obj = objects[color]
+            #dist_list = [((np.subtract(pos_to_coor(my_obj.position), #pos_to_coor(obj.position))) ** 2).sum() for obj in objects]
+            #dist_list[dist_list.index(0)] = float('inf') # The distance to the element itself should not be considered
+            #closest = dist_list.index(min(dist_list))
+            #if objects[closest].shape == 'square':
+            #    answer = 2
+            #else:
+            #    answer = 3
                 
         elif subtype == 1:
             """furthest-from->rectangle/circle"""
-            my_obj = objects[color]
[…]

### 2022-03-09 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Implement some things for binary questions - problem with accuracy (not learning: 0.5)

@@ -5,6 +5,8 @@ import torchvision.transforms as transforms
 from deepproblog.dataset import ImageDataset
 from deepproblog.query import Query
 from problog.logic import Term, Constant
+import random
+random.seed(0)
 
 path = os.path.dirname(os.path.abspath(__file__))
 
@@ -32,55 +34,66 @@ class SORTOFCLEVRDataset(ImageDataset):
 
     def to_query(self, i):
         norelational_question, norelational_answer, binary_question, binary_answer = self.data[i]
-        # Begin with nonrelational 
-        sh = None
-        if norelational_question[0] == 1: # Question about red object
-            sh = "red"
-        elif norelational_question[1] == 1:
-            sh = "green"
-        else:
-            print("[ERROR] No object specified")
-        
-        if norelational_question[2] == 1: # Nonbinary question
-            pass
-        elif norelational_question[3] == 1: # Binary question
-            print("Not yet defined")
-        else:
-            print("[ERROR] No type of question specified")
-        
-        question = None
-        outcome = None
-        if norelational_question[4] == 1: # Query about the shape of the object
-            question = "shape"
-            if norelational_answer == 2:
-                outcome = 1 #"rectangle"
-            elif norelational_answer == 3:
-                outcome = 0 # "circle"
+        if random.random() < 0: # Select nonbinary questions with 50% chance (TODO: set this back to 0.5)
+            sh = None
+            if norelational_question[0] == 1: # Question about red object
+                sh = "red"
+            elif norelational_question[1] == 1:
+                sh = "green"
             else:
-                print("[ERROR] Wrong outcome for the shape")
-        elif norelational_question[5] == 1: # Query about the horizontal position
-            question = "horizontal_side"
-            if norelational_answer == 0:
-                outcome = 1 # "left"
-            elif norelational_answer == 1:
-                outcome = 0 # "right"
-            else: 
-                print("[ERROR] Wrong outcome for the horizontal position")
-        elif norelational_question[6] == 1: # Query about the vertical position
-            question = "vertical_side"
-            if norelational_answer == 0:
-                outcome = 1 # "bottom"
-            elif norelational_answer == 1:
-                outcome = 0 # "top"
-            else: 
-                print("[ERROR] Wrong outcome for the vertical position")
-        else:
-            print("[ERROR] No question specified")
+                print("[ERROR] No object specified")
+            
+            assert(norelational_question[2] == 1 and norelational_question[3] == 0) # Nonbinary question
+            
+            question = None
+            outcome = None
[…]

### 2022-03-09 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl

@@ -66,6 +66,29 @@ green_vertical_side(Img, Bottom) :-
     \+ bottom_side(Pos), 
     Bottom = 0.
 
+% Note: Do not need red_number_of_shapes and green_number_of_shapes right now. But has been added since this will be necessary later (implementation with same_shape will have to change too though)
+red_number_of_shapes(Img, Count) :-
+    detect_state(red, Img, Y_red),
+    detect_state(green, Img, Y_green),
+    same_shape(Y_red, Y_green),
+    Count = 2.
+red_number_of_shapes(Img, Count) :-
+    detect_state(red, Img, Y_red),
+    detect_state(green, Img, Y_green),
+    \+ same_shape(Y_red, Y_green),
+    Count = 1.
+
+green_number_of_shapes(Img, Count) :-
+    detect_state(red, Img, Y_red),
+    detect_state(green, Img, Y_green),
+    same_shape(Y_red, Y_green),
+    Count = 2.
+green_number_of_shapes(Img, Count) :-
+    detect_state(red, Img, Y_red),
+    detect_state(green, Img, Y_green),
+    \+ same_shape(Y_red, Y_green),
+    Count = 1.
+
 position(Out, Pos) :-
     Pos is Out mod 4.
 
@@ -80,3 +103,6 @@ bottom_side(Out) :-
 to_coor(Out, X, Y) :-
     X is Out mod 2, 
     Y is Out // 2.
+
+same_shape(Y1, Y2) :-
+    (Y1 >= 4, Y2 >= 4) ; (Y1 < 4, Y2 < 4).

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py
Training does succeed - simply wait long enough

@@ -40,8 +40,8 @@ train_log = train_model(
     loader,
     1,
     log_iter=3,
-    #initial_test=False,
-    test_iter=3,
+    initial_test=False,
+    test_iter=50,
     test=lambda x: [
         #("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
         ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Set the probability of chosing for a non-binary/binary question back to 0.5

@@ -34,7 +34,7 @@ class SORTOFCLEVRDataset(ImageDataset):
 
     def to_query(self, i):
         norelational_question, norelational_answer, binary_question, binary_answer = self.data[i]
-        if random.random() < 0: # Select nonbinary questions with 50% chance (TODO: set this back to 0.5)
+        if random.random() < 0.5: # Select nonbinary questions with 50% chance
             sh = None
             if norelational_question[0] == 1: # Question about red object
                 sh = "red"

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Start by generalizing data generation for other sizes then 2 x 2

@@ -9,6 +9,7 @@ import random
 random.seed(0)
 
 path = os.path.dirname(os.path.abspath(__file__))
+size = "2x2"
 
 transform = transforms.Compose(
     [transforms.ToTensor(), transforms.Normalize((0.5, 0.5, 0.5), (0.5, 0.5, 0.5))]
@@ -19,7 +20,7 @@ class SORTOFCLEVRDataset(ImageDataset):
         self,
         subset,
     ):
-        super().__init__("{}/{}/images".format(path, subset), transform=transform)
+        super().__init__("{}/{}}/{}/images".format(path, size, subset), transform=transform)
         self.data = []
         self.subset = subset
         with open("{}/{}/{}.csv".format(path, subset, subset)) as f:

### 2022-03-10 relational-networks/sort_of_clevr_generator.py

@@ -183,8 +183,9 @@ def build_dataset_item():
     return dataset
 
 if __name__ == "__main__":
+    size = str(WIDTH) + "x" + str(WIDTH)
     for (dataset, num, seed) in [("train", 10000, 0), ("val", 2000, 1), ("test", 2000, 2)]:
-        path = '../deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/' + dataset
+        path = '../deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/' + size + '/' + dataset
 
         if not os.path.exists(path + '/images'):
             # Create a new directory because it does not exist 
@@ -206,5 +207,5 @@ if __name__ == "__main__":
                 for q in questions_binary_relations:
                     array.append(q)
                 array.append(answer_binary_relations)
-                cv2.imwrite('../deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/' + dataset + '/images/' + str(i) + '.png', img)
+                cv2.imwrite('../deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/' + size + '/' + dataset + '/images/' + str(i) + '.png', img)
                 writer.writerow(array)

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Bugfix for size

@@ -20,10 +20,10 @@ class SORTOFCLEVRDataset(ImageDataset):
         self,
         subset,
     ):
-        super().__init__("{}/{}}/{}/images".format(path, size, subset), transform=transform)
+        super().__init__("{}/{}/{}/images".format(path, size, subset), transform=transform)
         self.data = []
         self.subset = subset
-        with open("{}/{}/{}.csv".format(path, subset, subset)) as f:
+        with open("{}/{}/{}/{}.csv".format(path, size, subset, subset)) as f:
             for line in f:
                 norelational_question, norelational_answer, binary_question, binary_answer = \
                     [(l.rstrip('\n')[1:-1]).split() for l in line.split(",")]

### 2022-03-10 relational-networks/sort_of_clevr_generator.py
Generalize generator for other sizes - generated 4 x 4

@@ -19,17 +19,18 @@ parser.add_argument('--t-subtype', type=int, default=-1,
 args = parser.parse_args()
 
 IMG_SIZE = 100
-NUM_OBJECTS = 2
-WIDTH = 2
+NUM_OBJECTS = 4
+WIDTH = 4
 
 colors = [
     (0,0,255),##r
     (0,255,0),##g
-    #(255,0,0),##b
-    #(0,156,255),##o
-    #(128,128,128),##k
-    #(0,255,255)##y
+    (255,0,0),##b
+    (0,156,255),##o
+    (128,128,128),##k
+    (0,255,255)##y
 ]
+used_colors = colors[0:NUM_OBJECTS]
 
 class Object: 
     def __init__(self, color: tuple, position: int, shape: String):
@@ -37,19 +38,12 @@ class Object:
         self.position = position
         self.shape = shape
 
-size = 5
-question_size = len(colors) + 2 + 3 ## (number of colors for one-hot vector of color), 2 for question type (nonbinary VS binary), 3 for question subtype
-q_type_idx = len(colors)
-sub_q_type_idx = len(colors) + 2
+question_size = NUM_OBJECTS + 2 + 3 ## (number of colors for one-hot vector of color), 2 for question type (nonbinary VS binary), 3 for question subtype
+q_type_idx = NUM_OBJECTS
+sub_q_type_idx = NUM_OBJECTS + 2
 """Answer : [yes, no, rectangle, circle, r, g, b, o, k, y]"""
 
 nb_questions = 1
-dirs = './data'
-
-try:
-    os.makedirs(dirs)
-except:
-    print('directory {} already exists'.format(dirs))
 
 def generate_position(objects):
     while True:
@@ -72,7 +66,7 @@ def pos_to_coor(position):
 def build_one_image():
     objects = []
     img = np.ones((IMG_SIZE, IMG_SIZE, 3)) * 255
-    for color in colors:
+    for color in used_colors:
         position = generate_position(objects)
         x_coor, y_coor = pos_to_coor(position)
         if random.random()<0.5:
@@ -91,7 +85,7 @@ def build_nonrelational_questions(objects):
     nonrelational_answers = []
     for _ in range(nb_questions):
         question = np.zeros((question_size))
-        color = random.randint(0, len(colors) - 1)
+        color = random.randint(0, len(used_colors) - 1)
         question[color] = 1
         question[q_type_idx] = 1
         subtype = random.randint(0,2)
[…]

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Make changes for generalizing data.py

@@ -9,7 +9,8 @@ import random
 random.seed(0)
 
 path = os.path.dirname(os.path.abspath(__file__))
-size = "2x2"
+num = 2
+size = str(num) + 'x' + str(num)
 
 transform = transforms.Compose(
     [transforms.ToTensor(), transforms.Normalize((0.5, 0.5, 0.5), (0.5, 0.5, 0.5))]
@@ -35,20 +36,21 @@ class SORTOFCLEVRDataset(ImageDataset):
 
     def to_query(self, i):
         norelational_question, norelational_answer, binary_question, binary_answer = self.data[i]
-        if random.random() < 0.5: # Select nonbinary questions with 50% chance
+        if random.random() < 0.75: # Select nonbinary questions with 75% chance (three questions nonbinary / one question binary)
             sh = None
-            if norelational_question[0] == 1: # Question about red object
-                sh = "red"
-            elif norelational_question[1] == 1:
-                sh = "green"
-            else:
+            for i, color in enumerate(["red", "green", "blue", "orange", "grey", "yellow"]):
+                if norelational_question[i] == 1: # Question about red object
+                    sh = color
+                if i == num - 1:
+                    break
+            if sh is None:
                 print("[ERROR] No object specified")
             
-            assert(norelational_question[2] == 1 and norelational_question[3] == 0) # Nonbinary question
+            assert(norelational_question[num] == 1 and norelational_question[num + 1] == 0) # Nonbinary question
             
             question = None
             outcome = None
-            if norelational_question[4] == 1: # Query about the shape of the object
+            if norelational_question[num + 2] == 1: # Query about the shape of the object
                 question = "shape"
                 if norelational_answer == 2:
                     outcome = 1 #"rectangle"
@@ -56,7 +58,7 @@ class SORTOFCLEVRDataset(ImageDataset):
                     outcome = 0 # "circle"
                 else:
                     print("[ERROR] Wrong outcome for the shape")
-            elif norelational_question[5] == 1: # Query about the horizontal position
+            elif norelational_question[num + 3] == 1: # Query about the horizontal position
                 question = "horizontal_side"
                 if norelational_answer == 0:
                     outcome = 1 # "left"
@@ -64,7 +66,7 @@ class SORTOFCLEVRDataset(ImageDataset):
                     outcome = 0 # "right"
                 else: 
                     print("[ERROR] Wrong outcome for the horizontal position")
-            elif norelational_question[6] == 1: # Query about the vertical position
[…]

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Some bugfixes in data - still not correctly learning

@@ -39,7 +39,7 @@ class SORTOFCLEVRDataset(ImageDataset):
         if random.random() < 0.75: # Select nonbinary questions with 75% chance (three questions nonbinary / one question binary)
             sh = None
             for i, color in enumerate(["red", "green", "blue", "orange", "grey", "yellow"]):
-                if norelational_question[i] == 1: # Question about red object
+                if norelational_question[i] == 1:
                     sh = color
                 if i == num - 1:
                     break
@@ -80,7 +80,7 @@ class SORTOFCLEVRDataset(ImageDataset):
         else:
             sh = None
             for i, color in enumerate(["red", "green", "blue", "orange", "grey", "yellow"]):
-                if norelational_question[i] == 1: # Question about red object
+                if binary_question[i] == 1: 
                     sh = color
                 if i == num - 1:
                     break

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Bugfix: problem was due to two 'i' vars

@@ -38,10 +38,10 @@ class SORTOFCLEVRDataset(ImageDataset):
         norelational_question, norelational_answer, binary_question, binary_answer = self.data[i]
         if random.random() < 0.75: # Select nonbinary questions with 75% chance (three questions nonbinary / one question binary)
             sh = None
-            for i, color in enumerate(["red", "green", "blue", "orange", "grey", "yellow"]):
-                if norelational_question[i] == 1:
+            for j, color in enumerate(["red", "green", "blue", "orange", "grey", "yellow"]):
+                if norelational_question[j] == 1:
                     sh = color
-                if i == num - 1:
+                if j == num - 1:
                     break
             if sh is None:
                 print("[ERROR] No object specified")
@@ -79,10 +79,10 @@ class SORTOFCLEVRDataset(ImageDataset):
 
         else:
             sh = None
-            for i, color in enumerate(["red", "green", "blue", "orange", "grey", "yellow"]):
-                if binary_question[i] == 1: 
+            for j, color in enumerate(["red", "green", "blue", "orange", "grey", "yellow"]):
+                if binary_question[j] == 1: 
                     sh = color
-                if i == num - 1:
+                if j == num - 1:
                     break
             if sh is None:
                 print("[ERROR] No object specified")

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Pass the width as an argument to the SORTOFCLEVRDataset

@@ -9,8 +9,6 @@ import random
 random.seed(0)
 
 path = os.path.dirname(os.path.abspath(__file__))
-num = 2
-size = str(num) + 'x' + str(num)
 
 transform = transforms.Compose(
     [transforms.ToTensor(), transforms.Normalize((0.5, 0.5, 0.5), (0.5, 0.5, 0.5))]
@@ -20,8 +18,10 @@ class SORTOFCLEVRDataset(ImageDataset):
     def __init__(
         self,
         subset,
+        width,
     ):
-        super().__init__("{}/{}/{}/images".format(path, size, subset), transform=transform)
+        super().__init__("{}/{}/{}/images".format(path, str(width) + 'x' + str(width), subset), transform=transform)
+        size = str(width) + 'x' + str(width)
         self.data = []
         self.subset = subset
         with open("{}/{}/{}/{}.csv".format(path, size, subset, subset)) as f:
@@ -41,16 +41,16 @@ class SORTOFCLEVRDataset(ImageDataset):
             for j, color in enumerate(["red", "green", "blue", "orange", "grey", "yellow"]):
                 if norelational_question[j] == 1:
                     sh = color
-                if j == num - 1:
+                if j == self.width - 1:
                     break
             if sh is None:
                 print("[ERROR] No object specified")
             
-            assert(norelational_question[num] == 1 and norelational_question[num + 1] == 0) # Nonbinary question
+            assert(norelational_question[self.width] == 1 and norelational_question[self.width + 1] == 0) # Nonbinary question
             
             question = None
             outcome = None
-            if norelational_question[num + 2] == 1: # Query about the shape of the object
+            if norelational_question[self.width + 2] == 1: # Query about the shape of the object
                 question = "shape"
                 if norelational_answer == 2:
                     outcome = 1 #"rectangle"
@@ -58,7 +58,7 @@ class SORTOFCLEVRDataset(ImageDataset):
                     outcome = 0 # "circle"
                 else:
                     print("[ERROR] Wrong outcome for the shape")
-            elif norelational_question[num + 3] == 1: # Query about the horizontal position
+            elif norelational_question[self.width + 3] == 1: # Query about the horizontal position
                 question = "horizontal_side"
                 if norelational_answer == 0:
                     outcome = 1 # "left"
@@ -66,7 +66,7 @@ class SORTOFCLEVRDataset(ImageDataset):
                     outcome = 0 # "right"
                 else: 
                     print("[ERROR] Wrong outcome for the horizontal position")
[…]

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -15,6 +15,8 @@ import random
 random.seed(0)
 #np.random.seed(args.seed)
 
+width = 2 
+
 cnn_red = CNNNetwork(out_size=8)
 cnn_green = CNNNetwork(out_size=8)
 
@@ -23,9 +25,9 @@ net_green = Network(cnn_green, "cnn_green", Adam(cnn_green.parameters(), lr=3e-3
 
 model = Model("/home/jorrit/Data/KU Leuven/Semester 12/Capita Selecta H05N0a/deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl", [net_red, net_green])
 
-train_dataset = SORTOFCLEVRDataset("train")
-val_dataset = SORTOFCLEVRDataset("val")
-test_dataset = SORTOFCLEVRDataset("test")
+train_dataset = SORTOFCLEVRDataset("train", width)
+val_dataset = SORTOFCLEVRDataset("val", width)
+test_dataset = SORTOFCLEVRDataset("test", width)
 loader = DataLoader(train_dataset, 32, shuffle=True)
 
 model.add_tensor_source("train", train_dataset)

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py
Generalize sort_of_clevr.py to work with a variable number of CNN networks

@@ -16,14 +16,23 @@ random.seed(0)
 #np.random.seed(args.seed)
 
 width = 2 
+out_size = (width ** 2) * 2 # Times two for the distinction between squares and circles
 
-cnn_red = CNNNetwork(out_size=8)
-cnn_green = CNNNetwork(out_size=8)
+colors = ["red", "green", "blue", "orange", "grey", "yellow"]
+used_colors = colors[0:width]
+cnns = {}
+for i, color in enumerate(used_colors):
+    cnn = CNNNetwork(out_size=out_size)
+    cnns["cnn_" + color] = cnn
 
-net_red = Network(cnn_red, "cnn_red", Adam(cnn_red.parameters(), lr=3e-3), batching=True)
-net_green = Network(cnn_green, "cnn_green", Adam(cnn_green.parameters(), lr=3e-3), batching=True)
+nets = {}
+nets_ordered = []
+for i, color in enumerate(used_colors):
+    net = Network(cnns["cnn_" + color], "cnn_" + color, Adam(cnns["cnn_" + color].parameters(), lr=3e-3), batching=True)
+    nets["net_" + color] = net
+    nets_ordered.append(net)
 
-model = Model("/home/jorrit/Data/KU Leuven/Semester 12/Capita Selecta H05N0a/deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl", [net_red, net_green])
+model = Model("/home/jorrit/Data/KU Leuven/Semester 12/Capita Selecta H05N0a/deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl", nets_ordered)
 
 train_dataset = SORTOFCLEVRDataset("train", width)
 val_dataset = SORTOFCLEVRDataset("val", width)

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Bugfix: store width in the SORTOFCLEVRDataset

@@ -24,6 +24,7 @@ class SORTOFCLEVRDataset(ImageDataset):
         size = str(width) + 'x' + str(width)
         self.data = []
         self.subset = subset
+        self.width = width
         with open("{}/{}/{}/{}.csv".format(path, size, subset, subset)) as f:
             for line in f:
                 norelational_question, norelational_answer, binary_question, binary_answer = \

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Modify .pl file to accomodate 4x4 grids - untested

@@ -1,108 +1,164 @@
 % We know that there are two objects in a four grid space. Two shapes possible, two colors possible.
-% The green cnn detects the position, and the shape --> x. If x < 4: Shape = rectangle. Else: shape = circle. (x modulo 4 = position)  
+% The green cnn detects the position, and the shape --> x. If x < size: Shape = rectangle. Else: shape = circle. (x modulo size = position)  
 
-nn(cnn_red,[X],Y_red,[0,1,2,3,4,5,6,7]) :: detect_state(red, X, Y_red).
-nn(cnn_green, [X], Y_green, [0,1,2,3,4,5,6,7]) :: detect_state(green, X, Y_green).
+width(4).
+size(N) :-
+    width(Width),
+    N is Width * Width.
+states(N) :-
+    size(Size),
+    N is Size * 2.
 
+% [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32]
+nn(cnn_red,[X],Y_red, [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32]) :: detect_state(red, X, Y_red).
+nn(cnn_green, [X], Y_green,  [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32]) :: detect_state(green, X, Y_green).
+nn(cnn_blue,[X],Y_blue, [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32]) :: detect_state(blue, X, Y_blue).
+nn(cnn_orange, [X], Y_orange,  [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32]) :: detect_state(orange, X, Y_orange).
+
+detect_same_states(Shape, Count) :-
+    check_state(red, Return_red),
[…]

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Bugfix: Start at zero instead of one

@@ -9,11 +9,12 @@ states(N) :-
     size(Size),
     N is Size * 2.
 
-% [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32]
-nn(cnn_red,[X],Y_red, [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32]) :: detect_state(red, X, Y_red).
-nn(cnn_green, [X], Y_green,  [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32]) :: detect_state(green, X, Y_green).
-nn(cnn_blue,[X],Y_blue, [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32]) :: detect_state(blue, X, Y_blue).
-nn(cnn_orange, [X], Y_orange,  [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32]) :: detect_state(orange, X, Y_orange).
+% [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]
+% [0, 1, 2, 3, 4, 5, 6, 7]
+nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(red, X, Y_red).
[…]

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Some bugfixes

@@ -14,22 +14,22 @@ states(N) :-
 nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(red, X, Y_red).
 nn(cnn_green, [X], Y_green,  [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(green, X, Y_green).
 nn(cnn_blue,[X],Y_blue, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(blue, X, Y_blue).
-nn(cnn_orange, [X], Y_orange,  [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(orange, X, Y_orange).
+nn(cnn_orange, [X], Y_orange, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(orange, X, Y_orange).
 
-detect_same_states(Shape, Count) :-
-    check_state(red, Return_red),
-    check_state(green, Return_green),
-    check_state(blue, Return_blue),
-    check_state(orange, Return_orange),
+detect_same_states(Shape, Img, Count) :-
+    check_state(red, Shape, Img, Return_red),
+    check_state(green, Shape, Img, Return_green),
+    check_state(blue, Shape, Img, Return_blue),
+    check_state(orange, Shape, Img, Return_orange),
     Count is Return_red + Return_green + Return_blue + Return_orange.
 
-check_state(Color, Return) :-
-    detect_state(Color, X, Y_color),
+check_state(Color, Shape, Img, Return) :-
+    detect_state(Color, Img, Y_color),
[…]

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -15,7 +15,7 @@ import random
 random.seed(0)
 #np.random.seed(args.seed)
 
-width = 2 
+width = 4
 out_size = (width ** 2) * 2 # Times two for the distinction between squares and circles
 
 colors = ["red", "green", "blue", "orange", "grey", "yellow"]

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Try to let it train perfectly on 2x2 with the reformed .pl file - problem with binary questions

@@ -1,7 +1,7 @@
 % We know that there are two objects in a four grid space. Two shapes possible, two colors possible.
 % The green cnn detects the position, and the shape --> x. If x < size: Shape = rectangle. Else: shape = circle. (x modulo size = position)  
 
-width(4).
+width(2).
 size(N) :-
     width(Width),
     N is Width * Width.
@@ -11,17 +11,18 @@ states(N) :-
 
 % [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]
 % [0, 1, 2, 3, 4, 5, 6, 7]
-nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(red, X, Y_red).
-nn(cnn_green, [X], Y_green,  [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(green, X, Y_green).
-nn(cnn_blue,[X],Y_blue, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(blue, X, Y_blue).
-nn(cnn_orange, [X], Y_orange, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(orange, X, Y_orange).
+nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7]) :: detect_state(red, X, Y_red).
+nn(cnn_green, [X], Y_green,  [0, 1, 2, 3, 4, 5, 6, 7]) :: detect_state(green, X, Y_green).
[…]

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -19,7 +19,7 @@ width = 4
 out_size = (width ** 2) * 2 # Times two for the distinction between squares and circles
 
 colors = ["red", "green", "blue", "orange", "grey", "yellow"]
-used_colors = colors[0:width]
+used_colors = colors[0:width*2]
 cnns = {}
 for i, color in enumerate(used_colors):
     cnn = CNNNetwork(out_size=out_size)

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Working training process for 2x2 again

@@ -143,8 +143,6 @@ position_is_bottom(Img, Color) :-
 
 % BINARY QUESTION
 % Question about the number of same shapes like that one
-
-% Note: Do not need red_number_of_shapes and green_number_of_shapes right now. But has been added since this will be necessary later (implementation with same_shape will have to change too though)
 red_number_of_shapes(Img, Count) :-
     detect_state(red, Img, Y_red),
     to_shape(Y_red, Shape),
@@ -154,7 +152,7 @@ green_number_of_shapes(Img, Count) :-
     to_shape(Y_green, Shape),
     detect_same_states(Shape, Img, Count).
 blue_number_of_shapes(Img, Count) :-
-    detect_state(red, Img, Y_blue),
+    detect_state(blue, Img, Y_blue),
     to_shape(Y_blue, Shape),
     detect_same_states(Shape, Img, Count).
 orange_number_of_shapes(Img, Count) :-
@@ -168,7 +166,7 @@ to_shape(Y_color, Shape) :-
     Shape = 0. % Shape = 0 --> Rectangle 
 to_shape(Y_color, Shape) :-
     size(Size),
-    Y_color  >= Size,
+    Y_color >= Size,
     Shape = 1. % Shape = 1 --> Circle
 
 

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -15,7 +15,7 @@ import random
 random.seed(0)
 #np.random.seed(args.seed)
 
-width = 4
+width = 2
 out_size = (width ** 2) * 2 # Times two for the distinction between squares and circles
 
 colors = ["red", "green", "blue", "orange", "grey", "yellow"]

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Working training process on 4x4

@@ -1,7 +1,7 @@
 % We know that there are two objects in a four grid space. Two shapes possible, two colors possible.
 % The green cnn detects the position, and the shape --> x. If x < size: Shape = rectangle. Else: shape = circle. (x modulo size = position)  
 
-width(2).
+width(4).
 size(N) :-
     width(Width),
     N is Width * Width.
@@ -11,18 +11,17 @@ states(N) :-
 
 % [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]
 % [0, 1, 2, 3, 4, 5, 6, 7]
-nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7]) :: detect_state(red, X, Y_red).
-nn(cnn_green, [X], Y_green,  [0, 1, 2, 3, 4, 5, 6, 7]) :: detect_state(green, X, Y_green).
-nn(cnn_blue,[X],Y_blue, [0, 1, 2, 3, 4, 5, 6, 7]) :: detect_state(blue, X, Y_blue).
-nn(cnn_orange, [X], Y_orange, [0, 1, 2, 3, 4, 5, 6, 7]) :: detect_state(orange, X, Y_orange).
+nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(red, X, Y_red).
+nn(cnn_green,[X], Y_green, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(green, X, Y_green).
+nn(cnn_blue,[X],Y_blue, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(blue, X, Y_blue).
[…]

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -15,11 +15,11 @@ import random
 random.seed(0)
 #np.random.seed(args.seed)
 
-width = 2
+width = 4
 out_size = (width ** 2) * 2 # Times two for the distinction between squares and circles
 
 colors = ["red", "green", "blue", "orange", "grey", "yellow"]
-used_colors = colors[0:width*2]
+used_colors = colors[0:width]
 cnns = {}
 for i, color in enumerate(used_colors):
     cnn = CNNNetwork(out_size=out_size)

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Update model.pl in order to work on 6x6 grids

@@ -1,7 +1,7 @@
 % We know that there are two objects in a four grid space. Two shapes possible, two colors possible.
 % The green cnn detects the position, and the shape --> x. If x < size: Shape = rectangle. Else: shape = circle. (x modulo size = position)  
 
-width(4).
+width(6).
 size(N) :-
     width(Width),
     N is Width * Width.
@@ -9,19 +9,22 @@ states(N) :-
     size(Size),
     N is Size * 2.
 
+% [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71]
 % [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]
 % [0, 1, 2, 3, 4, 5, 6, 7]
-nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(red, X, Y_red).
-nn(cnn_green,[X], Y_green, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(green, X, Y_green).
-nn(cnn_blue,[X],Y_blue, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]) :: detect_state(blue, X, Y_blue).
[…]

### 2022-03-10 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -15,7 +15,7 @@ import random
 random.seed(0)
 #np.random.seed(args.seed)
 
-width = 4
+width = 6
 out_size = (width ** 2) * 2 # Times two for the distinction between squares and circles
 
 colors = ["red", "green", "blue", "orange", "grey", "yellow"]

### 2022-03-11 paper/paper.tex
Start writing for approach
Write about the generation of data

@@
 \section{LITERATURE SURVEY}
+\label{sec:literature_survey}
 The application focuses on Visual Question Answering (VQA), for which huge datasets are present, along with very sophisticated methods.
@@
 Finally, since this application uses DeepProbLog, quite some time was spent in digesting the DeepProbLog paper \cite{deepproblog}, along with understanding the  examples provided in the code repository \cite{deepproblog_code}.
+
+\section{APPROACH}
+The implementation process involved three main parts:
+\begin{enumerate}
+    \item Generation of data.
+    \item Creation of the logical part with DeepProbLog statements.
+    \item Linking the data and controlling the training process in pure Python code.
+\end{enumerate}
+
+% TODO maybe elaborate why I switched from having a CNN per square in the grid, to one CNN per color.
+
+\subsection{Generation of data}
+As mentioned in Section \ref{sec:literature_survey}, the data used in this application is based on the Sort Of CLEVR dataset, with one extra simplification.
+Given that the logical part will have to decide whether an object is located on the left side of an image, the neural network will have to convey positional information to the logical part.
+Hence, each discrete position will have to be encoded by a possible outcome of the neural network.
+Therefore, objects may only be located at certain places in a grid.
+In this application, a grid of 2x2, 4x4 and 6x6 has been used.
+
+The data generator that was used for the creation of the Sort Of CLEVR dataset has been modified in order to place objects in the mentioned grid positions \cite{sort_of_clevr_dataset}.
+An example of a generated image is given in Figure \ref{fig:sample_image_own_dataset}.
+
+\begin{figure}[H]
+    \begin{center}
+    %\includegraphics[width=0.3\textwidth]{sample_own_dataset.png} TODO
+    \captionsetup{justification=centering}
+    \caption{A sample image from the dataset that has been used for this application}
+    \label{fig:sample_image_own_dataset}
+    \end{center}
+\end{figure}
+
+Each specified color will have an object located somewhere in the grid, of which the shape can be a rectangle or a circle.
+
+These images are accompanied with three non-binary questions and one binary question. For each question, a random object is chosen. The possibilities are:
+\begin{enumerate}
+    \item Non-binary - What is the shape of this object \footnote{I.e. the shape will be either a rectangle or a circle.}?
+    \item Non-binary - Is this object located on the left side of the image?
+    \item Non-binary - Is this object located on the bottom side of the image?
+    \item Binary - How many objects have the same shape of this object?
+\end{enumerate}
+
+These questions are encoded in a one-hot encoding, after which they are stored in a CSV file, along with the expected answers.
+A training set, a validation set, and a test set are generated.
+% Validation set useful?
+
+\subsection{Logical rule encodings}
+
+\subsection{Controlling the training process}
+
+\section{EXPERIMENTS}
 

### 2022-03-11 paper/paper.tex
Write about the controlling of the training process

@@
 
-Each specified color will have an object located somewhere in the grid, of which the shape can be a rectangle or a circle.
+Each specified color will have an object located somewhere in the grid, of which the shape can be a square or a circle.
 
@@
 \begin{enumerate}
-    \item Non-binary - What is the shape of this object \footnote{I.e. the shape will be either a rectangle or a circle.}?
+    \item Non-binary - What is the shape of this object \footnote{I.e. the shape will be either a square or a circle.}?
     \item Non-binary - Is this object located on the left side of the image?
@@
 \subsection{Logical rule encodings}
+% TODO optimizations in these logical rule encodings? Possible to change e.g. red_number_of_shapes(...) into number_of_shapes(red, ...)?
 
 \subsection{Controlling the training process}
+The overall training process is controlled via the Python interfaces of DeepProbLog, along with general PyTorch implementations of the CNN's.
+First of all, CNN's are defined with PyTorch.
+A relatively simple network is used, where the input is given as a square RGB image of 100 pixels wide, which is transformed by the CNN into 72 output features for the 6x6 grid.
+Each color that is present in the image has its accompanied CNN network, hence the 72 output features encode the possible positions of the object with that color, along with their shape, which can be either square or circular ($6 \cdot 6 \cdot 2 = 72$).
+
+The final thing required before commencing the training process, are the data loaders.
+The most challenging part here is the transformation from the generated data to specific query mappings and their outcome.
+One of the questions are chosen, and a correct mapping between a predicate in the logical rule encoding file and the answer is set up.
 

### 2022-03-11 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Commit before refactoring

@@ -16,6 +16,8 @@ nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16,
 nn(cnn_green,[X], Y_green, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71]) :: detect_state(green, X, Y_green).
 nn(cnn_blue,[X],Y_blue, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71]) :: detect_state(blue, X, Y_blue).
 nn(cnn_orange,[X], Y_orange, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71]) :: detect_state(orange, X, Y_orange).
[…]

### 2022-03-11 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Refactor model.pl

@@ -96,8 +96,7 @@ class SORTOFCLEVRDataset(ImageDataset):
             assert(binary_answer >= 4)
             outcome = binary_answer - 3
         sub = {Term("image"): Term("tensor", Term(self.subset, Constant(i)))}
-        question = sh + "_" + question
-        return Query(Term(question, Term("image"), Constant(outcome)), sub)
+        return Query(Term(question, Term("image"), Term(sh), Constant(outcome)), sub)
            
     def __len__(self):
         return len(self.data)

### 2022-03-11 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl

@@ -41,46 +41,11 @@ check_state(Color, Shape, Img, Return) :-
 
 % NON-BINARY QUESTIONS
 % Question about the shape
-red_shape(Img, Rectangle) :-
-    shape_is_rectangle(Img, red),
+shape(Img, Color, Rectangle) :-
+    shape_is_rectangle(Img, Color),
     Rectangle = 1.
-red_shape(Img, Rectangle) :-
-    \+ shape_is_rectangle(Img, red),
-    Rectangle = 0.
-
-green_shape(Img, Rectangle) :-
-    shape_is_rectangle(Img, green),
-    Rectangle = 1.
-green_shape(Img, Rectangle) :-
-    \+ shape_is_rectangle(Img, green),
-    Rectangle = 0.
-
-blue_shape(Img, Rectangle) :-
-    shape_is_rectangle(Img, blue),
-    Rectangle = 1.
-blue_shape(Img, Rectangle) :-
-    \+ shape_is_rectangle(Img, blue),
-    Rectangle = 0.
-
-orange_shape(Img, Rectangle) :-
-    shape_is_rectangle(Img, orange),
-    Rectangle = 1.
-orange_shape(Img, Rectangle) :-
-    \+ shape_is_rectangle(Img, orange),
-    Rectangle = 0.
-
-grey_shape(Img, Rectangle) :-
-    shape_is_rectangle(Img, grey),
-    Rectangle = 1.
-grey_shape(Img, Rectangle) :-
-    \+ shape_is_rectangle(Img, grey),
-    Rectangle = 0.
-
-yellow_shape(Img, Rectangle) :-
-    shape_is_rectangle(Img, yellow),
-    Rectangle = 1.
-yellow_shape(Img, Rectangle) :-
-    \+ shape_is_rectangle(Img, yellow),
+shape(Img, Color, Rectangle) :-
+    \+ shape_is_rectangle(Img, Color),
     Rectangle = 0.
 
 shape_is_rectangle(Img, Color) :-
@@ -88,48 +53,12 @@ shape_is_rectangle(Img, Color) :-
     size(Size),
     Y_color < Size.
 
-
 % Question about the horizontal side
-red_horizontal_side(Img, Left) :-
-    position_is_left(Img, red),
+horizontal_side(Img, Color, Left) :-
+    position_is_left(Img, Color),
     Left = 1.
-red_horizontal_side(Img, Left) :-
-    \+ position_is_left(Img, red),
-    Left = 0.
-
-green_horizontal_side(Img, Left) :-
[…]

### 2022-03-11 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -50,9 +50,9 @@ train_log = train_model(
     model,
     loader,
     1,
-    log_iter=3,
+    log_iter=1,
     initial_test=False,
-    test_iter=50,
+    test_iter=1,
     test=lambda x: [
         #("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
         ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),

### 2022-03-12 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Refactor .pl file for supporting cuts

@@ -1,6 +1,8 @@
 % We know that there are two objects in a four grid space. Two shapes possible, two colors possible.
 % The green cnn detects the position, and the shape --> x. If x < size: Shape = rectangle. Else: shape = circle. (x modulo size = position)  
 
+:- use_module(library(cut)).
+
 width(6).
 size(N) :-
     width(Width),
@@ -29,23 +31,23 @@ detect_same_states(Shape, Img, Count) :-
     Count is Return_red + Return_green + Return_blue + Return_orange + Return_grey + Return_yellow.
 
 check_state(Color, Shape, Img, Return) :-
+    cut(check_state_with_cut(Color, Shape, Img, Return)).
+check_state_with_cut(1, Color, Shape, Img, Return) :-
     detect_state(Color, Img, Y_color),
     to_shape(Y_color, Shape_color),
     Shape =:= Shape_color,
     Return = 1.
-check_state(Color, Shape, Img, Return) :-
-    detect_state(Color, Img, Y_color),
-    to_shape(Y_color, Shape_color),
-    Shape =\= Shape_color,
+check_state_with_cut(2, Color, Shape, Img, Return) :-
     Return = 0.
 
 % NON-BINARY QUESTIONS
 % Question about the shape
 shape(Img, Color, Rectangle) :-
+    cut(shape_with_cut(Img, Color, Rectangle)).
+shape_with_cut(1, Img, Color, Rectangle) :-
     shape_is_rectangle(Img, Color),
     Rectangle = 1.
-shape(Img, Color, Rectangle) :-
-    \+ shape_is_rectangle(Img, Color),
+shape_with_cut(2, Img, Color, Rectangle) :-
     Rectangle = 0.
 
 shape_is_rectangle(Img, Color) :-
@@ -55,10 +57,11 @@ shape_is_rectangle(Img, Color) :-
 
 % Question about the horizontal side
 horizontal_side(Img, Color, Left) :-
+    cut(horizontal_side_with_cut(Img, Color, Left)).
+horizontal_side_with_cut(1, Img, Color, Left) :-
     position_is_left(Img, Color),
     Left = 1.
-horizontal_side(Img, Color, Left) :-
-    \+ position_is_left(Img, Color),
+horizontal_side_with_cut(2, Img, Color, Left) :-
     Left = 0.
 
 position_is_left(Img, Color) :-
[…]

### 2022-03-12 paper/paper.tex
Write a bit further

@@
 
-\subsection{Logical rule encodings}
-% TODO optimizations in these logical rule encodings? Possible to change e.g. red_number_of_shapes(...) into number_of_shapes(red, ...)?
-
 \subsection{Controlling the training process}
@@
 
-The final thing required before commencing the training process, are the data loaders.
+The final thing (besides the logical rule encodings) required before commencing the training process, are the data loaders.
 The most challenging part here is the transformation from the generated data to specific query mappings and their outcome.
 One of the questions are chosen, and a correct mapping between a predicate in the logical rule encoding file and the answer is set up.
+
+\subsection{Logical rule encodings}
+Once the CNN belonging to a specific color has determined the position and the shape of that object, logical rules can deduce whether this object is located on the left hand side of the image, on the bottom side, and how many objects have the same shape.
+The logical rule program has been listed in Appendix \ref{appendix:logical_rule_encodings}
 
@@
 \label{comparison_with_CNN}
+
+\section{APPENDIX}
+\subsection{Logical rule encodings}
+\label{appendix:logical_rule_encodings}
+% TODO put logical rules here
 

### 2022-03-12 relational-networks/sort_of_clevr_generator.py
Reduce the size of the val and test size

@@ -19,8 +19,8 @@ parser.add_argument('--t-subtype', type=int, default=-1,
 args = parser.parse_args()
 
 IMG_SIZE = 100
-NUM_OBJECTS = 4
-WIDTH = 4
+NUM_OBJECTS = 6
+WIDTH = 6
 
 colors = [
     (0,0,255),##r
@@ -178,7 +178,7 @@ def build_dataset_item():
 
 if __name__ == "__main__":
     size = str(WIDTH) + "x" + str(WIDTH)
-    for (dataset, num, seed) in [("train", 10000, 0), ("val", 2000, 1), ("test", 2000, 2)]:
+    for (dataset, num, seed) in [("train", 10000, 0), ("val", 500, 1), ("test", 500, 2)]:
         path = '../deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/' + size + '/' + dataset
 
         if not os.path.exists(path + '/images'):

### 2022-03-13 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/pure_cnn_data.py
Create a quick pure CNN based dataset

@@ -1,0 +1,52 @@
+import torch
+from torch.utils.data import Dataset
+import os
+from pathlib import Path
+import torchvision.transforms as transforms
+from PIL import Image
+import random
+
+path = os.path.dirname(os.path.abspath(__file__))
+transform = transforms.Compose(
+    [transforms.ToTensor(), transforms.Normalize((0.5, 0.5, 0.5), (0.5, 0.5, 0.5))]
+)
+
+class Pure_CNN_Data(Dataset):
+    def __init__(self, subset, width, extension="png"):
+        super().__init__()
+        root = "{}/{}/{}/images".format(path, str(width) + 'x' + str(width), subset)
+        self.root = Path(root)
+        self.transform = transform
+        self.extension = extension
+        self.subset = subset
+        self.data = []
+        size = str(width) + 'x' + str(width)
+        self.subset = subset
+        self.width = width
+        with open("{}/{}/{}/{}.csv".format(path, size, subset, subset)) as f:
+            for line in f:
+                norelational_question, norelational_answer, binary_question, binary_answer = \
+                    [(l.rstrip('\n')[1:-1]).split() for l in line.split(",")]
+                norelational_question = list(map(int, list(map(float, norelational_question))))
+                norelational_answer = int(float(norelational_answer[0]))
+                binary_question = list(map(int, list(map(float, binary_question))))
+                binary_answer = int(float(binary_answer[0]))
+                self.data.append((norelational_question, norelational_answer, binary_question, binary_answer))
+
+    def __len__(self):
+        return len(self.data)
+
+    def __getitem__(self, idx):
+        if type(idx) is tuple:
+            idx = idx[0]
+        p = self.root / "{}.{}".format(idx, self.extension)
+        with open(p, "rb") as f:
+            img = Image.open(f)
+            img = img.convert("RGB")
+            if self.transform is not None:
+                img = self.transform(img)
+        norelational_question, norelational_answer, binary_question, binary_answer = self.data[idx]
+        if random.random() < 0.75:
+            return img, norelational_question, norelational_answer
+        else:
+            return img, binary_question, binary_answer

### 2022-03-13 deepproblog/src/deepproblog/examples/SORTOFCLEVR/network_for_pure_CNN.py
More implementing for pure CNN approach

@@ -1,0 +1,75 @@
+from turtle import forward
+import torch
+from torch import nn
+import numpy as np
+
+class CNNNetwork(nn.Module):
+    def __init__(self, out_size):
+        super(CNNNetwork, self).__init__()
+        self.convolutions = nn.Sequential(
+            nn.Conv2d(3, 6, 5, stride=2),
+            nn.ReLU(),
+            nn.MaxPool2d(2),
+            #nn.Conv2d(6, 16, 3, stride=1, padding=1),
+            #nn.ReLU(),
+            #nn.MaxPool2d(2),
+            nn.Dropout2d(0.4),
+        )
+
+        self.mlp = nn.Sequential(
+            nn.LazyLinear(out_size), # Square and red, square and green, circle and red, circle and green
+            nn.Softmax(dim=1)
+            # nn.Dropout2d(0.8)
+        )
+
+    def forward(self, x):
+        x = self.convolutions(x)
+        x = torch.flatten(x, 1)
+        x = self.mlp(x)
+        return x
+
+class MLP(nn.Module):
+    def __init__(self, input_size, out_size): # Input size = (number of colors for one-hot vector of color), 2 for question type (nonbinary VS binary), 3 for question subtype
+        super().__init__()
+        self.layer1 = nn.Linear(input_size, 16)
+        self.layer2 = nn.Linear(16, 8)
+        self.layer3 = nn.Linear(8, out_size)
+
+    def forward(self, x):
+        y = self.layer1(x)
+        z = self.layer2(y)
+        q = self.layer3(z)
+        return q
+
+class Combine(nn.Module):
+    def __init__(self, input_size_image, input_size_MLP, out_size):
+        super().__init__()
+        self.layer1 = nn.Linear(input_size_image + input_size_MLP, 128)
+        self.layer2 = nn.Linear(128, 32)
+        self.layer3 = nn.Linear(32, out_size)
+    
+    def forward(self, x1, x2):
+        y = torch.cat((x1, x2), dim=1)
+        z = self.layer1(y)
+        q = self.layer2(z)
+        r = self.layer3(q)
+        return r
+
+class PureCNN(nn.Module):
+    def __init__(self, output_size):
+        super().__init__()
+        self.cnn_net = CNNNetwork(out_size=(6 **2) * 2)
[…]

### 2022-03-13 deepproblog/src/deepproblog/examples/SORTOFCLEVR/pure_cnn_training.py

@@ -1,0 +1,95 @@
+from this import d
+from data.pure_cnn_data import Pure_CNN_Data
+from network_for_pure_CNN import PureCNN
+from torch.utils.data import DataLoader
+import torch
+from torch import nn, tensor
+
+# Check if GPU is available
+device = "cuda" if torch.cuda.is_available() else "cpu"
+print(f"Using {device} device")
+
+
+
+def accuracy_metric(predictions, expected):
+    pred = torch.argmax(predictions, dim=1) # Indices of the max value of all elements -> 0 if "no" has highest probability, 1 if "yes"
+    return torch.sum(pred.long() == expected).item()
+
+from torch.nn.modules.activation import Softmax
+def train(model, train_dl, val_dl, loss_function, optimizer, epochs=10, accuracy_metric=None):
+
+    train_loss, val_loss = [], []
+    
+    # Optimization loop
+    for epoch in range(epochs):
+        print('Epoch: ' + str(epoch))
+
+        for phase in ['train', 'val']:
+            if phase == 'train':
+                model.train(True)
+                dataloader = train_dl
+            else:
+                model.train(False)
+                dataloader = val_dl
+            
+            actual_loss = 0.0
+            actual_acc = 0.0
+            
+            for step, (img, questions, answer) in enumerate(dataloader):
+                questions = torch.FloatTensor(questions)
+                answer_one_hot = torch.zeros((10)).to(device)
+                answer_one_hot[answer] = 1.
+                if phase == 'train':
+                    outputs = model(img, questions)
+                    loss = loss_function(outputs, answer_one_hot.long())
+                    train_loss.append(loss)
+                    
+                    # Backpropagation
+                    optimizer.zero_grad() # Needed because backprop accumulates the gradients on subsequent passes
+                    loss.backward()       # Backpropagates the prediction loss (gradient of the loss with respect to each parameter)
+                    optimizer.step()      # adjust the parameters by the collected gradients from the backward step
+                
+                else:
+                    with torch.no_grad(): # disable grad tracking for faster model evaluation
+                        outputs = model(img, questions)
+                        loss = loss_function(outputs, answer_one_hot.long())
+                        val_loss.append(loss)
+                        acc = accuracy_metric(outputs, answer_one_hot) #Use self-defined accuracy metric
[…]

### 2022-03-15 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/pure_cnn_data.py
Make pure CNN approach more general, to also work on the 2x2 dataset

@@ -47,6 +47,6 @@ class Pure_CNN_Data(Dataset):
                 img = self.transform(img)
         norelational_question, norelational_answer, binary_question, binary_answer = self.data[idx]
         if random.random() < 0.75:
-            return img, norelational_question, norelational_answer
+            return img, torch.FloatTensor(norelational_question), norelational_answer
         else:
-            return img, binary_question, binary_answer
+            return img, torch.FloatTensor(binary_question), binary_answer

### 2022-03-15 deepproblog/src/deepproblog/examples/SORTOFCLEVR/network_for_pure_CNN.py

@@ -56,11 +56,11 @@ class Combine(nn.Module):
         return r
 
 class PureCNN(nn.Module):
-    def __init__(self, output_size):
+    def __init__(self, size, output_size):
         super().__init__()
-        self.cnn_net = CNNNetwork(out_size=(6 **2) * 2)
-        self.mlp = MLP(input_size=6 + 2 + 3, out_size=16) # Input size = (number of colors for one-hot vector of color), 2 for question type (nonbinary VS binary), 3 for question subtype
-        self.combine = Combine((6 **2) * 2, 16, output_size)
+        self.cnn_net = CNNNetwork(out_size=(size **2) * 2)
+        self.mlp = MLP(input_size=size + 2 + 3, out_size=16) # Input size = (number of colors for one-hot vector of color), 2 for question type (nonbinary VS binary), 3 for question subtype
+        self.combine = Combine((size **2) * 2, 16, output_size)
 
     def forward(self, img, question):
         out_cnn = self.cnn_net(img)

### 2022-03-15 deepproblog/src/deepproblog/examples/SORTOFCLEVR/pure_cnn_training.py

@@ -1,25 +1,25 @@
+from random import weibullvariate
 from this import d
 from data.pure_cnn_data import Pure_CNN_Data
 from network_for_pure_CNN import PureCNN
 from torch.utils.data import DataLoader
 import torch
+from deepproblog.utils import format_time_precise
 from torch import nn, tensor
 
 # Check if GPU is available
 device = "cuda" if torch.cuda.is_available() else "cpu"
 print(f"Using {device} device")
 
-
-
 def accuracy_metric(predictions, expected):
     pred = torch.argmax(predictions, dim=1) # Indices of the max value of all elements -> 0 if "no" has highest probability, 1 if "yes"
-    return torch.sum(pred.long() == expected).item()
+    return torch.sum(pred == expected).item()
 
 from torch.nn.modules.activation import Softmax
-def train(model, train_dl, val_dl, loss_function, optimizer, epochs=10, accuracy_metric=None):
+def train(model, train_dl, val_dl, loss_function, optimizer, epochs=10, accuracy_metric=None, batch_size=8):
 
     train_loss, val_loss = [], []
-    
+     
     # Optimization loop
     for epoch in range(epochs):
         print('Epoch: ' + str(epoch))
@@ -36,12 +36,9 @@ def train(model, train_dl, val_dl, loss_function, optimizer, epochs=10, accuracy
             actual_acc = 0.0
             
             for step, (img, questions, answer) in enumerate(dataloader):
-                questions = torch.FloatTensor(questions)
-                answer_one_hot = torch.zeros((10)).to(device)
-                answer_one_hot[answer] = 1.
                 if phase == 'train':
                     outputs = model(img, questions)
-                    loss = loss_function(outputs, answer_one_hot.long())
+                    loss = loss_function(outputs, answer.long())
                     train_loss.append(loss)
                     
                     # Backpropagation
@@ -52,17 +49,17 @@ def train(model, train_dl, val_dl, loss_function, optimizer, epochs=10, accuracy
                 else:
                     with torch.no_grad(): # disable grad tracking for faster model evaluation
                         outputs = model(img, questions)
-                        loss = loss_function(outputs, answer_one_hot.long())
+                        loss = loss_function(outputs, answer.long())
                         val_loss.append(loss)
[…]

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/network_for_pure_CNN.py
Overfitting now if testing on small training set

@@ -3,6 +3,7 @@ import torch
 from torch import nn
 import numpy as np
 
+prob = 0.0
 class CNNNetwork(nn.Module):
     def __init__(self, out_size):
         super(CNNNetwork, self).__init__()
@@ -18,7 +19,7 @@ class CNNNetwork(nn.Module):
 
         self.mlp = nn.Sequential(
             nn.LazyLinear(out_size), # Square and red, square and green, circle and red, circle and green
-            nn.Softmax(dim=1)
+            #nn.Softmax(dim=1)
             # nn.Dropout2d(0.8)
         )
 
@@ -31,29 +32,46 @@ class CNNNetwork(nn.Module):
 class MLP(nn.Module):
     def __init__(self, input_size, out_size): # Input size = (number of colors for one-hot vector of color), 2 for question type (nonbinary VS binary), 3 for question subtype
         super().__init__()
-        self.layer1 = nn.Linear(input_size, 16)
-        self.layer2 = nn.Linear(16, 8)
-        self.layer3 = nn.Linear(8, out_size)
+        self.net = nn.Sequential(
+            nn.Linear(input_size, 16),
+            nn.ReLU(),
+            #nn.BatchNorm1d(num_features=16),
+            nn.Dropout(prob),
+            nn.Linear(16, 8),
+            nn.ReLU(),
+            #nn.BatchNorm1d(num_features=8),
+            nn.Dropout(prob),
+            nn.Linear(8, out_size),
+            nn.Softmax(dim=1),
+            #nn.ReLU(),
+            #nn.BatchNorm1d(num_features=out_size),
+            nn.Dropout(prob),
+        )
 
     def forward(self, x):
-        y = self.layer1(x)
-        z = self.layer2(y)
-        q = self.layer3(z)
-        return q
+        return self.net(x)
 
 class Combine(nn.Module):
     def __init__(self, input_size_image, input_size_MLP, out_size):
         super().__init__()
-        self.layer1 = nn.Linear(input_size_image + input_size_MLP, 128)
-        self.layer2 = nn.Linear(128, 32)
-        self.layer3 = nn.Linear(32, out_size)
+        self.net = nn.Sequential(
+            nn.Linear(input_size_image + input_size_MLP, 128),
+            nn.ReLU(),
+            #nn.BatchNorm1d(num_features=128),
+            nn.Dropout(prob),
+            nn.Linear(128, 32),
+            nn.ReLU(),
[…]

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/pure_cnn_training.py

@@ -12,7 +12,9 @@ device = "cuda" if torch.cuda.is_available() else "cpu"
 print(f"Using {device} device")
 
 def accuracy_metric(predictions, expected):
+    print(predictions)
     pred = torch.argmax(predictions, dim=1) # Indices of the max value of all elements -> 0 if "no" has highest probability, 1 if "yes"
+    print(pred, expected)
     return torch.sum(pred == expected).item()
 
 from torch.nn.modules.activation import Softmax
@@ -76,6 +78,11 @@ def train(model, train_dl, val_dl, loss_function, optimizer, epochs=10, accuracy
     print("Training complete")
     return train_loss, val_loss
 
+def init_weights(m):
+    if isinstance(m, (nn.Linear, nn.Conv2d)):
+        torch.nn.init.xavier_uniform(m.weight)
+        m.bias.data.fill_(0.01)
+   
 size = 2
 output_size = 4 + size
 network = PureCNN(size=size, output_size=output_size) # Yes, no, square, circle, 1, 2, 3, 4, 5, 6
@@ -86,13 +93,19 @@ batch_size = 8
 train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
 test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=True)
 
+for (img, questions, answer) in train_loader:
+    network(img, questions)
+network.apply(init_weights)
+
 freq_number = 1 / (4 * size)
 freqs = [1/8, 1/8, 1/4, 1/4]
 for i in range(size):
     freqs.append(freq_number)
 freqs = torch.FloatTensor(freqs)
 weights = 1 / freqs
-weights = torch.sum(weights) / weights
+print(weights)
+weights = weights / torch.sum(weights)
+print(weights)
 # Chance on shape = 1/4, answer = rectangle or shape. So freq is 1/8
 # Chance on horizontal or vertical = 1/2, answer = yes or no. So freq is 1/2
 # Chance on number of objects = 1/4, answer = 1, 2, 3, 4, 5 or 6. So freq is 1 / (4 * 6)
@@ -101,5 +114,5 @@ loss_function.to(device)
 
 optimizer = torch.optim.Adam(network.parameters(), lr = 3e-4)
 
-epochs = 20
+epochs = 2000
 train_loss, test_loss = train(network, train_loader, test_loader, loss_function, optimizer, epochs, accuracy_metric, batch_size)

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/network_for_pure_CNN.py
Some modifications for training on big 2x2 dataset, stagnation around 80%

@@ -3,7 +3,7 @@ import torch
 from torch import nn
 import numpy as np
 
-prob = 0.0
+prob = 0.1
 class CNNNetwork(nn.Module):
     def __init__(self, out_size):
         super(CNNNetwork, self).__init__()

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/pure_cnn_training.py

@@ -12,9 +12,7 @@ device = "cuda" if torch.cuda.is_available() else "cpu"
 print(f"Using {device} device")
 
 def accuracy_metric(predictions, expected):
-    print(predictions)
     pred = torch.argmax(predictions, dim=1) # Indices of the max value of all elements -> 0 if "no" has highest probability, 1 if "yes"
-    print(pred, expected)
     return torch.sum(pred == expected).item()
 
 from torch.nn.modules.activation import Softmax
@@ -114,5 +112,5 @@ loss_function.to(device)
 
 optimizer = torch.optim.Adam(network.parameters(), lr = 3e-4)
 
-epochs = 2000
+epochs = 20
 train_loss, test_loss = train(network, train_loader, test_loader, loss_function, optimizer, epochs, accuracy_metric, batch_size)

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/network_for_pure_CNN.py
Add pure NN loss and accuracy plot on 2x2 dataset

@@ -10,15 +10,16 @@ class CNNNetwork(nn.Module):
         self.convolutions = nn.Sequential(
             nn.Conv2d(3, 6, 5, stride=2),
             nn.ReLU(),
+            #nn.BatchNorm2d(6),
             nn.MaxPool2d(2),
             #nn.Conv2d(6, 16, 3, stride=1, padding=1),
             #nn.ReLU(),
             #nn.MaxPool2d(2),
-            nn.Dropout2d(0.4),
+            #nn.Dropout2d(0.4),
         )
 
         self.mlp = nn.Sequential(
-            nn.LazyLinear(out_size), # Square and red, square and green, circle and red, circle and green
+            nn.LazyLinear(out_size),
             #nn.Softmax(dim=1)
             # nn.Dropout2d(0.8)
         )
@@ -42,7 +43,7 @@ class MLP(nn.Module):
             #nn.BatchNorm1d(num_features=8),
             nn.Dropout(prob),
             nn.Linear(8, out_size),
-            nn.Softmax(dim=1),
+            #nn.Softmax(dim=1),
             #nn.ReLU(),
             #nn.BatchNorm1d(num_features=out_size),
             nn.Dropout(prob),

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/pure_cnn_training.py

@@ -1,11 +1,13 @@
 from random import weibullvariate
 from this import d
+from turtle import st
 from data.pure_cnn_data import Pure_CNN_Data
 from network_for_pure_CNN import PureCNN
 from torch.utils.data import DataLoader
 import torch
 from deepproblog.utils import format_time_precise
 from torch import nn, tensor
+import time
 
 # Check if GPU is available
 device = "cuda" if torch.cuda.is_available() else "cpu"
@@ -18,7 +20,9 @@ def accuracy_metric(predictions, expected):
 from torch.nn.modules.activation import Softmax
 def train(model, train_dl, val_dl, loss_function, optimizer, epochs=10, accuracy_metric=None, batch_size=8):
 
-    train_loss, val_loss = [], []
+    train_loss, val_loss, epoch_accs, times = [], [], [], []
+    start_time = time.time()
+    times.append(0)
      
     # Optimization loop
     for epoch in range(epochs):
@@ -39,7 +43,7 @@ def train(model, train_dl, val_dl, loss_function, optimizer, epochs=10, accuracy
                 if phase == 'train':
                     outputs = model(img, questions)
                     loss = loss_function(outputs, answer.long())
-                    train_loss.append(loss)
+                    #train_loss.append(loss)
                     
                     # Backpropagation
                     optimizer.zero_grad() # Needed because backprop accumulates the gradients on subsequent passes
@@ -50,7 +54,7 @@ def train(model, train_dl, val_dl, loss_function, optimizer, epochs=10, accuracy
                     with torch.no_grad(): # disable grad tracking for faster model evaluation
                         outputs = model(img, questions)
                         loss = loss_function(outputs, answer.long())
-                        val_loss.append(loss)
+                        #val_loss.append(loss)
                         acc = accuracy_metric(outputs, answer) #Use self-defined accuracy metric
                         actual_acc += acc
                     
@@ -68,13 +72,20 @@ def train(model, train_dl, val_dl, loss_function, optimizer, epochs=10, accuracy
             # Normalize    
             epoch_loss = actual_loss / len(dataloader.dataset)
             epoch_acc = actual_acc / len(dataloader.dataset)
+            if phase == "val":
+                print(epoch_acc)
+                epoch_accs.append(epoch_acc)
+                val_loss.append(epoch_loss)
[…]

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/visualize_pure_cnn_outcomes.py

@@ -1,0 +1,42 @@
+import pickle
+import cv2
+import matplotlib.pyplot as plt
+with open('values_of_training_16_03_2022_12_00.pk', 'rb') as fp:
+    train_loss = pickle.load(fp)
+    test_loss = pickle.load(fp)
+    epoch_accs = pickle.load(fp)
+    times = pickle.load(fp)
+
+epoch_accs.insert(0, 1/8)
+del epoch_accs[-1]
+
+fig = plt.figure()
+ax=fig.add_subplot(111, label="1")
+ax1=fig.add_subplot(111, label="2", frame_on=False)
+
+lns1 = ax.plot(train_loss, color="g", label="Training loss")
+lns2 = ax.plot(test_loss, color="r", label="Testing loss")
+lns3 = ax1.plot(epoch_accs, color="b", label="Testing accuracy")
+#ax1.xlabel("Number of batch iterations")
+#ax2.ylabel("Loss")
+ax.set_xlabel("Epoch", color="black")
+ax.set_ylabel("Loss", color="black")
+ax.tick_params(axis='x', colors="black")
+ax.tick_params(axis='y', colors="black")
+
+#ax1.xaxis.tick_top()
+ax1.yaxis.tick_right()
+#ax1.set_xlabel('x label 2', color="C1") 
+ax1.set_ylabel('Accuracy', color="b")       
+#ax1.xaxis.set_label_position('top') 
+ax1.yaxis.set_label_position('right') 
+#ax1.tick_params(axis='x', colors="C1")
+ax1.tick_params(axis='y', colors="b")
+
+
+leg = lns1 + lns2 + lns3
+labs = [l.get_label() for l in leg]
+ax1.legend(leg, labs, loc=0)
+plt.savefig("plots/pure_cnn_loss_and_acc_2x2.png")
+
+print("Total training time: " + str(times[-1]))

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/confusion_matrix_pure_cnn.py
Do a small experiment on 6x6

@@ -1,0 +1,45 @@
+import torch
+from torch.utils.data import DataLoader
+from data.pure_cnn_data import Pure_CNN_Data
+from network_for_pure_CNN import PureCNN
+from sklearn.metrics import confusion_matrix
+import seaborn as sn
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+
+size = 6
+output_size = 4 + size
+network = PureCNN(size=size, output_size=output_size) # Yes, no, square, circle, 1, 2, 3, 4, 5, 6
+train_dataset = Pure_CNN_Data("train", size)
+test_dataset = Pure_CNN_Data("test", size)
+batch_size = 8
+train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
+test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=True)
+
+
+y_pred = []
+y_true = []
+
+network.load_state_dict(torch.load("models/sort_of_clevr_220316_114813087345.pt"))
+network.eval()
+# iterate over test data
+for (img, questions, answer) in test_loader:
+        output = network(img, questions) # Feed Network
+
+        output = torch.argmax(output, dim=1).cpu().numpy()
+        y_pred.extend(output) # Save Prediction
+        
+        labels = answer.cpu().numpy()
+        y_true.extend(labels) # Save Truth
+
+# constant for classes
+classes = ('Rectangle', 'Circle', 'Yes', 'No', '1', '2', '3', '4', '5', '6')
+
+# Build confusion matrix
+cf_matrix = confusion_matrix(y_true, y_pred)
+df_cm = pd.DataFrame(cf_matrix/np.sum(cf_matrix), index = [i for i in classes],
+                     columns = [i for i in classes])
+plt.figure(figsize = (12,7))
+sn.heatmap(df_cm, annot=True)
+plt.savefig('plots/confusion_matrix_6x6.png')

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/pure_cnn_training.py

@@ -92,7 +92,7 @@ def init_weights(m):
         torch.nn.init.xavier_uniform(m.weight)
         m.bias.data.fill_(0.01)
    
-size = 2
+size = 6
 output_size = 4 + size
 network = PureCNN(size=size, output_size=output_size) # Yes, no, square, circle, 1, 2, 3, 4, 5, 6
 network.to(device)
@@ -127,7 +127,7 @@ epochs = 25
 train_loss, test_loss, epoch_accs, times = train(network, train_loader, test_loader, loss_function, optimizer, epochs, accuracy_metric, batch_size)
 import pickle
 
-with open('values_of_training_16_03_2022_12_00.pk', 'wb') as fp:
+with open('values_of_training_16_03_2022_12_40_6x6.pk', 'wb') as fp:
     pickle.dump(train_loss, fp)
     pickle.dump(test_loss, fp)
     pickle.dump(epoch_accs, fp)

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/confusion_matrix_pure_cnn.py
Add some new outcomes

@@ -21,7 +21,7 @@ test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=True)
 y_pred = []
 y_true = []
 
-network.load_state_dict(torch.load("models/sort_of_clevr_220316_114813087345.pt"))
+network.load_state_dict(torch.load("models/model_pure_NN_6x6_100_iterations_16_03_2022.pt"))
 network.eval()
 # iterate over test data
 for (img, questions, answer) in test_loader:
@@ -42,4 +42,4 @@ df_cm = pd.DataFrame(cf_matrix/np.sum(cf_matrix), index = [i for i in classes],
                      columns = [i for i in classes])
 plt.figure(figsize = (12,7))
 sn.heatmap(df_cm, annot=True)
-plt.savefig('plots/confusion_matrix_6x6.png')
+plt.savefig('plots/confusion_matrix_6x6_100_iterations.png')

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/pure_cnn_training.py

@@ -123,11 +123,11 @@ loss_function.to(device)
 
 optimizer = torch.optim.Adam(network.parameters(), lr = 3e-4)
 
-epochs = 25
+epochs = 100
 train_loss, test_loss, epoch_accs, times = train(network, train_loader, test_loader, loss_function, optimizer, epochs, accuracy_metric, batch_size)
 import pickle
 
-with open('values_of_training_16_03_2022_12_40_6x6.pk', 'wb') as fp:
+with open('values_of_training_16_03_2022_13_00_6x6_100_epochs.pk', 'wb') as fp:
     pickle.dump(train_loss, fp)
     pickle.dump(test_loss, fp)
     pickle.dump(epoch_accs, fp)

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -15,7 +15,7 @@ import random
 random.seed(0)
 #np.random.seed(args.seed)
 
-width = 6
+width = 2
 out_size = (width ** 2) * 2 # Times two for the distinction between squares and circles
 
 colors = ["red", "green", "blue", "orange", "grey", "yellow"]
@@ -25,9 +25,14 @@ for i, color in enumerate(used_colors):
     cnn = CNNNetwork(out_size=out_size)
     cnns["cnn_" + color] = cnn
 
+# Hove to add these networks in order to work well
+if width < 6:
+    for color in (list(set(colors) - set(used_colors))):
+        cnns["cnn_" + color] = cnn
+
 nets = {}
 nets_ordered = []
-for i, color in enumerate(used_colors):
+for i, color in enumerate(colors):
     net = Network(cnns["cnn_" + color], "cnn_" + color, Adam(cnns["cnn_" + color].parameters(), lr=3e-3), batching=True)
     nets["net_" + color] = net
     nets_ordered.append(net)

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/visualize_pure_cnn_outcomes.py

@@ -1,7 +1,7 @@
 import pickle
 import cv2
 import matplotlib.pyplot as plt
-with open('values_of_training_16_03_2022_12_00.pk', 'rb') as fp:
+with open('values_of_training_16_03_2022_13_00_6x6_100_epochs.pk', 'rb') as fp:
     train_loss = pickle.load(fp)
     test_loss = pickle.load(fp)
     epoch_accs = pickle.load(fp)
@@ -37,6 +37,6 @@ ax1.tick_params(axis='y', colors="b")
 leg = lns1 + lns2 + lns3
 labs = [l.get_label() for l in leg]
 ax1.legend(leg, labs, loc=0)
-plt.savefig("plots/pure_cnn_loss_and_acc_2x2.png")
+plt.savefig("plots/pure_cnn_loss_and_acc_6x6_100_epochs.png")
 
 print("Total training time: " + str(times[-1]))

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/data.py
Training works now for 2x2 - strange issue earlier

@@ -96,6 +96,7 @@ class SORTOFCLEVRDataset(ImageDataset):
             assert(binary_answer >= 4)
             outcome = binary_answer - 3
         sub = {Term("image"): Term("tensor", Term(self.subset, Constant(i)))}
+        #question = sh + "_" + question
         return Query(Term(question, Term("image"), Term(sh), Constant(outcome)), sub)
            
     def __len__(self):

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl

@@ -1,9 +1,7 @@
 % We know that there are two objects in a four grid space. Two shapes possible, two colors possible.
 % The green cnn detects the position, and the shape --> x. If x < size: Shape = rectangle. Else: shape = circle. (x modulo size = position)  
 
-:- use_module(library(cut)).
-
-width(6).
+width(2).
 size(N) :-
     width(Width),
     N is Width * Width.
@@ -14,8 +12,8 @@ states(N) :-
 % [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71]
 % [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]
 % [0, 1, 2, 3, 4, 5, 6, 7]
-nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71]) :: detect_state(red, X, Y_red).
[…]

### 2022-03-16 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -21,18 +21,13 @@ out_size = (width ** 2) * 2 # Times two for the distinction between squares and 
 colors = ["red", "green", "blue", "orange", "grey", "yellow"]
 used_colors = colors[0:width]
 cnns = {}
-for i, color in enumerate(used_colors):
+for color in colors:
     cnn = CNNNetwork(out_size=out_size)
     cnns["cnn_" + color] = cnn
 
-# Hove to add these networks in order to work well
-if width < 6:
-    for color in (list(set(colors) - set(used_colors))):
-        cnns["cnn_" + color] = cnn
-
 nets = {}
 nets_ordered = []
-for i, color in enumerate(colors):
+for color in colors:
     net = Network(cnns["cnn_" + color], "cnn_" + color, Adam(cnns["cnn_" + color].parameters(), lr=3e-3), batching=True)
     nets["net_" + color] = net
     nets_ordered.append(net)
@@ -57,7 +52,7 @@ train_log = train_model(
     1,
     log_iter=1,
     initial_test=False,
-    test_iter=1,
+    test_iter=20,
     test=lambda x: [
         #("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
         ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),

### 2022-03-17 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py
Ready for training on 2x2 with DeepProbLog

@@ -52,7 +52,7 @@ train_log = train_model(
     1,
     log_iter=1,
     initial_test=False,
-    test_iter=20,
+    test_iter=1,
     test=lambda x: [
         #("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
         ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),

### 2022-03-17 deepproblog/src/deepproblog/examples/SORTOFCLEVR/confusion_matrix_deepproblog.py
Create a confusion matrix for the DeepProbLog network as well

@@ -1,0 +1,82 @@
+from network import CNNNetwork
+from deepproblog.network import Network
+from deepproblog.model import Model
+from torch.optim import Adam
+from deepproblog.dataset import DataLoader
+from data.data import SORTOFCLEVRDataset
+from sklearn.metrics import confusion_matrix
+import seaborn as sn
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import torch
+from deepproblog.engines.exact_engine import ExactEngine
+
+width = 2
+out_size = (width ** 2) * 2 # Times two for the distinction between squares and circles
+
+colors = ["red", "green", "blue", "orange", "grey", "yellow"]
+used_colors = colors[0:width]
+cnns = {}
+for color in colors:
+    cnn = CNNNetwork(out_size=out_size)
+    cnns["cnn_" + color] = cnn
+
+nets = {}
+nets_ordered = []
+for color in colors:
+    net = Network(cnns["cnn_" + color], "cnn_" + color, Adam(cnns["cnn_" + color].parameters(), lr=3e-3), batching=True)
+    nets["net_" + color] = net
+    nets_ordered.append(net)
+
+
+train_dataset = SORTOFCLEVRDataset("train", width)
+val_dataset = SORTOFCLEVRDataset("val", width)
+test_dataset = SORTOFCLEVRDataset("test", width)
+loader = DataLoader(train_dataset, 32, shuffle=True)
+test_loader = DataLoader(train_dataset, 32, shuffle=True)
+
+model = Model("/home/jorrit/Data/KU Leuven/Semester 12/Capita Selecta H05N0a/deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl", nets_ordered)
+model.load_state("models/sort_of_clevr_220317_151942876802.pth")
+model.add_tensor_source("train", train_dataset)
+model.add_tensor_source("val", val_dataset)
+model.add_tensor_source("test", test_dataset)
+model.set_engine(ExactEngine(model), cache=True)
+model.eval()
+
+
+y_pred, y_true = [], []
+for i, gt_query in enumerate(test_dataset.to_queries()):
+    test_query = gt_query.variable_output()
+    answer = model.solve([test_query])[0]
+    if len(answer.result) == 0:
+        print("no answer for query {}".format(gt_query))
+    else:
+        max_ans = max(answer.result, key=lambda x: answer.result[x])
+    p = answer.result[max_ans]
[…]

### 2022-03-17 deepproblog/src/deepproblog/examples/SORTOFCLEVR/visualize_deepproblog_outcomes.py

@@ -1,0 +1,45 @@
+import pickle
+import cv2
+import matplotlib.pyplot as plt
+with open('log/log_2x2_deepproblog.log', 'r') as f:
+    content = f.readlines()
+
+train_loss, accuracy = [], []
+for i, row in enumerate(content[3:]):
+    info = row.split(',')
+    accuracy.append(float(info[1]))
+    if i == 0:
+        train_loss.append(0.8007569704786874)
+    else:
+        train_loss.append(float(info[3]))
+    time = info[2]
+fig = plt.figure()
+ax=fig.add_subplot(111, label="1")
+ax1=fig.add_subplot(111, label="2", frame_on=False)
+
+lns1 = ax.plot(train_loss, color="g", label="Training loss")
+#lns2 = ax.plot(test_loss, color="r", label="Testing loss")
+lns3 = ax1.plot(accuracy, color="b", label="Testing accuracy")
+#ax1.xlabel("Number of batch iterations")
+#ax2.ylabel("Loss")
+ax.set_xlabel("Epoch", color="black")
+ax.set_ylabel("Loss", color="black")
+ax.tick_params(axis='x', colors="black")
+ax.tick_params(axis='y', colors="black")
+
+#ax1.xaxis.tick_top()
+ax1.yaxis.tick_right()
+#ax1.set_xlabel('x label 2', color="C1") 
+ax1.set_ylabel('Accuracy', color="b")       
+#ax1.xaxis.set_label_position('top') 
+ax1.yaxis.set_label_position('right') 
+#ax1.tick_params(axis='x', colors="C1")
+ax1.tick_params(axis='y', colors="b")
+
+
+leg = lns1 + lns3
+labs = [l.get_label() for l in leg]
+ax1.legend(leg, labs, loc=5)
+plt.savefig("plots/deepproblog_2x2.png")
+
+print("Total training time: " + str(time))

### 2022-03-17 deepproblog/src/deepproblog/examples/SORTOFCLEVR/confusion_matrix_deepproblog.py
Make sure a good name has been given to the model

@@ -44,7 +44,6 @@ model.add_tensor_source("test", test_dataset)
 model.set_engine(ExactEngine(model), cache=True)
 model.eval()
 
-
 y_pred, y_true = [], []
 for i, gt_query in enumerate(test_dataset.to_queries()):
     test_query = gt_query.variable_output()
@@ -79,4 +78,4 @@ df_cm = pd.DataFrame(cf_matrix/np.sum(cf_matrix), index = [i for i in classes],
                      columns = [i for i in classes])
 plt.figure(figsize = (12,7))
 sn.heatmap(df_cm, annot=True)
-plt.savefig('plots/confusion_matrix_2x2_deepproblog.png')
+plt.savefig('plots/model_deepproblog_2x2.png')

### 2022-03-18 paper/paper.tex
Some notes
Include some figures

@@
     \begin{center}
-    %\includegraphics[width=0.3\textwidth]{sample_own_dataset.png} TODO
+    \includegraphics[width=0.3\textwidth]{sample_image_dataset.png}
     \captionsetup{justification=centering}
@@
 
-\section{COMPARISONS WITH PURE SYSTEM 1 APPROACHES}
+\subsection{COMPARISONS WITH PURE SYSTEM 1 APPROACHES}
 \label{comparison_with_CNN}
+The network based on pure neural predicates is able to recognize the questions quickly, however, seems to experience difficulties when having to decide for the correct answer.
+This can clearly be seen in the confusion matrix (Figure \ref{fig:confusion_matrix_6x6_pure_NN}).
+% TODO add confusion_matrix_pure_NN_6x6_clear_mistakes here
+
+\begin{figure}[H]
+    \begin{center}
+    \includegraphics[width=0.3\textwidth]{confusion_matrix_pure_NN_6x6_clear_mistakes.png} 
+    \captionsetup{justification=centering}
+    \caption{The confusion matrix of the 6x6 dataset on a purely Neural Network based model}
+    \label{fig:confusion_matrix_6x6_pure_NN}
+    \end{center}
+\end{figure}
 

### 2022-03-18 paper/paper.tex
Write some further

@@
 
-%\let\thefootnote\relax\footnotetext{\hspace*{-5mm}This footnote will be used only by the Editor and Associate Editors.~The edition in this area is not permitted to the authors.
-This footnote must not be removed while editing the manuscript.}
-
-%\section*{NOMENCLATURE}
-
-%\symbolnomenclature{$P$}{Number of poles.}
-%\symbolnomenclature{$V_{qd}$}{Stator voltage \textit{dq} components.}
-%\symbolnomenclature{$I_{qd}$}{Stator current \textit{dq} components.}
-
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-%Sections
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-
-%Introduction
-
 \section{INTRODUCTION}
@@
 System 2, on the other hand, will use this extracted information for deriving certain properties of objects\footnote{For example, finding the shape of the green object, or deriving if it is located on the left hand side of the image.}, or even for capturing the relations\footnote{Here, one could think of deriving if an object is located to the left of another object, or also for finding the number of circles in the image.} between the objects.
+
+\section{ORGANIZATION OF THE PAPER}
 
@@
 This can clearly be seen in the confusion matrix (Figure \ref{fig:confusion_matrix_6x6_pure_NN}).
-% TODO add confusion_matrix_pure_NN_6x6_clear_mistakes here
+% TODO also talk about confusion matrix of deepproblog
 
@@
 
+% Denote difference between epochs and iterations!
+% Trained on CPU
+
+It is clear that the network trained with DeepProbLog is able to learn way faster then the purely NN based approach, if measured in the number of iterations \footnote{By the number of iterations, the number of training steps on a batch is meant.}.
+However, the differences in training time are much less significant% TODO give concrete measures
+, due to the high computational cost associated with the arithmetic parts of the circuit (i.e. the semirings).
+
+\section{CONCLUSIONS}
+
 \section{APPENDIX}
@@
 
-\section{ORGANIZATION OF THE PAPER}
-%TODO. Put this above the literature study
-
-This section presents the main issues for editing the manuscript.
-
-\subsection{General Organization}
-
-The papers that shall be published in the Brazilian Power Electronics Journal must contain the following main sections:
-1) Title; 2) Authors and Affiliations; 3) Abstract and Keywords; 4) Introduction; 5) Body Text; 6) Conclusions; \linebreak 7) References; 8) Biographies.
-This order must be respected, unless the authors add some items, such as: Nomenclature; Appendices and Acknowledgements.
-
-Some comments regarding the main items of the manuscripts are presented below.
-
-\subsubsection{Title}
-
-The title of the paper should be as succinct as possible, stating the subject of the paper in a very clear manner.
-It should be centered at the top of the first page, in bold, type size 14 points, with the whole title in capital letters.
-
-\subsubsection{Authors and affiliations}
-
-Below the title (leaving one blank line), also centered, the name(s) of the author(s) must be included.
-The middle names may be abbreviated, but the first and last names must be written in their complete forms (type size 12 points).
-Immediately below the authors' names, their affiliations, with city, state and country, must be informed (type size 10 points).~The electronic addresses must be informed just below the affiliations (type size 10 points).
-
-\subsubsection{Abstract and keywords}
-
-This part is considered one of the most important in the whole paper. It is based on information in Abstract and Keywords that technical papers are indexed and stored in databases.
-
-The Abstract should have no more than 200 words, indicating the main ideas contained in the paper, as well as procedures and obtained results.
-The Abstract should not be confused with the Introduction and should not have any abbreviations, references, figures, etc.
-For writing the Abstract, as well as the whole manuscript, you should use passive voice, e.
-g.,  ``...
-the experimental results show that...'' instead of ``...~the results we obtained show that...''.~The word Abstract must be written both in italic and in bold.
-The Abstract text should be in bold.
-
-Keywords are index terms that identify the main topics of the paper. The term Keywords must be both in italic and bold. The Keywords themselves should be in bold.
-
-\subsubsection{Introduction}
-
-The Introduction must prepare the reader for the paper he/she will read, including a historical overview of the subject and also presenting the main contributions of the paper.
-The Introduction must not be similar to the Abstract and it is the first section of the paper to be numbered as a section.
-
-\subsubsection{Body text}
-
-The authors must organize the body text in various sections, which should contain important information about the proposal of the paper, facilitating its comprehension for readers.
-
-\subsubsection{Conclusions}
-
-The conclusions should be as clear as possible, highlighting the importance of the paper in the respective research area.
-The advantages and disadvantages of the proposed subject should be clearly emphasized, as well as the obtained results and possible applications.
-
-\subsubsection{References}
-
-The citation of references throughout the text should appear between square brackets, just before the punctuation mark at the end of the sentence in which the reference is inserted.
-Only the number of the references should be used, avoiding citations such as ``...
-according to the reference [2]...''.
-
-Papers that were accepted for publication, but were not published yet, should also be in the references along with the citation ``in Press''.
-
-Papers from journals and conferences must begin with the name of the authors (initials followed by the last name), followed by the title, journal or conference name (in italic), number of volume, pages, month and year of publication.
-
-Regarding books, following the name of the authors (initials followed by last name), the title should be in italic, and then should come the publisher, number of edition and place and year of publication.
-
-At the end of these guidelines, there is an example of how the references should be inserted~%\cite{refbib1,refbib2,refbib3,refbib4,refbib5,refbib6,refbib7,refbib8}.
-
-%\nocite{refbib1}
-%\nocite{refbib2}
-%\nocite{refbib3}
-%\nocite{refbib4}
-%\nocite{refbib5}
-%\nocite{refbib6}
-%\nocite{refbib7}
-%\nocite{refbib8}
-
-\subsubsection{Biographies}
-
-The biographies of the authors should appear in the same order as in the beginning of the paper and should basically contain the following items:
-\begin{itemize}
-	\item Full name (in bold and underlined);
-	\item Place and year of undergraduation and graduation conclusions;
-	\item Professional experience (Institutions and companies in which they have worked, number of patents obtained, areas of expertise, relevant scientific activities, scientific societies in which they are members, etc.).
-\newline
-\end{itemize}
-
-In case additional items are used, such as Nomenclature, Appendices and Acknowledgements, the following instructions should be considered:
-
-\subsubsection{Nomenclature}
-
-The nomenclature consists of the definition of quantities and symbols used throughout the paper.
-Its inclusion is not mandatory and this item must not be numbered.
-If this item is included, it should precede the Introduction.
-In case the authors do not include this item, the  definition of quantities and symbols must occur during the text, right after they appear.
-In the beginning of these guidelines there is an example of this optional item.
-
-\subsubsection{Acknowledgements and appendices}
-
-The acknowledgements to any collaborators, as well as appendices, do not receive any numeration and should be at the end of the text, before the references.
-At the end of this text there is an example of this optional item.
-
-On the last page of the paper, the authors should distribute the contents evenly, using both columns, in a way that both end in a parallel manner.
-
-\subsection{Organization of the Sections of the Paper}
-
-The organization of the manuscript in titles and subtitles is important to divide it in sections, which help the reader to find subjects of interest in the paper.
-They also help the authors to develop their paper in an orderly form.
-The paper can be organized in primary, secondary and tertiary sections.
-
-The primary sections are the titles of the actual sections.
-They are written in capital letters in the center of the column separated by a blank line above and another one below them, and sequential Roman numerals should be used.
-
-The secondary sections are the subtitles of the sections.
-Just the first letter of each word of the section should be written with a capital letter.
-It should be located at the left part of the column being separated by a blank line above from the rest of the text.
-The designation of the secondary sections is done with letters in uppercase form, followed by a dot.
-They should be in italic.
-
-The tertiary sections are subdivisions of the secondary sections.
-Only the first letter of the first word of the section should be a capital letter.
-The designation of the tertiary sections should be done with Arabic numerals, followed by parentheses.
-They should be in italic.
-
-\section{OTHER INSTRUCTIONS}
-
-\subsection{Editorial Rules}
-
-For papers with multiple authors, it is necessary to inform the order of presentation of the authors and filling out the Copyright form at the https://mc04.manuscriptcentral.com/revistaep, authorizing the publication of the paper.
-
-The Brazilian Power Electronics Journal should be considered source of original publication.
-It reserves its right to make normative, spelling and grammatical modifications in the original files, but respecting the style of the authors.
-The final versions cannot be sent to the authors.
-
-The published papers will become property of the Brazilian Power Electronics Journal, and its total or partial reprinting must be authorized by SOBRAEP.
-
-Figures, tables and equations should follow the following guidelines.
-
-\subsection{Figures and Tables}
-
-Tables and figures (drawings or pictures) should be inserted in the text right after they are mentioned for the first time, as long as they fit the size of the columns; if necessary, use the whole page.
-Figures resolution should be at least 300 dpi and vector files should be preferably used for better print quality.
-Table captions should be above the tables and figure captions should be below the figures.
-The tables should have titles and they are designated by the word Table, being numbered in sequence by Roman numerals.
-Table captions must be centered and in bold.
-
-Figures also need captions and they are designated by Figure in the text (Fig.
-in the caption itself), numbered with Arabic numerals in a sequenced manner, left- and right- justified, as shown in the example.
-The designation of the parts of a figure is done by adding lowercase letters to the numbers of the figures starting with the letter a, e.g.
-Figure 1(a).
-
-\begin{figure}[H]
-%	\includegraphics[scale=1]{figura.eps}
-	\centering
-	\caption{Magnetization as a function of applied field. (Note that ``Fig.'' is abbreviated and there is a period after the figure number followed by two spaces.)}
-	\label{fig:fig1}
-\end{figure}
-
-To better understand graphs, the definition of their axes should be done with words not letters, except when referring to waveforms and phase planes.
-The units should be between parentheses.
-For example, use the denomination ``Magnetization (A/m)'', instead of ``M (A/m)''.
-
-Figures and tables should be positioned preferably in the beginning or the end of the column, avoiding putting them in the middle.
-Avoid tables and figures whose sizes exceed the size of the columns.
-The figures should preferentially be in black, with a white background, since the printed version of the journal is in black and white.
-Their lines should be thick, so the impression is readable.
-
-\subsection{Abbreviations and Acronyms}
-Abbreviations and acronyms must be defined the first time they are used in the text, e.g. ``... Pulse-Width Modulation (PWM)...''.
-
-\subsection{Equations}
-Number equations consecutively with equation numbers in parentheses flush with the right margin, as in (1).
-The equations should be written in a compact form, centered in the column.
-If a nomenclature section is not included in the beginning of the text, the quantities should be defined right after the equation, such as:
-\begin{equation}
-	\Delta I_{L}=I_{o}+\frac{\sqrt{3}}{2}\frac{V_{i}}{Z}
-\end{equation}
-where:
-
-\symboldescription{$\Delta I_{L}$}{resonant inductor peak current;}
-\symboldescription{$I_o$}{load current;}
-\symboldescription{$V_i$}{source voltage;}
-\symboldescription{$Z$}{characteristic impedance.}
-
-\section{CONCLUSIONS}
-This paper was fully written in accordance with the guidelines for submissions of papers in English.
-
-\section*{ACKNOWLEDGEMENTS}
-The authors thank John Doe for the collaboration of preparing this paper. This Project was financed by the CNPq (xxyyzz process).
-
 \bibliographystyle{bib_sobraep}
@@
 
-\balance
+%\balance
 

### 2022-03-18 paper/paper.tex
Write paper overview

@@
 \section{INTRODUCTION}
-The Neuro Symbolic AI community is growing rapidly, indicating that people start to recognize the value of the field.
 The Neuro Symbolic AI field is interested in building a bridge between the robustness of probabilistic knowledge, with the well-known popularity and proven strengths of deep neural networks.
@@
 System 1 will be required in order to gain an understanding of the image under investigation, with in particular their shapes and colors.
-System 2, on the other hand, will use this extracted information for deriving certain properties of objects\footnote{For example, finding the shape of the green object, or deriving if it is located on the left hand side of the image.}, or even for capturing the relations\footnote{Here, one could think of deriving if an object is located to the left of another object, or also for finding the number of circles in the image.} between the objects.
+System 2, on the other hand, will use this extracted information for deriving certain properties of objects\footnote{For example, finding the shape of the green object, or deriving if it is located on the left hand side of the image.}, or even for capturing the relations\footnote{Here, one could think of counting the number of circles in the image.} between the objects.
 
 \section{ORGANIZATION OF THE PAPER}
+This paper will first provide some background in Section \ref{sec:literature_survey} on certain types of datasets that are typically used for Visual Question Answering purposes.
+% Maybe also more terminology?
+Then, Section \ref{sec:approach} will dive deeper in the different components constituting the overall system.
+Once the general structure has been outlined, Section \ref{sec:experiments} provides some results of conducted experiments.
+A main focus in this paper is to outline the advantages of using a Neuro-Symbolic AI approach (offered by the DeepProbLog framework), instead of a purely neural network based approach.
+These specific experiments are listed in Subsection \ref{subsec:experiments_NN_vs_deepproblog}.
+Finally, the main findings of this paper are repeated in Section \ref{sec:conclusions}.
 
@@
 Seen from an optimization viewpoint, errors made during prediction in this setup can be targeted exactly, which makes the optimization process also more targeted, and hence more efficient.
-Finally, this paper also provides evidence for these statements, since in Section \ref{comparison_with_CNN}, the comparison between a VQA implementation with DeepProbLog is made with a purely CNN based approach.
+Finally, this paper also provides evidence for these statements, since in Subsection \ref{subsec:experiments_NN_vs_deepproblog}, the comparison between a VQA implementation with DeepProbLog is made with a purely CNN based approach.
 % TODO is this the case?
@@
 \section{APPROACH}
+\label{sec:approach}
 The implementation process involved three main parts:
@@
 \section{EXPERIMENTS}
+\label{sec:experiments}
 
 \subsection{COMPARISONS WITH PURE SYSTEM 1 APPROACHES}
-\label{comparison_with_CNN}
+\label{subsec:experiments_NN_vs_deepproblog}
 The network based on pure neural predicates is able to recognize the questions quickly, however, seems to experience difficulties when having to decide for the correct answer.
@@
 \section{CONCLUSIONS}
+\label{sec:conclusions}
 

### 2022-03-19 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl
Visualize the outcome of the 6x6 training on a plot

@@ -1,7 +1,7 @@
 % We know that there are two objects in a four grid space. Two shapes possible, two colors possible.
 % The green cnn detects the position, and the shape --> x. If x < size: Shape = rectangle. Else: shape = circle. (x modulo size = position)  
 
-width(2).
+width(6).
 size(N) :-
     width(Width),
     N is Width * Width.
@@ -12,8 +12,8 @@ states(N) :-
 % [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71]
 % [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]
 % [0, 1, 2, 3, 4, 5, 6, 7]
-nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7]) :: detect_state(red, X, Y_red).
-nn(cnn_green,[X], Y_green, [0, 1, 2, 3, 4, 5, 6, 7]) :: detect_state(green, X, Y_green).
+nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71]) :: detect_state(red, X, Y_red).
[…]

### 2022-03-19 deepproblog/src/deepproblog/examples/SORTOFCLEVR/sort_of_clevr.py

@@ -15,7 +15,7 @@ import random
 random.seed(0)
 #np.random.seed(args.seed)
 
-width = 2
+width = 6
 out_size = (width ** 2) * 2 # Times two for the distinction between squares and circles
 
 colors = ["red", "green", "blue", "orange", "grey", "yellow"]
@@ -29,6 +29,7 @@ nets = {}
 nets_ordered = []
 for color in colors:
     net = Network(cnns["cnn_" + color], "cnn_" + color, Adam(cnns["cnn_" + color].parameters(), lr=3e-3), batching=True)
+    #net.cuda()
     nets["net_" + color] = net
     nets_ordered.append(net)
 
@@ -49,10 +50,10 @@ train_accs = []
 train_log = train_model(
     model,
     loader,
-    1,
+    5,
     log_iter=1,
-    initial_test=False,
-    test_iter=20,
+    initial_test=True,
+    test_iter=25,
     test=lambda x: [
         #("Val_accuracy", get_confusion_matrix(x, val_dataset, eps=1e-6).accuracy()),
         ("Test_accuracy", get_confusion_matrix(x, test_dataset, eps=1e-6).accuracy()),

### 2022-03-19 deepproblog/src/deepproblog/examples/SORTOFCLEVR/visualize_deepproblog_outcomes.py

@@ -1,15 +1,17 @@
 import pickle
 import cv2
 import matplotlib.pyplot as plt
-with open('log/log_2x2_deepproblog.log', 'r') as f:
+with open('log/log_6x6_deepproblog_18_03_2022.log', 'r') as f:
     content = f.readlines()
 
-train_loss, accuracy = [], []
+train_loss, accuracy, acc_iter = [], [], []
 for i, row in enumerate(content[3:]):
     info = row.split(',')
-    accuracy.append(float(info[1]))
+    if info[1] != '':
+        accuracy.append(float(info[1]))
+        acc_iter.append(int(info[0]))
     if i == 0:
-        train_loss.append(0.8007569704786874)
+        train_loss.append(1.138294846170652)
     else:
         train_loss.append(float(info[3]))
     time = info[2]
@@ -19,7 +21,7 @@ ax1=fig.add_subplot(111, label="2", frame_on=False)
 
 lns1 = ax.plot(train_loss, color="g", label="Training loss")
 #lns2 = ax.plot(test_loss, color="r", label="Testing loss")
-lns3 = ax1.plot(accuracy, color="b", label="Testing accuracy")
+lns3 = ax1.plot(acc_iter, accuracy, color="b", label="Testing accuracy")
 #ax1.xlabel("Number of batch iterations")
 #ax2.ylabel("Loss")
 ax.set_xlabel("Epoch", color="black")
@@ -35,11 +37,11 @@ ax1.set_ylabel('Accuracy', color="b")
 ax1.yaxis.set_label_position('right') 
 #ax1.tick_params(axis='x', colors="C1")
 ax1.tick_params(axis='y', colors="b")
-
+ax1.get_xaxis().set_ticks([])
 
 leg = lns1 + lns3
 labs = [l.get_label() for l in leg]
 ax1.legend(leg, labs, loc=5)
-plt.savefig("plots/deepproblog_2x2.png")
+plt.savefig("plots/deepproblog_6x6_18_03_2022.png")
 
 print("Total training time: " + str(time))

### 2022-03-19 deepproblog/src/deepproblog/examples/SORTOFCLEVR/confusion_matrix_deepproblog.py
Add confusion matrix for the 6x6 case

@@ -12,7 +12,7 @@ import matplotlib.pyplot as plt
 import torch
 from deepproblog.engines.exact_engine import ExactEngine
 
-width = 2
+width = 6
 out_size = (width ** 2) * 2 # Times two for the distinction between squares and circles
 
 colors = ["red", "green", "blue", "orange", "grey", "yellow"]
@@ -37,7 +37,7 @@ loader = DataLoader(train_dataset, 32, shuffle=True)
 test_loader = DataLoader(train_dataset, 32, shuffle=True)
 
 model = Model("/home/jorrit/Data/KU Leuven/Semester 12/Capita Selecta H05N0a/deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl", nets_ordered)
-model.load_state("models/sort_of_clevr_220317_151942876802.pth")
+model.load_state("models/model_deepproblog_6x6_18_03_2022.pth")
 model.add_tensor_source("train", train_dataset)
 model.add_tensor_source("val", val_dataset)
 model.add_tensor_source("test", test_dataset)
@@ -45,9 +45,9 @@ model.set_engine(ExactEngine(model), cache=True)
 model.eval()
 
 y_pred, y_true = [], []
-for i, gt_query in enumerate(test_dataset.to_queries()):
-    test_query = gt_query.variable_output()
-    answer = model.solve([test_query])[0]
+for i, gt_query in enumerate(val_dataset.to_queries()):
+    val_query = gt_query.variable_output()
+    answer = model.solve([val_query])[0]
     if len(answer.result) == 0:
         print("no answer for query {}".format(gt_query))
     else:
@@ -55,7 +55,7 @@ for i, gt_query in enumerate(test_dataset.to_queries()):
     p = answer.result[max_ans]
     predicted = int(max_ans.args[gt_query.output_ind[0]])
     actual = int(gt_query.output_values()[0])
-    question = str(test_query)[6:]
+    question = str(val_query)[6:]
     if question.startswith("horizontal") or question.startswith("vertical"):
         new_predicted = predicted + 2
         new_actual = actual + 2
@@ -70,7 +70,7 @@ for i, gt_query in enumerate(test_dataset.to_queries()):
     y_true.append(new_actual) # Save Truth
 
 # constant for classes
-classes = ('Rectangle', 'Circle', 'Yes', 'No', '1', '2')
[…]

### 2022-03-19 deepproblog/src/deepproblog/examples/SORTOFCLEVR/confusion_matrix_pure_cnn.py

@@ -25,13 +25,13 @@ network.load_state_dict(torch.load("models/model_pure_NN_6x6_100_iterations_16_0
 network.eval()
 # iterate over test data
 for (img, questions, answer) in test_loader:
-        output = network(img, questions) # Feed Network
+    output = network(img, questions) # Feed Network
 
-        output = torch.argmax(output, dim=1).cpu().numpy()
-        y_pred.extend(output) # Save Prediction
-        
-        labels = answer.cpu().numpy()
-        y_true.extend(labels) # Save Truth
+    output = torch.argmax(output, dim=1).cpu().numpy()
+    y_pred.extend(output) # Save Prediction
+
+    labels = answer.cpu().numpy()
+    y_true.extend(labels) # Save Truth
 
 # constant for classes
 classes = ('Rectangle', 'Circle', 'Yes', 'No', '1', '2', '3', '4', '5', '6')

### 2022-03-19 paper/paper.tex
Write further & import the logical statements

@@
 \documentclass[english]{sobraep}
+\usepackage{minted}
 
@@
 \maketitle
+
+% TODO fix the numbering (also subsection = A)
+% TODO also maybe include some results from other papers.
 
@@
 \section{ORGANIZATION OF THE PAPER}
-This paper will first provide some background in Section \ref{sec:literature_survey} on certain types of datasets that are typically used for Visual Question Answering purposes.
-% Maybe also more terminology?
+This paper will first provide some necessary background in Section \ref{sec:literature_survey} on certain types of datasets that are typically used for Visual Question Answering purposes.
 Then, Section \ref{sec:approach} will dive deeper in the different components constituting the overall system.
-Once the general structure has been outlined, Section \ref{sec:experiments} provides some results of conducted experiments.
+Section \ref{sec:experiments}, furthermore, provides some results of conducted experiments.
 A main focus in this paper is to outline the advantages of using a Neuro-Symbolic AI approach (offered by the DeepProbLog framework), instead of a purely neural network based approach.
@@
 the rule based knowledge base).
-Intuitively, it makes sense that if certain facts of the world are known\footnote{They can be encoded, e.g.
+Intuitively, it makes sense that if certain facts of the world are known\footnote{Facts can be encoded, e.g.
 counting the number of spheres is simply a matter of detecting all the spheres in the image, after which a mathematical summation is a statement in the knowledge base.}, learning can proceed much more quickly\footnote{Not to say that learning might even be impossible if a lot of background knowledge is required.}.
-Seen from an optimization viewpoint, errors made during prediction in this setup can be targeted exactly, which makes the optimization process also more targeted, and hence more efficient.
+Seen from an optimization viewpoint, errors made during prediction in this setup can be targeted exactly, which makes the optimization process more targeted as well, and hence more efficient.
 Finally, this paper also provides evidence for these statements, since in Subsection \ref{subsec:experiments_NN_vs_deepproblog}, the comparison between a VQA implementation with DeepProbLog is made with a purely CNN based approach.
-% TODO is this the case?
 
-This paper is based on the CLEVR dataset, but uses however a much more simplified version.
+This paper is inspired on the CLEVR dataset, but uses however a much more simplified version.
 In essence, it is almost like the Sort-Of-CLEVR dataset \cite{sort_of_clevr_dataset}.
@@
 
-\begin{figure}[H]
+\begin{figure}[htp]
     \begin{center}
-    \includegraphics[width=0.3\textwidth]{sort_of_clevr.png}
+    \fbox{\includegraphics[width=0.25\textwidth]{sort_of_clevr.png}}
     \captionsetup{justification=centering}
@@
 
-As explained earlier, both system 1 and system 2 are required for these types of VQA's.
+As illustrated earlier, both system 1 and system 2 are required for these types of VQA's.
 
@@
     \item Generation of data.
+    \item Linking the data and controlling the training process in pure Python code.
     \item Creation of the logical part with DeepProbLog statements.
-    \item Linking the data and controlling the training process in pure Python code.
 \end{enumerate}
 
-% TODO maybe elaborate why I switched from having a CNN per square in the grid, to one CNN per color.
-
 \subsection{Generation of data}
-As mentioned in Section \ref{sec:literature_survey}, the data used in this application is based on the Sort Of CLEVR dataset, with one extra simplification.
-Given that the logical part will have to decide whether an object is located on the left side of an image, the neural network will have to convey positional information to the logical part.
+As mentioned in Section \ref{sec:literature_survey}, the data used in this application is based on the Sort-Of-CLEVR dataset, with one extra simplification.
+Given that the logical part will have to decide whether an object is for example located on the left side of an image, the neural network will have to convey positional information to the logical part.
 Hence, each discrete position will have to be encoded by a possible outcome of the neural network.
 Therefore, objects may only be located at certain places in a grid.
-In this application, a grid of 2x2, 4x4 and 6x6 has been used.
+In this paper, results on a grid of 2x2 and 6x6 are discussed.
 
-The data generator that was used for the creation of the Sort Of CLEVR dataset has been modified in order to place objects in the mentioned grid positions \cite{sort_of_clevr_dataset}.
-An example of a generated image is given in Figure \ref{fig:sample_image_own_dataset}.
+The data generator that was used for the creation of the Sort-Of-CLEVR dataset has been modified in order to place objects in the mentioned grid positions \cite{sort_of_clevr_dataset}.
+An example of a generated image is given in Figure \ref{fig:sample_image_own_dataset}, where the difference with Figure \ref{fig:sample_image_sort_of_clevr} is the grid-layout.
 
-\begin{figure}[H]
+\begin{figure}[htp]
     \begin{center}
-    \includegraphics[width=0.3\textwidth]{sample_image_dataset.png}
+    \fbox{\includegraphics[width=0.3\textwidth]{sample_image_dataset.png}}
     \captionsetup{justification=centering}
@@
 
-These images are accompanied with three non-binary questions and one binary question. For each question, a random object is chosen. The possibilities are:
-\begin{enumerate}
+These images are accompanied with a question about a random object, which can be one of the following:
+\begin{itemize}
     \item Non-binary - What is the shape of this object \footnote{I.e. the shape will be either a square or a circle.}?
@@
     \item Non-binary - Is this object located on the bottom side of the image?
-    \item Binary - How many objects have the same shape of this object?
-\end{enumerate}
+    \item Binary - How many objects have the same shape as this object?
+\end{itemize}
 
 These questions are encoded in a one-hot encoding, after which they are stored in a CSV file, along with the expected answers.
-A training set, a validation set, and a test set are generated.
-% Validation set useful?
+To make the training process more efficient, a training and test dataset has been generated beforehand.
 
 \subsection{Controlling the training process}
-The overall training process is controlled via the Python interfaces of DeepProbLog, along with general PyTorch implementations of the CNN's.
+The overall training process is controlled via the Python API of DeepProbLog, along with general PyTorch implementations of the CNN's.
 First of all, CNN's are defined with PyTorch.
-A relatively simple network is used, where the input is given as a square RGB image of 100 pixels wide, which is transformed by the CNN into 72 output features for the 6x6 grid.
+A relatively simple network is used, where the input is given as a square RGB image of 100 pixels wide, which is transformed by the CNN into 72 output features for the 6x6 grid\footnote{For the 2x2 grid example, 8 output features are required.}.
 Each color that is present in the image has its accompanied CNN network, hence the 72 output features encode the possible positions of the object with that color, along with their shape, which can be either square or circular ($6 \cdot 6 \cdot 2 = 72$).
@@
 The most challenging part here is the transformation from the generated data to specific query mappings and their outcome.
-One of the questions are chosen, and a correct mapping between a predicate in the logical rule encoding file and the answer is set up.
 
@@
 Once the CNN belonging to a specific color has determined the position and the shape of that object, logical rules can deduce whether this object is located on the left hand side of the image, on the bottom side, and how many objects have the same shape.
-The logical rule program has been listed in Appendix \ref{appendix:logical_rule_encodings}
+The logical rule program has been listed in Appendix \ref{appendix:logical_rule_encodings}.
 
@@
 \label{subsec:experiments_NN_vs_deepproblog}
+% General outline of pure NN structure
+
 The network based on pure neural predicates is able to recognize the questions quickly, however, seems to experience difficulties when having to decide for the correct answer.
@@
 \label{appendix:logical_rule_encodings}
-% TODO put logical rules here
+\inputminted[breaklines]{prolog}{"/home/jorrit/Data/KU Leuven/Semester 12/Capita Selecta H05N0a/deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl"}
 

### 2022-03-19 paper/paper.tex
Write further

@@
 A main focus in this paper is to outline the advantages of using a Neuro-Symbolic AI approach (offered by the DeepProbLog framework), instead of a purely neural network based approach.
-These specific experiments are listed in Subsection \ref{subsec:experiments_NN_vs_deepproblog}.
+These experiments are listed in Section \ref{sec:experiments}.
 Finally, the main findings of this paper are repeated in Section \ref{sec:conclusions}.
@@
 
-\begin{figure}[H]
+\begin{figure}[htp]
     \begin{center}
@@
 \label{sec:experiments}
+The main focus of this paper is to outline the advantages of using a Neuro-Symbolic AI approach (offered by the DeepProbLog framework), instead of a purely neural network based approach.
+Therefore, another purely neural network based approach had to be implemented.
+Not all details will be listed here, but the main idea is that the image has to be fused with the question, after which a prediction can be made\footnote{Possible answers on the questions are: rectangle, circle, yes, no, 1, 2, 3, 4, 5 and 6.
+Hence, the neural network will have 10 output nodes.}.
+The general structure of this network is given in Figure \ref{fig:pure_nn_network}.
+
+\begin{figure}[htp]
+    \begin{center}
+    \includegraphics[width=0.45\textwidth]{pure_nn_architecture.png} 
+    \captionsetup{justification=centering}
+    \caption{Abstract representation of the purely neural network based architecture}
+    \label{fig:pure_nn_network}
+    \end{center}
+\end{figure}
 
@@
 \label{subsec:experiments_NN_vs_deepproblog}
-% General outline of pure NN structure
+\subsubsection{Experiment: 2x2 grid}
+The loss curves of both the DeepProbLog approach, as well as the purely neural network based approach, are visualized respectively in Figure \ref{fig:loss_curve_deepproblog_2x2} and Figure \ref{fig:loss_curve_pure_NN_2x2}.
+
+\begin{figure}[htp]
+    \begin{center}
+    \includegraphics[width=0.3\textwidth]{loss_curve_deepproblog_2x2.png} 
+    \captionsetup{justification=centering}
+    \caption{DeepProbLog 2x2: Loss curve}
+    \label{fig:loss_curve_deepproblog_2x2}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htp]
+    \begin{center}
+    \includegraphics[width=0.3\textwidth]{loss_curve_pure_NN_2x2.png} 
+    \captionsetup{justification=centering}
+    \caption{Pure NN based approach: Loss curve}
+    \label{fig:loss_curve_pure_NN_2x2}
+    \end{center}
+\end{figure}
 

### 2022-03-19 paper/paper.tex
Write about 2x2 experiments

@@
     \begin{center}
-    \includegraphics[width=0.3\textwidth]{loss_curve_deepproblog_2x2.png} 
+    \includegraphics[width=0.45\textwidth]{loss_curve_deepproblog_2x2.png} 
     \captionsetup{justification=centering}
@@
     \begin{center}
-    \includegraphics[width=0.3\textwidth]{loss_curve_pure_NN_2x2.png} 
+    \includegraphics[width=0.45\textwidth]{loss_curve_pure_NN_2x2.png} 
     \captionsetup{justification=centering}
@@
 \end{figure}
+An extremely important remark to be made is the difference between `Number of iterations' and `Number of epochs'.
+By the number of iterations, the number of forward and backward passes of a batch (with size 32) is meant, whereas the number of epochs denote the number of times all the images of the training set are forward and backwardly passed.
+In this application, a training size of 10 000 was used, hence one epoch consists of 312.5 iterations.
+
+From the loss curves, it is clear that both approaches seem to converge to an accuracy of 100\%.
+However, DeepProbLog only requires around 40 iterations, whereas the purely neural network based approach requires at least 250 000 iterations.
+This again demonstrates the value of neuro-symbolic AI.
+
+On the other hand, one has to consider the actual running times for those iterations.
+DeepProbLog takes around 10 minutes to finish its 160 iterations, while the purely neural network based approach requires around 15 minutes to finish 250 000 iterations.
+Taking into consideration that the purely neural network based approach can be accelerated massively (by using GPU's), while DeepProbLog can't\footnote{DeepProbLog offers the ability to send the CNN to a GPU for faster inference, however, the arithmetic operators (i.e.
+semirings) of DeepProbLog work on the CPU.
+These arithmetic operators possess by far the highest computational cost.}, it is clear that DeepProbLog trains much more targeted, but is computationally extremely heavy (at least for now).
+
+\subsubsection{Experiment: 6x6 grid}
 

### 2022-03-19 paper/paper.tex
Write further

@@
     \captionsetup{justification=centering}
-    \caption{Pure NN based approach: Loss curve}
+    \caption{Pure NN based approach 2x2: Loss curve}
     \label{fig:loss_curve_pure_NN_2x2}
@@
 On the other hand, one has to consider the actual running times for those iterations.
-DeepProbLog takes around 10 minutes to finish its 160 iterations, while the purely neural network based approach requires around 15 minutes to finish 250 000 iterations.
+DeepProbLog takes around 10 minutes to finish its 160 iterations, while the purely neural network based approach requires around 5 minutes to finish 250 000 iterations.
 Taking into consideration that the purely neural network based approach can be accelerated massively (by using GPU's), while DeepProbLog can't\footnote{DeepProbLog offers the ability to send the CNN to a GPU for faster inference, however, the arithmetic operators (i.e.
@@
 \subsubsection{Experiment: 6x6 grid}
-
-The network based on pure neural predicates is able to recognize the questions quickly, however, seems to experience difficulties when having to decide for the correct answer.
-This can clearly be seen in the confusion matrix (Figure \ref{fig:confusion_matrix_6x6_pure_NN}).
-% TODO also talk about confusion matrix of deepproblog
+The loss curves for the 6x6 experiment of DeepProbLog and the neural network based approach are depicted in respectively Figure \ref{fig:loss_curve_deepproblog_6x6} and Figure \ref{fig:loss_curve_pure_NN_6x6}.
 
@@
     \begin{center}
-    \includegraphics[width=0.3\textwidth]{confusion_matrix_pure_NN_6x6_clear_mistakes.png} 
+    \includegraphics[width=0.45\textwidth]{loss_curve_deepproblog_6x6.png} 
     \captionsetup{justification=centering}
-    \caption{The confusion matrix of the 6x6 dataset on a purely Neural Network based model}
-    \label{fig:confusion_matrix_6x6_pure_NN}
+    \caption{DeepProbLog 6x6: Loss curve}
+    \label{fig:loss_curve_deepproblog_6x6}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htp]
+    \begin{center}
+    \includegraphics[width=0.45\textwidth]{loss_curve_pure_NN_6x6.png} 
+    \captionsetup{justification=centering}
+    \caption{Pure NN based approach 6x6: Loss curve}
+    \label{fig:loss_curve_pure_NN_6x6}
+    \end{center}
+\end{figure}
+
+In these experiments, the training time of the purely neural network approach was 20 minutes\footnote{For fair speed estimation, training has been conducted on the CPU.}, while the training time of the DeepProbLog approach was a little under eight hours\footnote{However, it should be mentioned that approximately half of the time was spent on calculating the accuracy each time, since the whole testing training set had to be forwarded through the network, while for the training iterations this is only one batch.}.
+
+The most important observation here is that the purely neural network approach overfits quickly.
+Another important remark is the fact that both approaches are clearly not longer able to attain 100\% accuracy.
+
+Confusion matrices indicate where typical mistakes are made.
+
+\begin{figure}[htp]
+    \begin{center}
+    \includegraphics[width=0.3\textwidth]{confusion_matrix_6x6_deepproblog.png} 
+    \captionsetup{justification=centering}
+    \caption{The confusion matrix of the 6x6 dataset from DeepProbLog}
+    \label{fig:confusion_matrix_6x6_deepproblog}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htp]
+    \begin{center}
+    \includegraphics[width=0.3\textwidth]{confusion_matrix_6x6_pure_NN.png} 
+    \captionsetup{justification=centering}
+    \caption{The confusion matrix of the 6x6 dataset from the purely neural network approach}
+    \label{fig:confusion_matrix_6x6_pure_nn}
     \end{center}

### 2022-03-19 paper/paper.tex
Write further

@@
     \captionsetup{justification=centering}
-    \caption{Abstract representation of the purely neural network based architecture}
+    \caption{Abstract representation of the purely neural network based architecture \cite{model_architecture}}
     \label{fig:pure_nn_network}
@@
     \begin{center}
-    \includegraphics[width=0.3\textwidth]{confusion_matrix_6x6_deepproblog.png} 
+    \includegraphics[width=0.45\textwidth]{confusion_matrix_6x6_deepproblog.png} 
     \captionsetup{justification=centering}
@@
     \begin{center}
-    \includegraphics[width=0.3\textwidth]{confusion_matrix_6x6_pure_NN.png} 
+    \includegraphics[width=0.45\textwidth]{confusion_matrix_6x6_pure_NN.png} 
     \captionsetup{justification=centering}
@@
 
-% Denote difference between epochs and iterations!
-% Trained on CPU
+DeepProbLog naturally will not make any `nonsense' mistakes such as answering `yes' to the question `What shape has the object under investigation?', since the possible correct answers are encoded in the program each time.
+However, the purely neural network based approach has remarkably learned to link the possible answers to the questions.
 
-It is clear that the network trained with DeepProbLog is able to learn way faster then the purely NN based approach, if measured in the number of iterations \footnote{By the number of iterations, the number of training steps on a batch is meant.}.
-However, the differences in training time are much less significant% TODO give concrete measures
-, due to the high computational cost associated with the arithmetic parts of the circuit (i.e. the semirings).
+Another observation is that DeepProbLog is much better in answering the questions `What shape has the object under investigation?' and `Is the object located on the left hand side (or on the bottom side) of the image?' then a purely neural network approach is.
+This makes sense, since DeepProbLog can use its knowledge base to derive these properties, once the position (and shape) of the given object is determined.
+
+Regarding the binary question: `How many objects have the same shape as the object under investigation?', a lot more confusion in both approaches is going on.
+DeepProbLog will typically be able to come close to the correct answer, but may make some `off-by-one' mistakes\footnote{I.e.
+one CNN that is mispredicting the shape of its object.}.
+The purely neural network based approach does a little worse in this perspective.
+It is also plausible that in this approach, the neural network may have observed that due to probabilistic reasons, there are likely three or four equal objects (inclusive the one under investigation), and hence prefer such an answer.
 
@@
 
-\section{APPENDIX}
+\bibliographystyle{bib_sobraep}
+\bibliography{Capita_Selecta_AI_Initial_Idea}
+
+\section*{APPENDIX}
 \subsection{Logical rule encodings}
@@
 
-\bibliographystyle{bib_sobraep}
-\bibliography{Capita_Selecta_AI_Initial_Idea}
-
 %\balance

### 2022-03-20 paper/paper.tex
Write further
Write abstract

@@
 \maketitle
-
-% TODO fix the numbering (also subsection = A)
-% TODO also maybe include some results from other papers.
+% TODO also maybe include some results from other papers. (E.g. see paper of relational-networks)
 
 \begin{abstract}
-	TODO
+	This report focusses on Visual Question Answering, where a Neuro Symbolic AI approach with a knowledge base is compared with a purely neural network based approach.
+From the experiments, it follows that DeepProbLog, the framework used for the Neuro Symbolic AI approach, is able to achieve the same accuracy as the pure neural network based approach with almost 200 times less iterations.
+Clearly, the training is much more targeted, but however, comes at a cost.
+The algebraic operators internal to DeepProbLog are extremely costly and hence the actual training time is more then twenty times slower, when both approaches were trained on a CPU.
+Another drawback of DeepProbLog is that no easy speedups can be achieved, since the algebraic operators only work on CPU's, and hence cannot benefit from accelerators such as GPU's.
 \end{abstract}
@@
 Seen from an optimization viewpoint, errors made during prediction in this setup can be targeted exactly, which makes the optimization process more targeted as well, and hence more efficient.
-Finally, this paper also provides evidence for these statements, since in Subsection \ref{subsec:experiments_NN_vs_deepproblog}, the comparison between a VQA implementation with DeepProbLog is made with a purely CNN based approach.
+Finally, this paper also provides evidence for these statements, since in subsection \ref{subsec:experiments_NN_vs_deepproblog}, the comparison between a VQA implementation with DeepProbLog is made with a purely CNN based approach.
 
@@
 As illustrated earlier, both system 1 and system 2 are required for these types of VQA's.
+
+A.
+Santoro et al.
+conducted similar experiment with the Sort-of-CLEVR dataset as in this paper, where they were able to achieve an accuracy of 63\% on relational questions with CNN's, whereas an accuracy of 94\% for both relational and non-relational questions was achieved with CNN's complemented with an RN.
+For them, augmenting the model with a relational module, such as an RN, turned out to be sufficient to overcome the hurdle of solving relational questions \cite{sort_of_clevr_dataset}.
 
@@
     \begin{center}
-    \fbox{\includegraphics[width=0.3\textwidth]{sample_image_dataset.png}}
+    \fbox{\includegraphics[width=0.25\textwidth]{sample_image_dataset.png}}
     \captionsetup{justification=centering}
@@
 
-\begin{figure}[htp]
+\begin{figure}[H]
     \begin{center}
@@
 From the loss curves, it is clear that both approaches seem to converge to an accuracy of 100\%.
-However, DeepProbLog only requires around 40 iterations, whereas the purely neural network based approach requires at least 250 000 iterations.
-This again demonstrates the value of neuro-symbolic AI.
+However, DeepProbLog only requires around 40 iterations, whereas the purely neural network based approach requires at least 7 800 iterations.
+This again demonstrates the value of Neuro Symbolic AI.
 
 On the other hand, one has to consider the actual running times for those iterations.
-DeepProbLog takes around 10 minutes to finish its 160 iterations, while the purely neural network based approach requires around 5 minutes to finish 250 000 iterations.
+DeepProbLog takes around 10 minutes to finish its 160 iterations, while the purely neural network based approach requires around 5 minutes to finish 7 800 iterations.
 Taking into consideration that the purely neural network based approach can be accelerated massively (by using GPU's), while DeepProbLog can't\footnote{DeepProbLog offers the ability to send the CNN to a GPU for faster inference, however, the arithmetic operators (i.e.
@@
 
-Confusion matrices indicate where typical mistakes are made.
+In Figure \ref{fig:confusion_matrix_6x6_deepproblog} and Figure \ref{fig:confusion_matrix_6x6_pure_nn}, the confusion matrices are depicted in order to show where typical mistakes are made.
 
@@
 This makes sense, since DeepProbLog can use its knowledge base to derive these properties, once the position (and shape) of the given object is determined.
+The observation that a pure neural network based approach has a much harder time to distinguish these cases, was also observed by \cite{sort_of_clevr_dataset}, where they achieved an accuracy of 52.3\% on these questions with a pure neural network based approach.
 

### 2022-03-20 paper/paper.tex
Write conclusion

@@
 \begin{itemize}
-    \item Non-binary - What is the shape of this object \footnote{I.e. the shape will be either a square or a circle.}?
-    \item Non-binary - Is this object located on the left side of the image?
-    \item Non-binary - Is this object located on the bottom side of the image?
+    \item Non-relational - What is the shape of this object \footnote{I.e. the shape will be either a square or a circle.}?
+    \item Non-relational - Is this object located on the left side of the image?
+    \item Non-relational - Is this object located on the bottom side of the image?
     \item Binary - How many objects have the same shape as this object?
@@
 
-Regarding the binary question: `How many objects have the same shape as the object under investigation?', a lot more confusion in both approaches is going on.
+Regarding the relational question: `How many objects have the same shape as the object under investigation?', a lot more confusion in both approaches is going on.
 DeepProbLog will typically be able to come close to the correct answer, but may make some `off-by-one' mistakes\footnote{I.e.
@@
 \label{sec:conclusions}
+The strengths of the Neuro Symbolic AI field have been demonstrated in the context of Visual Question Answering.
+By using DeepProbLog, the chosen framework for the Neuro Symbolic AI task, it became clear that almost 200 times less iterations are required to achieve the same accuracy as a purely neural network based approach.
+However, due to the costly algebraic operators, the total training time of the DeepProbLog approach was still more than twenty times slower, compared to the purely neural network based approach.
+
+Important to notice, however, is that DeepProbLog performs a lot better on the non-relational questions.
+This because the knowledge base can derive these properties much more accurately, while a purely neural network based approach has more difficulties with such derivations.
+
+Hence, a lot of value can be seen in Neuro Symbolic AI approaches, despite the costly algebraic operators.
+Especially because for tasks where the knowledge base is much larger, these approaches can make the difference between being able to learn a certain task or not.
+Over time, speedups for these algebraic operators could probably be developed, which opens the road to even more applications.
 

### 2022-03-20 paper/paper.tex
Write further

@@
 Clearly, the training is much more targeted, but however, comes at a cost.
-The algebraic operators internal to DeepProbLog are extremely costly and hence the actual training time is more then twenty times slower, when both approaches were trained on a CPU.
+The algebraic operators internal to DeepProbLog are extremely costly and hence the actual training time is considerably slower.
 Another drawback of DeepProbLog is that no easy speedups can be achieved, since the algebraic operators only work on CPU's, and hence cannot benefit from accelerators such as GPU's.
@@
 \section{ORGANIZATION OF THE PAPER}
-This paper will first provide some necessary background in Section \ref{sec:literature_survey} on certain types of datasets that are typically used for Visual Question Answering purposes.
+This paper will first provide some necessary background in Section \ref{sec:literature_survey} on certain types of datasets that are typically used for Visual Question Answering purposes, along with introducing some results of other researchers.
 Then, Section \ref{sec:approach} will dive deeper in the different components constituting the overall system.
@@
 Seen from an optimization viewpoint, errors made during prediction in this setup can be targeted exactly, which makes the optimization process more targeted as well, and hence more efficient.
-Finally, this paper also provides evidence for these statements, since in subsection \ref{subsec:experiments_NN_vs_deepproblog}, the comparison between a VQA implementation with DeepProbLog is made with a purely CNN based approach.
+Finally, this paper also provides evidence for these statements, since in subsection \ref{subsec:experiments_NN_vs_deepproblog}, the comparison between a VQA implementation with DeepProbLog is made with a purely neural network based approach.
 
@@
 Santoro et al.
-conducted similar experiment with the Sort-of-CLEVR dataset as in this paper, where they were able to achieve an accuracy of 63\% on relational questions with CNN's, whereas an accuracy of 94\% for both relational and non-relational questions was achieved with CNN's complemented with an RN.
+conducted similar experiment with the Sort-of-CLEVR dataset as in this paper, where they were able to achieve an accuracy of 63\% on relational questions with CNN's.
+In contrast, an accuracy of 94\% for both relational and non-relational questions was achieved with CNN's complemented with an RN.
 For them, augmenting the model with a relational module, such as an RN, turned out to be sufficient to overcome the hurdle of solving relational questions \cite{sort_of_clevr_dataset}.
@@
 \begin{itemize}
-    \item Non-relational - What is the shape of this object \footnote{I.e. the shape will be either a square or a circle.}?
+    \item Non-relational - What is the shape of this object \footnote{The shape will be either a square or a circle.}?
     \item Non-relational - Is this object located on the left side of the image?
     \item Non-relational - Is this object located on the bottom side of the image?
-    \item Binary - How many objects have the same shape as this object?
+    \item Relational - How many objects have the same shape as this object?
 \end{itemize}
 
-These questions are encoded in a one-hot encoding, after which they are stored in a CSV file, along with the expected answers.
-To make the training process more efficient, a training and test dataset has been generated beforehand.
+These questions are encoded in a vector encoding, after which they are stored in a CSV file, along with the expected answers.
+A training and test dataset has been generated beforehand, in order to make the training process more efficient.
 
@@
 \label{subsec:experiments_NN_vs_deepproblog}
-\subsubsection{Experiment: 2x2 grid}
+\subsubsection{Experiment - 2x2 grid}
 The loss curves of both the DeepProbLog approach, as well as the purely neural network based approach, are visualized respectively in Figure \ref{fig:loss_curve_deepproblog_2x2} and Figure \ref{fig:loss_curve_pure_NN_2x2}.
@@
 
-\subsubsection{Experiment: 6x6 grid}
+\subsubsection{Experiment - 6x6 grid}
 The loss curves for the 6x6 experiment of DeepProbLog and the neural network based approach are depicted in respectively Figure \ref{fig:loss_curve_deepproblog_6x6} and Figure \ref{fig:loss_curve_pure_NN_6x6}.
@@
 
-In these experiments, the training time of the purely neural network approach was 20 minutes\footnote{For fair speed estimation, training has been conducted on the CPU.}, while the training time of the DeepProbLog approach was a little under eight hours\footnote{However, it should be mentioned that approximately half of the time was spent on calculating the accuracy each time, since the whole testing training set had to be forwarded through the network, while for the training iterations this is only one batch.}.
+In these experiments, the training time of the purely neural network approach was 20 minutes\footnote{For fair speed estimation, training has been conducted on the CPU.}, while the training time of the DeepProbLog approach was a little under eight hours\footnote{However, it should be mentioned that approximately half of the time was spent on calculating the accuracy each time, since the whole testing testing set had to be forwarded through the network, while for the training iterations this is only one batch.}.
 
-The most important observation here is that the purely neural network approach overfits quickly.
+The most important observation here is that the purely neural network approach overfits quickly and also achieves a considerably lower accuracy (68\% instead of almost 75\% for DeepProbLog).
 Another important remark is the fact that both approaches are clearly not longer able to attain 100\% accuracy.
+However, if the DeepProbLog network could train longer, it would be able to converge even further.
 
@@
 By using DeepProbLog, the chosen framework for the Neuro Symbolic AI task, it became clear that almost 200 times less iterations are required to achieve the same accuracy as a purely neural network based approach.
-However, due to the costly algebraic operators, the total training time of the DeepProbLog approach was still more than twenty times slower, compared to the purely neural network based approach.
+However, due to the costly algebraic operators, the total training time of the DeepProbLog approach was considerably slower, compared to the purely neural network based approach.
 

### 2022-03-20 paper/paper.tex
Further review

@@
 Another important remark is the fact that both approaches are clearly not longer able to attain 100\% accuracy.
-However, if the DeepProbLog network could train longer, it would be able to converge even further.
+However, if the DeepProbLog network could train longer, it would be able to converge somewhat further.
 
@@
 
-DeepProbLog naturally will not make any `nonsense' mistakes such as answering `yes' to the question `What shape has the object under investigation?', since the possible correct answers are encoded in the program each time.
-However, the purely neural network based approach has remarkably learned to link the possible answers to the questions.
+DeepProbLog naturally will not make any `nonsense' mistakes such as answering `yes' to the question `What shape has the object under investigation?', since the possible correct answers are encoded in the program.
+However, the purely neural network based approach has learned perfectly to link the possible answers to the questions.
 
@@
 one CNN that is mispredicting the shape of its object.}.
-The purely neural network based approach does a little worse in this perspective.
-It is also plausible that in this approach, the neural network may have observed that due to probabilistic reasons, there are likely three or four equal objects (inclusive the one under investigation), and hence prefer such an answer.
+The purely neural network based approach does also in this perspective a little worse.
+It is also plausible that in this approach, the neural network may have observed that due to probabilistic reasons, there are likely three or four equal objects (inclusive the one under investigation), and hence prefers such an answer.
 

### 2022-03-20 paper/paper.tex
Small addition for referring to other authors

@@
 For them, augmenting the model with a relational module, such as an RN, turned out to be sufficient to overcome the hurdle of solving relational questions \cite{sort_of_clevr_dataset}.
+They were the only researchers who undertook experiments on a dataset resembling the one from this paper, and hence are the only reference point.
 
@@
 The observation that a pure neural network based approach has a much harder time to distinguish these cases, was also observed by \cite{sort_of_clevr_dataset}, where they achieved an accuracy of 52.3\% on these questions with a pure neural network based approach.
+DeepProbLog was not able to achieve the accuracy of 94\% that these researchers achieved, which may be due to the inherent high cost of the algebraic operators, as well as due to less resources and less hyperparameter tuning, among many other unknown variables.
 

### 2022-03-21 paper/paper.tex
Review whole paper again

--- 2022-03-20 paper/paper.tex
@@
 Then, Section \ref{sec:approach} will dive deeper in the different components constituting the overall system.
-Section \ref{sec:experiments}, furthermore, provides some results of conducted experiments.
-A main focus in this paper is to outline the advantages of using a Neuro-Symbolic AI approach (offered by the DeepProbLog framework), instead of a purely neural network based approach.
+A main focus of this paper is to outline the advantages of using a Neuro-Symbolic AI approach (offered by the DeepProbLog framework), compared to a purely neural network based approach.
 These experiments are listed in Section \ref{sec:experiments}.
@@
 The application focuses on Visual Question Answering (VQA), for which huge datasets are present, along with very sophisticated methods.
-The best known dataset for VQA is CLEVR \cite{clevr_dataset}, which contains 100k images with one million questions.
+The best known dataset for VQA is CLEVR \cite{clevr_dataset}, which contains 100k images accompanied by one million questions.
 An example image is given in Figure \ref{fig:sample_image_clevr}, while example questions are:
@@
 In essence, it is almost like the Sort-Of-CLEVR dataset \cite{sort_of_clevr_dataset}.
-This Sort-Of-CLEVR dataset contains images such as in Figure \ref{fig:sample_image_sort_of_clevr}, while asking questions such as:
+This Sort-Of-CLEVR dataset contains images as in Figure \ref{fig:sample_image_sort_of_clevr}, while asking questions such as:
 \begin{itemize}
@@
 Santoro et al.
-conducted similar experiment with the Sort-of-CLEVR dataset as in this paper, where they were able to achieve an accuracy of 63\% on relational questions with CNN's.
-In contrast, an accuracy of 94\% for both relational and non-relational questions was achieved with CNN's complemented with an RN.
+conducted similar experiments with the Sort-of-CLEVR dataset as in this paper, where they were able to achieve an accuracy of 63\% on relational questions with CNN's.
+In contrast, an accuracy of 94\% for both relational and non-relational questions was achieved with CNN's, complemented with an RN.
 For them, augmenting the model with a relational module, such as an RN, turned out to be sufficient to overcome the hurdle of solving relational questions \cite{sort_of_clevr_dataset}.
+They were the only researchers who undertook experiments on a dataset resembling the one from this paper, and hence are the only reference point.
 
@@
 Hence, each discrete position will have to be encoded by a possible outcome of the neural network.
-Therefore, objects may only be located at certain places in a grid.
+Therefore, objects may only be located at certain positions in a grid.
 In this paper, results on a grid of 2x2 and 6x6 are discussed.
@@
 \begin{itemize}
-    \item Non-relational - What is the shape of this object \footnote{The shape will be either a square or a circle.}?
+    \item Non-relational - What is the shape of this object?\footnote{The shape will be either a square or a circle.}
     \item Non-relational - Is this object located on the left side of the image?
@@
 \label{sec:experiments}
-The main focus of this paper is to outline the advantages of using a Neuro-Symbolic AI approach (offered by the DeepProbLog framework), instead of a purely neural network based approach.
-Therefore, another purely neural network based approach had to be implemented.
+The main focus of this paper is to outline the advantages of using a Neuro Symbolic AI approach (offered by the DeepProbLog framework), instead of a purely neural network based approach.
+Therefore, a neural network based approach had to be implemented.
 Not all details will be listed here, but the main idea is that the image has to be fused with the question, after which a prediction can be made\footnote{Possible answers on the questions are: rectangle, circle, yes, no, 1, 2, 3, 4, 5 and 6.
@@
 \end{figure}
-An extremely important remark to be made is the difference between `Number of iterations' and `Number of epochs'.
-By the number of iterations, the number of forward and backward passes of a batch (with size 32) is meant, whereas the number of epochs denote the number of times all the images of the training set are forward and backwardly passed.
+An extremely important remark to be made is the difference between `number of iterations' and `number of epochs'.
+By the number of iterations, the number of forward and backward passes of a batch (with size 32) is meant, whereas the number of epochs denotes the number of times all the images of the training set are forward and backwardly passed.
 In this application, a training size of 10 000 was used, hence one epoch consists of 312.5 iterations.
@@
 On the other hand, one has to consider the actual running times for those iterations.
-DeepProbLog takes around 10 minutes to finish its 160 iterations, while the purely neural network based approach requires around 5 minutes to finish 7 800 iterations.
+DeepProbLog takes around 10 minutes to finish its 160 iterations, while the purely neural network based approach only requires around 5 minutes to finish 7 800 iterations.
 Taking into consideration that the purely neural network based approach can be accelerated massively (by using GPU's), while DeepProbLog can't\footnote{DeepProbLog offers the ability to send the CNN to a GPU for faster inference, however, the arithmetic operators (i.e.
@@
 
-In these experiments, the training time of the purely neural network approach was 20 minutes\footnote{For fair speed estimation, training has been conducted on the CPU.}, while the training time of the DeepProbLog approach was a little under eight hours\footnote{However, it should be mentioned that approximately half of the time was spent on calculating the accuracy each time, since the whole testing testing set had to be forwarded through the network, while for the training iterations this is only one batch.}.
+In these experiments, the training time of the purely neural network approach was 20 minutes\footnote{For fair speed estimation, training has been conducted on the CPU.}, while the training time of the DeepProbLog approach was a little under eight hours\footnote{However, it should be mentioned that approximately half of the time was spent on calculating the accuracy each time, since the whole testing set had to be forwarded through the network, while for the training iterations this is only one batch.}.
 
@@
 This makes sense, since DeepProbLog can use its knowledge base to derive these properties, once the position (and shape) of the given object is determined.
-The observation that a pure neural network based approach has a much harder time to distinguish these cases, was also observed by \cite{sort_of_clevr_dataset}, where they achieved an accuracy of 52.3\% on these questions with a pure neural network based approach.
+The observation that a pure neural network based approach has a much harder time to distinguish these cases, was also observed by A.
+Santoro et al.
+\cite{sort_of_clevr_dataset}, where they achieved an accuracy of 52.3\% on these questions with a pure neural network based approach.
+DeepProbLog was not able to achieve the accuracy of 94\% that these researchers achieved, which may be due to the inherent training cost of the algebraic operators, as well as due to less resources and less hyperparameter tuning, among many other unknown variables.
 
@@
 \subsection{Logical rule encodings}
+Note: it has been tried to use cuts (with the `cut' library), given that the neural network is seemingly invoked again if the first of a dual predicate fails.
+However, this turned out to not yield any performance improvement and has been abandoned.
 \label{appendix:logical_rule_encodings}

### 2022-03-21 deepproblog/src/deepproblog/examples/SORTOFCLEVR/confusion_matrix_pure_cnn.py

@@ -12,11 +12,10 @@ size = 6
 output_size = 4 + size
 network = PureCNN(size=size, output_size=output_size) # Yes, no, square, circle, 1, 2, 3, 4, 5, 6
 train_dataset = Pure_CNN_Data("train", size)
-test_dataset = Pure_CNN_Data("test", size)
+val_dataset = Pure_CNN_Data("val", size)
 batch_size = 8
 train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
-test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=True)
-
+val_loader = DataLoader(val_dataset, batch_size=batch_size, shuffle=True)
 
 y_pred = []
 y_true = []
@@ -24,7 +23,7 @@ y_true = []
 network.load_state_dict(torch.load("models/model_pure_NN_6x6_100_iterations_16_03_2022.pt"))
 network.eval()
 # iterate over test data
-for (img, questions, answer) in test_loader:
+for (img, questions, answer) in val_loader:
     output = network(img, questions) # Feed Network
 
     output = torch.argmax(output, dim=1).cpu().numpy()
@@ -42,4 +41,4 @@ df_cm = pd.DataFrame(cf_matrix/np.sum(cf_matrix), index = [i for i in classes],
                      columns = [i for i in classes])
 plt.figure(figsize = (12,7))
 sn.heatmap(df_cm, annot=True)
-plt.savefig('plots/confusion_matrix_6x6_100_iterations.png')
+plt.savefig('plots/confusion_matrix_6x6_big_testset_iterations.png')

### 2022-03-21 deepproblog/src/deepproblog/examples/SORTOFCLEVR/model.pl

@@ -1,5 +1,4 @@
-% We know that there are two objects in a four grid space. Two shapes possible, two colors possible.
-% The green cnn detects the position, and the shape --> x. If x < size: Shape = rectangle. Else: shape = circle. (x modulo size = position)  
+% Grid = 6 by 6
 
 width(6).
 size(N) :-
@@ -9,9 +8,6 @@ states(N) :-
     size(Size),
     N is Size * 2.
 
-% [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71]
-% [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31]
-% [0, 1, 2, 3, 4, 5, 6, 7]
 nn(cnn_red,[X],Y_red, [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71]) :: detect_state(red, X, Y_red).
[…]

### 2022-03-21 deepproblog/src/deepproblog/examples/SORTOFCLEVR/pure_cnn_training.py

@@ -10,8 +10,9 @@ from torch import nn, tensor
 import time
 
 # Check if GPU is available
-device = "cuda" if torch.cuda.is_available() else "cpu"
-print(f"Using {device} device")
+#device = "cuda" if torch.cuda.is_available() else "cpu"
+#print(f"Using {device} device")
+device = "cpu"
 
 def accuracy_metric(predictions, expected):
     pred = torch.argmax(predictions, dim=1) # Indices of the max value of all elements -> 0 if "no" has highest probability, 1 if "yes"
@@ -127,7 +128,7 @@ epochs = 100
 train_loss, test_loss, epoch_accs, times = train(network, train_loader, test_loader, loss_function, optimizer, epochs, accuracy_metric, batch_size)
 import pickle
 
-with open('values_of_training_16_03_2022_13_00_6x6_100_epochs.pk', 'wb') as fp:
+with open('values_of_training_19_03_2022_16_00_6x6_100_epochs.pk', 'wb') as fp:
     pickle.dump(train_loss, fp)
     pickle.dump(test_loss, fp)
     pickle.dump(epoch_accs, fp)

### 2022-03-21 deepproblog/src/deepproblog/examples/SORTOFCLEVR/visualize_deepproblog_outcomes.py

@@ -11,7 +11,7 @@ for i, row in enumerate(content[3:]):
         accuracy.append(float(info[1]))
         acc_iter.append(int(info[0]))
     if i == 0:
-        train_loss.append(1.138294846170652)
+        train_loss.append(0.87)
     else:
         train_loss.append(float(info[3]))
     time = info[2]
@@ -24,7 +24,7 @@ lns1 = ax.plot(train_loss, color="g", label="Training loss")
 lns3 = ax1.plot(acc_iter, accuracy, color="b", label="Testing accuracy")
 #ax1.xlabel("Number of batch iterations")
 #ax2.ylabel("Loss")
-ax.set_xlabel("Epoch", color="black")
+ax.set_xlabel("Iteration", color="black")
 ax.set_ylabel("Loss", color="black")
 ax.tick_params(axis='x', colors="black")
 ax.tick_params(axis='y', colors="black")
@@ -42,6 +42,6 @@ ax1.get_xaxis().set_ticks([])
 leg = lns1 + lns3
 labs = [l.get_label() for l in leg]
 ax1.legend(leg, labs, loc=5)
-plt.savefig("plots/deepproblog_6x6_18_03_2022.png")
+plt.savefig("plots/deepproblog_6x6.png")
 
 print("Total training time: " + str(time))

### 2022-03-21 relational-networks/sort_of_clevr_generator.py

@@ -178,7 +178,7 @@ def build_dataset_item():
 
 if __name__ == "__main__":
     size = str(WIDTH) + "x" + str(WIDTH)
-    for (dataset, num, seed) in [("train", 10000, 0), ("val", 500, 1), ("test", 500, 2)]:
+    for (dataset, num, seed) in [("train", 10000, 0), ("val", 10000, 1), ("test", 500, 2)]:
         path = '../deepproblog/src/deepproblog/examples/SORTOFCLEVR/data/' + size + '/' + dataset
 
         if not os.path.exists(path + '/images'):

### 2022-03-24 paper/paper.tex
Final review of paper

@@
 system 1, typical subconscious tasks such as visual recognition, the processing of languages, \dots), along with the strengths of rule-based probabilistic systems (i.e.
-system 2, slow, sequential thinking such as the derivation of a proof).
+system 2, slow, sequential thinking such as the derivation of a proof) \cite{sys1and2}.
 
@@
 Then, Section \ref{sec:approach} will dive deeper in the different components constituting the overall system.
-A main focus of this paper is to outline the advantages of using a Neuro-Symbolic AI approach (offered by the DeepProbLog framework), compared to a purely neural network based approach.
+A main focus of this paper is to outline the advantages of using a Neuro Symbolic AI approach (offered by the DeepProbLog framework), compared to a purely neural network based approach.
 These experiments are listed in Section \ref{sec:experiments}.
@@
 This paper is inspired on the CLEVR dataset, but uses however a much more simplified version.
-In essence, it is almost like the Sort-Of-CLEVR dataset \cite{sort_of_clevr_dataset}.
-This Sort-Of-CLEVR dataset contains images as in Figure \ref{fig:sample_image_sort_of_clevr}, while asking questions such as:
+In essence, it is almost like the Sort-of-CLEVR dataset \cite{sort_of_clevr_dataset}.
+This Sort-of-CLEVR dataset contains images as in Figure \ref{fig:sample_image_sort_of_clevr}, while asking questions such as:
 \begin{itemize}
@@
     \captionsetup{justification=centering}
-    \caption{A sample image from the CLEVR dataset \cite{sort_of_clevr_dataset}}
+    \caption{A sample image from the Sort-of-CLEVR dataset \cite{sort_of_clevr_dataset}}
     \label{fig:sample_image_sort_of_clevr}
@@
 \begin{enumerate}
-    \item Generation of data.
+    \item Generation of the data.
     \item Linking the data and controlling the training process in pure Python code.
@@
 
-\subsection{Generation of data}
-As mentioned in Section \ref{sec:literature_survey}, the data used in this application is based on the Sort-Of-CLEVR dataset, with one extra simplification.
+\subsection{Generation of the data}
+As mentioned in Section \ref{sec:literature_survey}, the data used in this application is based on the Sort-of-CLEVR dataset, with one extra simplification.
 Given that the logical part will have to decide whether an object is for example located on the left side of an image, the neural network will have to convey positional information to the logical part.
@@
 
-The data generator that was used for the creation of the Sort-Of-CLEVR dataset has been modified in order to place objects in the mentioned grid positions \cite{sort_of_clevr_dataset}.
+The data generator that was used for the creation of the Sort-of-CLEVR dataset has been modified in order to position objects in the mentioned grid positions \cite{sort_of_clevr_dataset}.
 An example of a generated image is given in Figure \ref{fig:sample_image_own_dataset}, where the difference with Figure \ref{fig:sample_image_sort_of_clevr} is the grid-layout.
@@
 \begin{itemize}
-    \item Non-relational - What is the shape of this object?\footnote{The shape will be either a square or a circle.}
-    \item Non-relational - Is this object located on the left side of the image?
-    \item Non-relational - Is this object located on the bottom side of the image?
-    \item Relational - How many objects have the same shape as this object?
+    \item Non-relational --- What is the shape of this object\footnote{The shape will be either a square or a circle.}?
+    \item Non-relational --- Is this object located on the left hand side of the image?
+    \item Non-relational --- Is this object located on the bottom side of the image?
+    \item Relational --- How many objects have the same shape as this object?
 \end{itemize}
@@
 Not all details will be listed here, but the main idea is that the image has to be fused with the question, after which a prediction can be made\footnote{Possible answers on the questions are: rectangle, circle, yes, no, 1, 2, 3, 4, 5 and 6.
-Hence, the neural network will have 10 output nodes.}.
+Hence, the neural network will have 10 output nodes.
+Care has been taken for class skew, by introducing weights in the loss function.}.
 The general structure of this network is given in Figure \ref{fig:pure_nn_network}.
@@
 \label{subsec:experiments_NN_vs_deepproblog}
-\subsubsection{Experiment - 2x2 grid}
+\subsubsection{Experiment --- 2x2 grid}
 The loss curves of both the DeepProbLog approach, as well as the purely neural network based approach, are visualized respectively in Figure \ref{fig:loss_curve_deepproblog_2x2} and Figure \ref{fig:loss_curve_pure_NN_2x2}.
@@
 
-\subsubsection{Experiment - 6x6 grid}
+\subsubsection{Experiment --- 6x6 grid}
 The loss curves for the 6x6 experiment of DeepProbLog and the neural network based approach are depicted in respectively Figure \ref{fig:loss_curve_deepproblog_6x6} and Figure \ref{fig:loss_curve_pure_NN_6x6}.
@@
 
-In these experiments, the training time of the purely neural network approach was 20 minutes\footnote{For fair speed estimation, training has been conducted on the CPU.}, while the training time of the DeepProbLog approach was a little under eight hours\footnote{However, it should be mentioned that approximately half of the time was spent on calculating the accuracy each time, since the whole testing set had to be forwarded through the network, while for the training iterations this is only one batch.}.
+In these experiments, the training time of the purely neural network based approach was 20 minutes\footnote{For fair speed estimation, training has been conducted on the CPU.}, while the training time of the DeepProbLog approach was a little under eight hours\footnote{However, it should be mentioned that approximately half of the time was spent on calculating the accuracy each time, since the whole testing set had to be forwarded through the network, while for the training iterations this is only one batch.}.
 
-The most important observation here is that the purely neural network approach overfits quickly and also achieves a considerably lower accuracy (68\% instead of almost 75\% for DeepProbLog).
-Another important remark is the fact that both approaches are clearly not longer able to attain 100\% accuracy.
+The most important observation here is that the purely neural network approach overfits quickly and also achieves a considerably lower accuracy (68\% instead of 75\% for DeepProbLog).
+Another important remark is the fact that both approaches are clearly not longer able to attain an accuracy of 100\%.
 However, if the DeepProbLog network could train longer, it would be able to converge somewhat further.
@@
 
-Another observation is that DeepProbLog is much better in answering the questions `What shape has the object under investigation?' and `Is the object located on the left hand side (or on the bottom side) of the image?' then a purely neural network approach is.
+Another observation is that DeepProbLog is much better in answering the questions `What shape has the object under investigation?' and `Is the object located on the left hand side (or on the bottom side) of the image?' than a purely neural network approach is.
 This makes sense, since DeepProbLog can use its knowledge base to derive these properties, once the position (and shape) of the given object is determined.
@@
 Santoro et al.
-\cite{sort_of_clevr_dataset}, where they achieved an accuracy of 52.3\% on these questions with a pure neural network based approach.
-DeepProbLog was not able to achieve the accuracy of 94\% that these researchers achieved, which may be due to the inherent training cost of the algebraic operators, as well as due to less resources and less hyperparameter tuning, among many other unknown variables.
+\cite{sort_of_clevr_dataset}, where they achieved an accuracy of 63\% on these questions with a pure neural network based approach.
+DeepProbLog was not able to achieve the accuracy of 94\% that these researchers achieved on all questions with an added RN module, which may be due to the inherent training cost of the algebraic operators, as well as due to less resources, less hyperparameter tuning, and an absence of RN modules, among many other unknown variables.
 
@@
 \label{sec:conclusions}
-The strengths of the Neuro Symbolic AI field have been demonstrated in the context of Visual Question Answering.
+The strengths of the Neuro Symbolic AI field has been demonstrated in the context of Visual Question Answering.
 By using DeepProbLog, the chosen framework for the Neuro Symbolic AI task, it became clear that almost 200 times less iterations are required to achieve the same accuracy as a purely neural network based approach.
@@
 Hence, a lot of value can be seen in Neuro Symbolic AI approaches, despite the costly algebraic operators.
-Especially because for tasks where the knowledge base is much larger, these approaches can make the difference between being able to learn a certain task or not.
+Especially for tasks where the knowledge base is much larger, these approaches can make the difference between being able to learn a certain task or not.
 Over time, speedups for these algebraic operators could probably be developed, which opens the road to even more applications.

### 2022-03-25 paper/paper.tex
Add code repository to paper

@@
 	\normalsize $^{1}$Catholic University of Leuven, Leuven -- Belgium \\
-	\normalsize e-mail: jorrit.willaert@student.kuleuven.be
+	\normalsize e-mail: jorrit.willaert@student.kuleuven.be \\
+    \normalsize code repository: https://github.com/JorritWillaert/Capita-Selecta-Neuro-Symbolic-AI
 }
@@
 Therefore, a neural network based approach had to be implemented.
-Not all details will be listed here, but the main idea is that the image has to be fused with the question, after which a prediction can be made\footnote{Possible answers on the questions are: rectangle, circle, yes, no, 1, 2, 3, 4, 5 and 6.
+Not all details will be listed here, but the main idea is that the image has to be fused whttps://github.com/JorritWillaert/Capita-Selecta-Neuro-Symbolic-AIith the question, after which a prediction can be made\footnote{Possible answers on the questions are: rectangle, circle, yes, no, 1, 2, 3, 4, 5 and 6.
 Hence, the neural network will have 10 output nodes.
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{loss_curve_deepproblog_2x2.png} 
+    \includegraphics[width=0.40\textwidth]{loss_curve_deepproblog_2x2.png} 
     \captionsetup{justification=centering}
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{loss_curve_pure_NN_2x2.png} 
+    \includegraphics[width=0.40\textwidth]{loss_curve_pure_NN_2x2.png} 
     \captionsetup{justification=centering}
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{loss_curve_deepproblog_6x6.png} 
+    \includegraphics[width=0.40\textwidth]{loss_curve_deepproblog_6x6.png} 
     \captionsetup{justification=centering}
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{loss_curve_pure_NN_6x6.png} 
+    \includegraphics[width=0.40\textwidth]{loss_curve_pure_NN_6x6.png} 
     \captionsetup{justification=centering}

### 2022-03-25 paper/paper.tex
Fix url in text

--- 2022-03-24 paper/paper.tex
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{loss_curve_deepproblog_2x2.png} 
+    \includegraphics[width=0.42\textwidth]{loss_curve_deepproblog_2x2.png} 
     \captionsetup{justification=centering}
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{loss_curve_pure_NN_2x2.png} 
+    \includegraphics[width=0.42\textwidth]{loss_curve_pure_NN_2x2.png} 
     \captionsetup{justification=centering}
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{loss_curve_deepproblog_6x6.png} 
+    \includegraphics[width=0.42\textwidth]{loss_curve_deepproblog_6x6.png} 
     \captionsetup{justification=centering}
@@
     \begin{center}
-    \includegraphics[width=0.45\textwidth]{loss_curve_pure_NN_6x6.png} 
+    \includegraphics[width=0.42\textwidth]{loss_curve_pure_NN_6x6.png} 
     \captionsetup{justification=centering}
